At the end of trade, the Prague Stock Exchange tumbled into negative
After the fall of Tuesday morning, the Prague Stock Exchange corrected its losses.
Transactions with CEZ shares reached almost half of the normal daily trading.
Tuesday at the start of trading, the Prague Stock Exchange with its renewed his fall the previous day, when lost almost six percent.
This time, the decline was due to the fall of Wall Street shares.
The market reaction to the vote of the U.S. House of Representatives, who refused to adopt the plan to stabilize the U.S. financial sector is also well visible here.
Asian shares fall
Asian stock markets Tuesday lived a dramatic fall, even if the indices managed, during the day, erasing some of the losses.
The Hang Seng Index of the Hong Kong Stock Exchange lost four per cent during the exchange, but later he erased some losses and reduced down to about 2.5 percent.
The Hang Seng China Enterprises following the movement of Chinese Equity Hong Kong Stock Exchange lost 3.8 percent as markets closed in Shanghai.
The shares of the Sydney Stock Exchange lost more than five percent, but finally we managed to reduce losses to 4.3 percent.
According to the index, the Taiwan Stock Exchange lost 3.6 percent.
"The hesitation about the rescue operation in the U.S. will affect financial markets around the world," remarked Joseph Yam, head of the Hong Kong currency board.
Although Hong Kong is part of China, it sets monetary policy itself, that is to say, regardless of the Chinese central bank.
The interest rates in Hong Kong on the same level as in the United States.
According to the Australian Prime Minister Kevin Rudd, U.S. lawmakers should quickly resume negotiations and adopt the proposal supports the financial system.
Otherwise, we risk that other countries suffer the consequences.
The bloodshed of U.S. equities
On Monday, the U.S. House of Representatives rejected the project supports the financial system, which it would have had to spend up to 700 billion dollars (about 12 ridges Kc).
Legislators and disowned the call to support the project of President George Bush.
According to Bush, the project will address the major causes of the financial crisis and help stabilize the entire economy.
U.S. stocks lived Monday, bloodshed and major equity indices experienced the largest drop in the last 20 years.
The Dow Jones lost nearly seven percent have experienced a fall of this magnitude for the last time in 1987.
The index already lost during the vote, but when it appeared that the proposal was not adopted, it was in freefall.
Congress gave: the U.S. government can inject $ 700 billion into banks
The leaders of the U.S. Congress and the administration of President George W. Bush agreed on a broader form of financial aid agreement to the U.S. financial system.
It will be submitted to a vote early next week.
U.S. lawmakers ran a turning point in the negotiations on the adoption of a bailout in the form of financial assistance amounting to $ 700 billion (about 12 billion crowns), granted the U.S. financial system .
Success does not mean safe.
Indeed, before they release the final version of the bill and submit it to the vote, the Congressmans must complete a number of details of the agreement.
The plan supports the financial system will be discussed Monday at the House of Representatives.
Told Reuters on Sunday Barney Frank, the chairman of the Banking and Financial Regulation of the House.
According to sources, on Wednesday at the earliest, the plan should a priori be voted on in the Senate.
According to economists, the announcement that the rescue plan will be adopted should be a first major psychological factor to revive financial markets.
However, given the complexity of the mechanisms through which market support to be effective, follow a "disappointment."
Paulson: The plan must be effective
"We have made great progress.
We set our differing views on the form should have the package of measures to stabilize the market, "Bloomberg told the Agency Democrat Nancy Pelosi.
She said the final vote could take place as early as Sunday.
In the night from Saturday to Sunday, representatives of legislators met the U.S. Secretary of Finance Henry Paulson, to give the government fund a final form.
It should redeem from financial companies, real estate unmarketable assets that lead financial firms in considerable losses and threaten the stability of the entire system.
"We are about to agree on a plan that will work and should be also effective on the market.
We must also continue the recovery plan market, but I think we are, "said Paulson.
A signal for Asian trade
The global financial crisis had a significant impact on the equity markets fall.
According to Democratic Senator Harry Reid does évadiez, legislators are so Congress will lead to a final agreement on Sunday.
They want and calm investors before the start of trading on Asian financial markets, which are located in the first time zone where the Congress decision could affect trade Monday.
But for now, it is impossible to say with certainty when the two Houses of Congress will proceed to a vote, or if negotiations are not likely to get stuck at the last moment, by this or that problem.
Lawmakers hope it will be adopted in the coming days.
Nevertheless, the law still experience many changes.
The total amount for using the system should be divided into two parts.
The first $ 350 billion, as desired by President George Bush, should be available as soon as possible.
But if Congress has the impression that the program does not fulfill its function, it has the ability to block the granting of the remaining amount, following two steps: first an additional 100 billion dollars, and then, finally, $ 350 billion.
Bush hailed progress in negotiations
Although the president can put his veto this decision, the Congress, he has the opportunity to put this one in the minority.
Despite these changes, the main idea of ​​the program, which was to obtain finance for the purchase of bad real estate securities, whose value dropped, because hundreds of thousands of Americans are unable to pay their mortgages, was maintained.
"All the work is done.
The House of Representatives should be able to do Sunday to vote on the law, and the Senate Monday, "stated Republican Senator Judd Gregg.
U.S. President George Bush himself is pleased with the progress in the negotiations.
His spokesman Tony Fratto said that Bush was pleased with the progress made on Saturday and appreciated the "bipartisan effort to stabilize our financial markets and protect our economy."
Limitation of golden parachutes
The President of the Senate Banking Committee Christopher Dodd, chief negotiator, said that lawmakers have agreed for the financial program, contributing protection against losses, the agreement breaks the implementation of the plan on the time axis.
The new law also said plans to limit golden parachutes for directors of companies participating in the program and set up a committee that will oversee the fund.
It should be managed by the Ministry of Finance.
"We worked very hard on this issue and have made significant progress towards an agreement that will work and be effective for the market and for all Americans," said Paulson.
The plan also provides assistance to homeowners who have problems paying.
The government should negotiate new installments in the case of mortgages it will buy, while reducing monthly debtors and allowing them to keep their homes.
Marek: A psychological
According to the chief economist at Patria Finance David Marek, the proposed plan is a good idea, but its implementation will be very difficult.
"And this is because we do not know what the mechanism and the price of buying assets from problems.
This will be determinative of the loss sharing between the financial sector and the government, "said Marek, this week, the server iHNed.cz.
If the plan is adopted now, or early next week, is, according to Marek, not that important.
"It is much more important than Congressmans agree, this week, they support the plan and they devote as soon as possible.
The psychological significance of the agreement, providing for the adoption of the plan, the most important right now, "emphasized Marek.
A fight in the extreme: MP3 Players against mobile.
We will advise you how to choose
While virtually all mobile read MP3 files, MP3 player knows no call.
It seems clear that the result is better to buy a phone only.
Still there are enough reasons to obtain an independent player.
The choice depends entirely on the method of use and the requirements of the future owner.
It would be absurd to buy an expensive home gramophone upscale to put the new album Maxim Turbulenc.
On the one hand, these music products do not come out on vinyl record, and in terms of quality, there is no objective reason for that to happen.
However, if in your shelves crammed vinyl, with art rock, jazz or blues, you probably dream at least such a gramophone.
It is the same music for travel, namely compressed music to tell a simplified way - music in MP3.
Again, there are categories based on price and quality.
For one, it may be unacceptable to spend eight thousand crowns for a drive, the same way a fan of Pink Floyd would be hard to bear headphones bought for twenty crowns market.
These are two extremes, between which there is enough room for everyone.
The choice is wide.
The life of the batteries is also decisive
Some readers of premium music are capable of a lot more than a simple music playback, but this is of unknown function, of course, the most mobile.
No current device is as universal as the telephone.
Besides the primary functions, phone calls and sending SMS, it is able to play music and movies, save them, it has a camera of variable quality and may, for example, until to be used for navigation.
And if we take into account smartphones and communicators, you will have in your pocket a small computer.
Since no one knows fridge grill meat and no TV will take photographs, we see almost a miracle.
However, the universality of the mobile is not without drawbacks.
The more features you use, the greater the interval between charges will be reduced.
And reading music is one of the largest energy hogs.
Are few mobiles that are capable of playing music for ten to twelve hours, in most cases, this figure is much lower.
In this regard, music players (especially the most basic) are significantly more efficient.
In the case of mobile cheap, expect they will play music for a few hours.
If, in addition, you happen to call from time to time, get to be sure, a second charge for the job - this is true even for the more expensive units.
If problem does not arise for MP3 players, which are able, after a reloading, continuous operation of at least 9 hours, including underperforming.
Another problem occurs when recording music in the mobile.
Unfortunately, only a limited part of the equipment has a universal USB connector, especially since not all of them can be connected directly to the computer without special software.
One can, of course, record music directly on the memory card, but few card readers know to do it without reduction, given the tiny size of the memory cards used in mobile phones.
Regarding the players, you do not need, without exception (iPod), any software.
Simply fill through the USB connector, the music device from the computer.
Most mobile and readers will create a classified after the name of the artist, album title, style, or when in the judgment of the user library media themselves.
Some devices display an index with a tree structure, like the Windows Explorer, others are capable of two (iriver, Samsung, Sony, Cowon, smartphones with operating system).
Readers are easier to handle, mobile have more expertise
In selecting a specific device, you most interested in the life of the battery, the memory capacity, quality and type of sound output and, of course, ease of control.
If music is for you, essentially, a noise in the day and if you listen to that for a limited time, for example by taking the tram, just any mobile reading MP3.
Almost all mobiles are now able.
You do not even have to do too much attention to the music formats the mobile or the reader is able to read.
All come to play MP3 and the vast majority of the music that will be sent to you exactly what format.
It is one of the most popular formats and share it, the vast majority of devices also happens to play music WMA format.
The AAC (the format used by Apple company and iPods), meanwhile, is less common.
The high end mobiles also allow, for example, buying music online.
Just visit from the mobile phone, the corresponding web pages of the operator (or those of another supplier) and buy the song or album in question.
This service alone should be a compelling reason to get a musical mobile.
The offer operators unfortunately miserable and it is limited in most cases to radio tubes fast facts.
The prices are not the lowest.
Nevertheless, it is generally considered that this way of buying music (either GSM, internet, or even wireless internet) dominate the music industry in the future.
Most people are always on their mobile home.
Whenever you want to listen to something, you just get the mobile out of your pocket while you forget your MP3 player at home.
However, it is also important if you are still on your headphones or handsfree with a connection.
If this is not the case, you can use the built-in speakers that have virtually all phones, but a minimum of MP3 players.
For many, the main advantage of mobile music is their price.
Cheapest normally cost less than three miles.
For a price of four thousand three crowns, one can have a walkman already very suitable.
However, in most cases, you will be limited by the lack of output for ordinary headphones.
The price of the best phones and better equipped, also provided an input for ordinary headphones, does not exceed fifteen thousand.
Readers, by cons, have the advantage of having an easy drive.
Really anyone happens to ensure the control of the most basic drives - which does not necessarily correspond to the least expensive (see our choice).
A minimum of functions, and the similarity of the order with that of a cassette station, commonly used in the past, or a gramophone, is obvious.
There is no risk of collision as a mobile internet connected by chance, followed by transmission of a huge bill data.
Choose which device
Even the least expensive mobile (eg. 527 The Vodafone) usually has a slot for memory cards exchangeable (type M2, microSD, and so on).
Even taking into account the additional purchase of such a card, you will not exceed two thousand crowns.
But be careful.
The basic models do not support the principle that cards with a maximum capacity of 2 GB.
Only the most expensive fare even with memory cards of 8 GB.
If you already have a mobile phone and want to still buy a cheap MP3 player, take a Cowon, Creative one, a Sony, a Samsung, a Emgeton, or an iriver.
Depending on the capacity (max. 2 GB), you should not spend more than 1100 crowns.
If you are one of the most demanding listeners choose rather specialized mobile-walkman (Sony Ericsson, Nokia and some Samsung).
These devices are equipped with independent control keys for MP3, and thus the ease of control is similar to that of an independent MP3 player.
Sony Ericsson, the mobile of Walkman series have the same user menu as MP3 players sold separately, is the one who went furthest in this area.
The same service in the same price category, but with a memory capacity (up to 16 GB) and a life of the battery (usually 15 hours to 35 hours) above, is provided by a MP3 player produced by one of the brands mentioned above.
A first virtual operator win the Czech Republic this year itself.
Perhaps
The mobile market in the Czech Republic is relatively advanced, our operators offering almost the same services as their partners in Western Europe.
Despite this, we still lack something - a virtual operator, which would force traditional operators to lower prices.
It may not fail for a long time.
We have already mentioned repeatedly on Mobil.cz that Czech operators are among the most expensive in Europe.
The CTU (Czech Telecommunications Office), who reported that the price of an SMS was higher for us than in the rest of the Union, has confirmed.
Thus, following the last steps of the European Commission in the field of regulation of roaming charges, a paradoxical situation may occur - SMS sent from abroad will be for some customers cheaper Czech mobile operators that the country.
How is it possible that prices in the Czech Republic remain so high in comparison with Europe?
The answer is simple, there is no competition that would really get into the fight.
This may seem paradoxical, since we have still three mobile networks and penetration far beyond 100%.
Instead, mobile operators like to complain that the Czech market is extremely concurrenciez.
In this, Pavel Dvorak, President of the Council of the Czech Telecommunication Office (CTU), which has repeatedly said that the Czech Republic there was no room for another operator, chimed in with the operators.
It is probably true that classical operator with its own network apparently have much luck (by the way, now, he would find it difficult frequencies).
However, there is still a possibility - a virtual operator.
It is precisely the entry of virtual operators in the mobile market which resulted in a significant drop in prices, which were subsequently also react conventional operators.
Yet even before the entry of spoilers such as Tesco Mobile and Virgin Mobile on the market, similar to those we hear today among us suggested in Britain voice.
However, it appeared that there was still room for such operators and could be a real success.
We are also not required to have to look too far to find examples.
In February we reported the launch in Poland, the virtual operator Mobilking.
In just six months, the bank managed to win more than 100 thousand customers and become the fifth operator in the country.
Add that behind the Mobilking there Penta financial group, which has among others the U: fon Czech Republic.
The advantage of virtual operators is the ability to focus on a more specific target group.
For that to function effectively, they indeed need a lot fewer customers than a traditional operator.
They are, in effect, free of charges for construction, operation and maintains the mobile network, relatively high.
Thus in the world, virtual operators are emerging as low-cost operators - they offer calls and cheap SMS, which is often offset by a limited supply of services.
Eg Tesco Mobile offers, Great Britain, SMS at least two times cheaper than its competitors.
However, as the example of Mobilking Poland, rely on an unusual target group can also be a good publicity stunt.
Indeed, this operator is specifically men.
"Real men choose Mobilking - an operator who they like and whom they can trust," said David Seibert, CEO of Mobile Entertainment Company, which operates the virtual operator.
It is hard to say, if such a concept would be likely to also walk home.
Miroslav Cepicky 'spokesman Vodafone doubt: "The Czech market is relatively small for a segmental approach, which is based on the most virtual operators.
Especially since it is relatively saturated in terms of service delivery. "
Czech Republic, no chance, say the mobile operators
Nevertheless, it seems almost certain that it will be a virtual operator in the Czech Republic, it will not Mobilking.
"We discuss the expansion of this successful project, but negotiations in the Czech Republic are not very promoters.
The launch of Mobilking will rather take place in other countries in our region, "said in a telephone talks to Jana Mobil.cz Studnicková, spokesman for the financial group Penta.
It has indirectly confirmed that the operators in the Czech Republic were, in any case, not in favor of this idea.
Instead, they try to do everything possible for a potential competitor could not be produced.
The group GTS Novera, which would go a step further and to become a real competitor Telefonika in the field of business customers, do not hide long enough, its intention to launch a mobile virtual network operator.
"We are keen to be able to offer our customers not only fixed telecommunication services but also mobile.
And the sooner the better.
We have already held talks about this possibility several times with all Czech mobile operators.
With some, we were able to progress in the negotiations, "said the spokesman Pavel Kaidl group.
The future is perhaps promising.
According to unofficial information, it seems that we might be able to host the first virtual operator already by the end of the year.
But for now, its creation is accompanied by total silence.
"Right now, we do not believe that there is room on the Czech market for a virtual operator as such.
The Czech market is in comparison with other very specific.
For the moment, no subject provided a serious and complex project in this area has not contacted us, "stated Vlastimil Srsen Department Press Telefonika O2, in his statement to Mobil.cz.
Other operators are also related to the specificity of the Czech market.
The spokesman for T-Mobile Martina Kemrová says in a rare agreement with the statement of O2: "We have not registered yet viable and advantageous bilateral project, which could serve as a basis."
And she adds: "It is virtually impossible for a virtual operator appears in the T-Mobile network by the end of the year.
To operate in a limited period of time, we should now have a concrete agreement. "
Vodafone directs his attention instead on completion of requests for its own 3G license.
Miroslav Cepicky 'said against it: "We are open to negotiations with potential virtual operators, especially in the field of infrastructure and shared costs.
This is what we believe means more contributions from the perspective of customers.
The main strategy of Vodafone in this area is finding a partner to establish a common network for a fast mobile internet. "
Responsible authorities: in line with the operators
The approach of mobile operators is easily understandable, the input of another operator would mean increased competition, would led to lower prices and therefore to reduced profits.
What good is therefore to facilitate the achievement of such a competitor?
When it comes to their interests, operators know how to listen as thick as thieves. The baffle accompanying the creation of the U: fon also evidenced.
The apparent greater pressure on the CTU during the creation of the U: fon, was that exerted by T-Mobile.
Evidenced by publicly available information from the web pages of the CTU.
Today, however, the U: fon is ready to serve as an argument for not accepting a virtual operator.
Martina Kemrová noticed about it: "Competition in the mobile market has been more recently enhanced by the entry of a fourth mobile operator.
Given the nature of the mobile market in the Czech Republic, it is clear that the entry of an additional player would submit, and especially its services to high standards. "
But given the attitude of the mobile operators here, the indifference of the Czech regulatory agencies seem disconcerting.
It is however not only the attitude of the CTU, which, unlike Britain and other developed countries, has not, unfortunately, the Czech Republic, the power to intervene in economic competition.
It belongs exclusively to the Office for the Protection of Economic Competition (ÚOHS).
But it passed, deal with this problem, its typical position.
"The entry of a virtual mobile operator on the market would be possible after the conclusion of an agreement between a mobile operator and the virtual operator in question concerning the rental of the necessary infrastructure.
No such agreement has been reached yet, because the supply of potential interest is a priori not shown enough interest to traditional operators, "said in response to our question Kristian Chalupa, Department of External Relations ÚOHS.
A declaration made so do not be surprised by representatives of operators.
But from an office, which must represent the interests of consumers and among other also take care that nobody takes advantage of its market position, such a statement is more than confusing.
Especially since Kristian Chalupa adds: "In other countries, where MVNOs are normally present, we can see that their entry into the market has contributed to a decline in prices of mobile telephone services."
Now push in the direction of an honest functioning of the market and lower prices does not seem part of the interest of ÚOHS.
It is actually shocking is almost touching harmony of the three mobile operators, resulting from their reactions.
The question whether this is really a chance, naturally arises.
Similarly, the price of gasoline strictly identical for all service stations is probably due to chance and hard fought competition.
"The Office has not identified, about, signs of anti-competitive behavior, so it has no reason to intervene in one way or another.
No operator has a dominant position, none has therefore increased corresponding responsibility for his behavior on the market.
The tools needed to open mobile market to MVNOs probably lack even telecommunications regulator, "said in his statement Chaloupa.
The interpretation of the dominant position on the market is one of many points of contention.
Of course, there is a relevant market analysis prepared by the CTU, that telecommunications is the point of view of economic competition, a single market.
None of Czech operators has a dominant position in this market.
However, some law experts offer another vision: that the creation of a virtual operator is possible, obtain, whenever the consent of the network operator.
And mobile operator logically monopoly on its network.
Thus it must play a dominant role in a certain segment of its business role.
But even without accepting this argument, it should be less disturbing for ÚOHS three mobile operators carry visibly in a similar way.
However, complaints from many stakeholders (including the company GTS Novera, already mentioned) show they face in negotiations with all operators, similar constraints.
Put the blame on the CTU is a fairly common trick in communications, whereby the ÚOHS washes his hands of the matter.
We have already encountered this type of attitude in several similar cases.
It has unfortunately failed to pass in the novelization of the Telecommunications Act, recently passed an extension of the powers of CTU in the field of economic competition in telecommunications, although many experts promised improved position.
That representatives ÚOHS should very well know, but their interests are apparently other.
When nobody is looking, it can work
However, the operation of a kind of virtual operators nickname, many in the Czech mobile networks remains unnoticed.
These companies publishing their own price list of mobile telephone services, but these are only public part.
In most cases it is a question of companies dealing with the multi-level marketing.
Particularized of mobile telephone services are proposed for example by Amway, Bohemia Telecom Starlife and many others.
Price lists of these firms are usually able to elected officials.
The trick lies in the fact that the company to the operator of a typical enterprise customer who order a large quantity of SIM cards figure.
As a valued customer, it gets quotations (and other) special.
The problem is that the commercial terms of all Czech mobile operators prohibit such resale.
"If it happened that you mention, it could be a breach of contractual terms that we would consider and that could lead to a judgment of the collaboration with the company in question," answered our question on Martina Kemrová this problem.
Nevertheless, it is quite unlikely that echo such activity is not reached until officials mobile operators.
Especially in the case of the three companies he mentioned may be thousands of customers.
No huge operator, however, did say against such a procedure.
Indeed, the activities of these firms provide their non-negligible profits, and at the same time, as opposed to true virtual operators, they threaten their own with no formal marketing.
Miroslav Cepicky indicates possible problems: "The law allows such speculation, however, the services of these companies are used by a significant percentage of customers.
In addition, they are forced to admit that the SIM card in the phone is not registered under their name, they therefore can not fully dispose of, like ordinary customers mobile operators. "
But it is precisely this which should seem strange to CTU.
In addition, there is another question ÚOHS.
If mobile operators condone such a procedure, why do they block the creation of a virtual operator?
It should be added that the ÚOHS has relatively broad powers in order to reveal such activity, and does not wish to settle for explanations of operators, who say they have no idea that this would happen, their contractual terms prohibiting .
When we are no longer the most expensive country
As we have already mentioned several times, the virtual operators entering the mobile market has brought a considerable decline in the price of services.
However, in almost all countries where MVNOs appeared, traditional operators tried, sometimes more, sometimes less, to prevent their creation.
The arguments used by them were virtually the same - too small a market, or too saturated, problems with the quality of services, etc..
But it is precisely at this level that have occurred in developed countries, regulators, not defending the interests of mobile operators, but those of their clients.
Both through formal action by informal pressure, they ended up getting the creation of a first virtual operator, followed by others.
Unfortunately, the Czech regulators treat this issue like a hot potato which is discarded by passing to a nearby target.
Following the experiences we have, we can not escape the impression that the confusion in their skills in these cases is more than profitable.
But do not throw the helve after the hatchet.
If the information are true and slide a virtual operator will soon appear here, the Czech mobile market may be becoming mobile.
If one of the operators accepted the creation of a virtual mobile operator, the ÚOHS can only hardly remain indifferent to rejection (discrimination) and other stakeholders.
And maybe we'll stop calling more expensive than in the rest of Europe.
The new Czech anthem has four new versions.
Choose the best
Listen to the four goals of the new version of the Czech national anthem.
Sunday, on the occasion of the Day of Czech nationality, Prime Minister Mirek Topolánek solemnly presented the new recordings of the national anthem Kde domov mu ˚ d (Where is my home?).
The anthem was again recorded by the orchestra of the National Theatre under the direction of Jirí Belohlávek.
We have four versions - with a male or female solo singing, choir and an interpretation with an instrumental version.
The song is performed by Katerina Knezínková and Adam Plachetka.
Otakar Jeremiás and Jaroslav Krcek are the authors of the hymn arrangements.
You can listen to four new versions on the server iHNed.cz.
Belohlávek considers the Czech national anthem as one of the most beautiful hymns.
As he had previously given to Cesky 'rozhlas (Czech public radio), he chose to interpret the solo versions with young singers and representative voices, which are marked and appreciated.
"From the beginning, I tried to take care that the two singers and the choir have good diction, so that one understands the lyrics they sing simultaneously," he said.
The Czech national anthem will celebrate next year's 175th anniversary.
The song Kde domov mu ˚ j sounds for the first time in 1834 on the boards Estates divadlo (Theatre states) in Fidlovačka (Kermesse cobblers), original piece of Czech Josef Tyl Kajetán, accompanied by the music of Frantisek Skroup.
It became popular and people have spontaneously appropriate.
After creating the Tchécoslaovaquie in 1918, the first verse naturally became part of the national anthem.
He remained one of the seven national symbols even after the establishment of the independent Czech Republic.
How sounds the "new" hymn
Public transport (MHD) introduce Prague Wednesday, the chip in their ticketing system
Wednesday, October 1, 2008 will be recorded in the history of Prazsky 'Dopravní podnik (the Prague Transportation Agency) as the date on which ascend in the subway, trams and the first passenger bus, which, instead of having a paper ticket will have in their pocket, an electronic coupon.
At this moment, it is available for about one hundred thousand people, the owners of the smart card Opencard.
Passengers can purchase a coupon 30 days or 90 days (it will be valid from 1 January 2009) and both to register on their smart card in information and offices Dopravní podnik point (the Agency of Transportation), located in the Muzeum metro stations, Mu ˚ stek, Nádrazí Holesovice Andel Roztyly, Letnany, Kobylisy, Rajská zahrada, Kacerov and Luka.
From yesterday, there is also the possibility to buy the coupons on the internet web pages Dopravní podnik: www.dpp.cz.
More than four hundred people took advantage of the service in the morning.
Those who begin to use the online store can forget permanently counters in subway stations, where they were far trampling impatiently in long queues in order to obtain paper tickets.
In fact, they buy their coupon on the internet and save on their Opencard card in one of the thirteen Mestská knihovna (public libraries).
"In these points contact, there is available to the passenger window with a trained staff that will help interested with the purchase through the Internet and, in addition, save the coupon they bought on their cards," says spokesman Martin Opatrny project '.
Besides the libraries, it is also possible to record electronic coupons on Opencard in vending machines in the lobby of several subway stations.
What distributors like these?
They are red, remind machines compost tickets and the passengers may have already noticed in the metro Roztyly, Budejovická, I. P. Pavlova, Florenc Vltavská.
"Today, the city has five, but by the end of the year, there should be eighties," added Opatrny '.
A PLC control the coupon to the driver's seat
Controllers that will operate from tomorrow, are easy to use.
Simply insert the smart card and coupon Opencard previously purchased will register itself on the map.
Electronic coupons are valid from tomorrow not only in the capital but also in the vicinity of the city.
Namely in suburban trains and bus lines 300 to 499, mainly used by the inhabitants of the towns of Central Bohemia to access capital.
"In the integrated Prazská integrovaná doprava (Prague integrated transport) trains, controllers are equipped with card readers, with which they establish temporary zonal validity of coupons," said the ticket control of Filip Drápal Ropid organization that designs schedules transport Prague.
The suburban buses are equipped with readers integrated into the body of the driver cards.
When boarding it is necessary not only to show the smart card driver, but it is also the place Opencard where indicated on the side of the box.
Thus, the driver checks the validity of the registered coupons.
"If the passenger would need to check the validity of coupons saved, there is nothing easier than to request such information to the driver," Drápal completed.
Passengers who do not take the suburban buses and will not remember the date when the validity of their coupon expires, can rejoin the vending machines initially used to store coupons on the map.
It was there, on the screen of the device that will display information about the validity of their document.
Sudeten demanded a referendum in the U.S.
Sudeten Germans demanded in 1945 that Sumava is integrated in the United States.
This follows a letter deposited in the collections of the Jihoceská vedecká knihovna (Scientific Library of South Bohemia).
If we can not be part of Germany or Austria, we at least want to live under the patronage of the United States of America.
In 1945, some of the Sudeten Germans groups allegedly addressed to the President of the USA with such a desire.
This stems from another letter preserved in a private archive, which is now deposited in the collections of the Jihoceská vedecká knihovna.
Germans Cesky 'Krumlov pray in the letter U.S. President not to allow "Šumavská zupa" (area of ​​forest in southern Bohemia) - annexed by Hitler under the Munich Agreement - is made in Czechoslovakia .
"We understand the situation and want to be really sure that the words proclaiming that American troops are in Germany not as oppressors and enemies, but as liberators," says the letter, signed "People, that the fate the Sumava wishes to heart. "
Since rallying Czechoslovakia is allegedly promising - knowing the Czech national character - that brutality, inconsiderate attitude, misunderstanding, oppression and servitude, the authors of the letter request the President U.S. to take in his hands the protectorate of Sumava for now and forever.
"We can not believe you would give this land to a stranger to us state that oppresses and kills minorities and has contributed nothing to the Allied victory without taking into consideration the opinion of the quarter of a million inhabitants , "is written in the letter.
The alleged reason for the authors can not sign the letter is the fear of vengeance of "Czech oppressors."
If the U.S. president questioned the opinion of Germans Sumava, it would only hold, according to the authors of the letter, a referendum in the region to determine if the people wanted to be part of the USA, or live under the patronage of the United States.
Although the text contained in the letter is, given the current knowledge of the history of post-war seem somewhat naive, some survivors, it illustrates the expectations of the Sudeten Germans at the time.
While the Czech Germans had at least foresee that the issue of the expulsion of the republic lay very few of them admitted such a possibility.
Some expected that the United States and Britain were going to get for a certain type of Sudeten autonomy.
Others believed they simply remain in Czechoslovakia.
The famous Austrian journalist Gustav Chalupa, born in Ceske Budejovice, agrees.
During the war, it was, as a German Ceske Budejovice, joined the navy in the Baltic countries.
When at the end of the war, he was captured by the English and placed in the camp capture the Holstein region, dozens of Czech Germans came to consult so that they learn Czech.
"They believed that once they return home, they would benefit from the Czech" said Chalupa.
None of the captured Germans who lived in Czechoslovakia before the war felt, he said, that, following the Benes Decrees, he would be expelled from the republic.
You do not think - you pay!
An emotional campaign attack drivers
The action the most expensive road safety in the Czech history.
One way to characterize the emotional media campaign that intends to launch on Wednesday, the Ministry of Transport.
The Office of the Minister Ales Řebíček believes it will discourage drivers from dangerous driving behavior.
This campaign cost 150 million appear on television, radio, cinema, internet, but also leaflets.
It should discourage drivers from driving fast and drunk driving.
But also remind them to take the belt before starting.
She especially wants to touch the conscience of young drivers, motorcyclists, pedestrians, not to mention professional drivers.
Which appear in the spots?
Especially personal stories that will attack the emotions.
Also evidenced by the "bloody" slogan throughout the campaign:
You do not think - you pay!
The phrase "You do not think" is written in capital letters on the license plate.
Then, in a pool of blood, there is the phrase "You will pay."
What should symbolize that we can pay life a moment of inattention.
The spots will "haunt" the audience until 2010.
The ministry is inspired by similar campaigns in Anglo-Saxon countries, where you can commonly see images with dramatic images of victims of accidents.
He believes this will reduce the rate of accidents and deaths on Czech roads.
The spots were produced by Euro RSCG.
The strategy of sugar and whip against drivers
"What works with the drivers, the system of sugar and whip.
For them, the sugar is shown, for example, by the fact to save time when red lights.
The whip is the threat of a fine or an accident.
Risks should be recalled drivers, "said Martin Koran, psychologist transport of Na Homolce hospital.
Thus we need information campaigns in the media and especially the negative ads, says the psychologist.
The signs indicating the danger to drivers, according to him, already less effective.
"When a static sign that warns against danger is installed, it will probably soon merge with the environment and the drivers will notice more," pointed Koran.
Olmert would in exchange for peace almost all occupied territories
Ehud Olmert, the Israeli president of the provisional government, ruled in favor of the return of virtually all territories occupied in 1967, thus including the West Bank, East Jerusalem and the Golan Heights in exchange for peace with Palestine and Syria.
He made this statement in an interview published Monday by the daily Yedioth Ahronoth.
"We have to reach an agreement with the Palestinians, which means it will be necessary to make almost all the territories (occupied), if not all," said Olmert daily.
"We will keep a certain percentage of the territory, but we will give the Palestinians a similar percentage (Israeli territory), as without it, peace will not happen," he added.
He admitted that the restitution can include East Jerusalem.
"Anyone who wants security in Jerusalem, and especially does not want tractors and bulldozers crush her feet, as happened to one of my best friends, will relinquish parts of Jerusalem," remarked Olmert referring to two attacks in the city in July, during which several people were killed and dozens injured.
According to the Prime Minister, it will be necessary to find "a special solution for the Temple Mount, sacred and historic sites" located inside the Old City.
"Whoever wishes to maintain Israeli sovereignty over the entire city will be forced to integrate 270 000 Arabs.
It will not work, "he pointed out later.
Retreat from the Golan Heights
Olmert also spoke in favor of the retirement of Israel from the Golan Heights, which is, according to him, an indispensable condition for the conclusion of a peace agreement with Syria.
However, this would also require some effort on the part of Damascus.
"I do not propose to make peace with Syria only on the basis of a retreat from the Golan," he pointed out.
"The Syrians know very well what they will have to give up to get the Golan.
They will have to give up their current relations with Iran, they will have to give up their relationship with Hezbollah (Hezbollah), they will have to give the constant support they give to Hamas terrorism (Hezbollah) to Al-Kaida (terrorist network), as well as that of Jihad (holy war) in Iraq, "the Prime Minister clarified.
Questions that arise after the accident: The stewards in because they are illegal?
The law ignores, walking in a long-distance bus is prohibited
In the context of the tragic accident of the bus company Student Agency near Padua, Italy, the question arises whether the stewards and passengers during the journey can move inside the bus.
"If we wanted to enforce the law strictly and formally, the activity of a steward is contrary to the law on road traffic," said the spokesman of the Ministry of Transport Karel Hanzelka.
The accident, which was lost during a 22 year old hostess, was apparently caused by the driver of a truck that crossed the path of the bus.
The girl was at that time unfortunately sitting next to the driver on the most dangerous of the vehicle seat, although it has at its disposal two other seats.
However, the coach can have an accident or stop abruptly, also when the steward serves coffee or distributes newspapers.
What matters is whether the coach is under the technical sheet with standing room or not.
If this equipment for standing passengers is not approved, passengers must remain seated.
Long distance Student Agency buses do not have standing room, which was confirmed by the aktualne.cz company director Radim Jančura.
"This is an issue that we dealt with the department at the beginning, he forbade any movement of passengers.
Then they canceled and we got that passengers can go to the toilet during the journey, provided they have their own seat, "he revealed his position.
The law ignores the steward
"There is no univocal legal interpretation of the role of steward - no legal requirement not responsible for this role.
On the other hand, no legal requirement does not prohibit the carrier to provide services.
The law on road transport only knows the term Catcher vehicle does not define their rights and duties, "adds more ambiguity spokesman Hanzelka.
Josef Pokorny ', director of the department of vehicular traffic, said, however, that the law sufficiently address the problem.
"Everything depends on whether the coach has in his approval permission to offer standing room.
Everything lies in there, "he said.
Coaches are divided into urban, where there is standing room only and a limited top speed, long distance with standing and permitted higher speeds and long distance bus without standing up with the maximum speed and the highest seats fitted seatbelts.
As the plane, said an expert
Jaroslav Horin, expert BESIP (traffic safety) in transportation security, did not see the movement of the stewards on board as a major problem.
"In a regular flow, there is no danger. Situation can be compared to that service in the aircraft.
Again, it is not sure when to produce turbulence and air hostess can bump your head. "
"However, if the coach would have braked abruptly, the laws of physics would obviously valid.
In the same way that a city bus or a tram.
The carrier must manage security stewards by internal regulations, "he said, and also believes that the point of view of the law, the issue is not resolved.
Jančura is ready to remove these services
Student Agency bus is the only carrier to offer the services of stewards.
He hires two percent.
Even after the accident, the Director does not consider their job as a profession at risk.
"However, as soon as I feel it is a risky business, I sweep away.
Passengers can get their coffee and newspaper boarding.
This would also reduce costs, "he said.
The concern for safety is the reason given for the absence of stewards in its vehicles director of Asiana Alexey Litvin, which provides, in comparison with SA, a very small number of lines.
"We do not have hostesses. We are opposed from the beginning.
Sooner or later it will end in a fatal accident, "he said, a year ago, to Ty'den cz..
A great tragedy happened
A young hostess of the Plzen region, who worked for the company for two years, died in the accident on the line of Naples.
A Slovenian truck probably antiquity the emergency lane without using a turn signal and it blocked the way to the bus.
The driver of the latter to try to avoid using a sudden maneuver, but it was grazed by the right side.
Jančura refuses the two seats reserved for rest stewards were sold.
"In the case of long distance lines, it is not possible to book these places, they are blocked."
The company has a complaint against the truck driver.
For compensation to the family of the girl, the agency does not wait for the judgment of the court, but in terms of financial compensation, it also relies on the culprit.
A change in the law?
Not to
A change in the law, which is being developed for more than a year by a group of thirty experts from the Department of Transportation, could provide clarification on the movement of stewards on board the bus.
"But it did not lead to any conclusion on this point.
Actually, it is not too interested in the bus, but the points system, the maximum speed on the highway and the use of mobile while driving, "said the expert Horin.
"The Department of Transportation does not consider the activities of stewards as something that would fundamentally threaten the safety of passengers," concluded the spokesman Hanzelka, indicating that the control bus safety is under the power of police and the office for safety.
The hopes of Düsseldorfois based on Frankfurt.
Big words were not lacking in the letter from the Director of WestLB employees home committee.
By a union of the entities of the financial institution in Düsseldorf with the Deka-Bank in Frankfurt, "the central institution of the financial markets of the Sparkasse financial group" could in the mail to be released Monday,.
WestLB bring a "block skill dubbed" sustainable productivity in such a case.
After all, such a relationship could be decisive kick sending to other levels in the banking sector of the Länder.
Here is what it looks like when the Executive Committee wishes to demonstrate its ability to act in difficult times.
For WestLB injured, still is under pressure.
It is not only the Commission but also the Federal Supervisory Authority for Financial Services that, it only recently made it clear to the state government of North Rhineland-Westphalia that time was running out in the search for a future solution.
However, it is matter for some time - also on the side of Frankfurt - a relationship of any kind between the Deka Bank, who knows the customers by Sparkasse their investment funds, and WestLB.
While the head of the Deta-Bank Franz Waas reported in the presentation of figures for the six months late August he saw no sense in merging the house Mainzer Landstrasse with a bank of Land, be it Helaba and WestLB.
However, the Board of Deka, each half is supported by the banks and the Länder and by groups of savings banks, asked the steering committee to conduct talks with WestLB for common business .
Then it could be the speed of the financial market, or parts thereof.
The talks come just begun however, they say in the financial sector.
This is not the first time that Deta-Bank, which, with its 3,000 employees, account for one of the largest employers in the financial center of Frankfurt, comes into play If is question of industry consolidation savings banks.
In 2003 it was believed for a moment that Deta-Bank could merge with Bank of Rhineland Palatinate and Halbab.
Nothing has yet emerged from this ternary bouquet.
Just the plans had they been made public that the government of Hesse was against any participation Hellaba therein.
Subsequently, two other houses either are not rejoignèrent.
Bank of Rhineland Palatinate was attached instead to the bank of Baden-Wuttenberg in Stuttgart.
But there were always new negotiations on the consolidation of the Deka-Bank with banks Länder.
Finally, Günther Merl, Chairman of the Steering Committee Hellaba, however, had decided against any commercial fusion strategy with its bank.
Regardless of this, the feeling seems to be spreading that the combination of different public sector institutions is particularly urgent.
Now that the election to Parliament of Bavaria passed a union with the BayernLB bank of Baden-Wuttenberg could materialize in the first.
For Helaba is not particularly good news.
If the pressure requires further mergers would increase potential partners beyond him gradually.
In the South, it would become a junior partner, although it has so far weathered the crisis better than banks in Munich and Stuttgart.
The group savings and transfers of Hesse-Thuringia, which owns 85 percent of the capital of Helaba fund, on the other hand shot a bolt at the beginning of the year on any union with WestLB.
Remain the rigor NordLB.
Such geo-strategic considerations, however, reflects only one aspect.
Another aspect raises the question of how different business models of each of these banks can match.
In June, Merl said that the decisive question as to what business model with the future ability of banks Länder should be ensured, had not previously been addressed by the German group of savings and cash transfers.
Eventually, a dismemberment of WestLB could take place, butchering that here is obviously not desired.
It is also referred to it in the letter of the Executive Committee in place: in any case, would be covered a `comprehensive solution 'to the institution.
How all this will be put in the same basket with the union of certain entities with Deta-Bank remains to be seen.
The second weekend of Oktoberfest is also known as the weekend of the Italian.
For Elena, it's the first time for Luca already the third or fourth time.
But this time, Elena comes as a girlfriend, and therefore nothing is the same, he said.
Behind them, near a five-liter barrel of beer from the Kaiser brand, is a well-built bearded shows about 200 visitors to the Oktoberfest which sounds deep her throat may occur.
Elena Luca tape first, then kisses her.
Bologna, they came to Verona.
From there, the bus station near the train station Puorta nueva, four buses are leaving tonight at 23:45, `destinazione Monaco, festa della birra 'arrival at 6:30.
Three buses are reserved primarily for Italian in a bus traveling from brésilens exclusively.
In a corner of the parking lot, the South American singing golds already beside their flag, they have already celebrated last night.
And loud, explains Marco Guarda, it is not for the Italians.
The bus belongs to Marco, who wears a long coat lined with faux fur and glasses with large silver mounts.
For five years, they go to the Oktoberfest, already three trips this year alone.
They go at night, stay the day at the party, and go to 22:30.
Y overnight involve unnecessary costs, says Marco.
The trip costs 75 euros, including welcome drink with Kaiser beer brewed according to the Bavarian Purity Law, health insurance and an official of the German speaking group - Marco did a language course in Frankfurt.
And already the buses run at night on the Autostrada towards Brenner `'.
There is no beer, not yet.
Quickly, everything becomes quiet in the bus, passengers sleep.
It's better this way, they will still need their forces.
Breaks will be made in Bressanone, and Holzkirchen, while many other buses with Italian registration plates are once again a little break before Munich on Highway 8.
When in the morning, the group finally arrives Marco at six thirty in the parking lot as planned near Theresa Place, about 50 other buses from all over Europe are already there.
Elena, Luca and other congregate, Marco is a last speech, explains the plan of attack.
Firstly, her hair of the little yellow cap.
Above is written left to Oktoberfest 'in Gothic, and beside the IP address of the travel agency Marco `conoscersiviaggiando.it".
Second: `When the doors of the big beer open, we run 'cries Marco in the early morning.
`Run! ' Running and reserve seats at the back of the tent.
`Not in front, otherwise it crashes, and not all the yellow caps on the same bench, we must divide the room! '
The mug, shouts Marco, costs 8.25 euros.
And do not forget the set!
Show `security guards that we behave well!
Once you leave your seat, they left! "
Third: `Tonight be back here at ten and a half stack! ' Included?
And that's it, let's go to Oktoberfest.
Along the way, someone forges yellow caps trees to find the way to the panels and even an election poster of a large Bavarian People's Party.
It wants to be ready for the return.
This is the second weekend of Oktoberfest, known as the `weekend Italian '.
There are no precise figures, we are talking about 50,000 who set off across the Alps and collapse in the beer stand, 10 percent of visitors would come to express Italy this weekend.
The Munich police is reinforced by seven police officers of South Tyrol, in the Italian volunteer rescuers who support the Bavarian Red Cross which carries a statistic on the country where the Italians are in first place ahead of the UK (60 procedures) and Austria (about 80) with nearly 200 medical interventions.
One that is particularly popular with Italians, it is trying the brewery Hofbräu.
Sleepless nights for the shareholders of Hypo Real Estate
The German banking system is relatively stable, insisted the Federal Minister of Finance a few weeks.
How fortunate that the politician used the word `relatively 'and he slipped the German banking sector would not be spared by the movements of crisis.
This is indeed occurred this weekend.
Financial Real Bavarian Hypo Real Estate (HRE), the DAX side, gets a consortium of German banks a credit of one billion to protect against market turbulence.
A person in the know of the situation told Reuters on Monday that aid funds are awarded to a total of € 35 billion.
The Hypo Real Estate will now pay interest on the portion to which she would have the right.
The money comes from both private banks as public banks.
In the background is the company Depfa girl who bears the losses.
The financial statement was, according to a newspaper article, refinanced short-term for long-term projects for which he had borrowed money - which is no longer possible because of the distrust markets.
In the first half of 2008, the cash reserve of the bank was reduced by 95 percent to € 2.37 million, the rate of equity capital also had weakened slightly from 1.6 to 1.45 percent.
The profits from ongoing and net financial transactions were compared to the same period the previous year, fallen to zero, profits from the allocation of debt securities and fixed and the termination provisions in credit operations fell by more than 70 percent to 5 million.
And it is only thanks to the large profits of cost reimbursement accounting downstream from the restructuring of the former Depfa group, as well as interest payments according to the Book of Tax Procedures and commercial purchases for companies Konzern the deficit gains about 16 percent turned out to be moderate.
After its privatization in 1990, the former financial status had initially speculated badly on industrial property loans, which then were subsidiarised to Aareal Bank.
Because what the classical state funding was not profitable enough, the Depfa was then engaged more intensively in infrastructure projects and financing of joint projects between private investors and state (Privat-Public-Partnership , PPP) and internationally diversified.
On the value of the company-daughter, Hypo Real Estate to provide for depreciation that should have on the calculation of gains and losses of the group an essential material effect still remains unclear.
The fact is that the dividends were cut.
Already in 2007, they were truncated to two-thirds.
Hypo Real Estate, since the acquisition of Depfa, a state investor and infrastructure highly important.
It is stronger than other institutes dependent on refinancing since the inter-bank market has no deposit customers.
With the bankruptcy of the investment bank Lehman Brothers two weeks ago, the allocation of funds between banks has dried up considerably again, banks have accumulated liquidity.
Hypo Real Estate needs annually for a part - about 50 billion euros - of all credits Depfa an average short-term refinancing.
According to a statement of the Hypo Real Estate, the borrowing of the group is covered with medium-term credit and business protected from the influence of international financial markets largely incapable of walking today.
Other sources say that refinancing would be provided with funds by the end of 2009.
The President of the Executive Committee of HRE Georg Funke explained, however, that the Hypo Real Estate Group will no longer have to resort to financial markets in the medium term.
The Federal Reserve Bank and Federal Institution for Financial Services Supervision (BaFin) assume that the ability of the Group Hypo Real market is now assured.
Shareholders and creditors of the bank have more than hope.
However, given the dynamic and weightlessness of the crisis, there is no certainty.
It is also not inconceivable that we should not use the funding to its full extent.
But the opposite can no longer be dismissed.
After that the bank is, according to the latest news, even to the gates of insolvency late Sunday evening, the rescue at least provisionally will fail to reassure rather than spirits.
The share price collapsed by 75 percent to 3.30 euros.
Bond prices, however, are doing particularly well.
While debt primarily have barely budged, the prices of second-ready flex.
Most affected are mainly investment funds of the former Hypo-Württemberg girl and of course those who have a life beyond 2009.
The obligations of the bank Hypo Real Estate previously seemed to be an investment alternative speculation, their value must now be considered as dependent on the stability of the international banking system after the net tightening of the banking crisis and the crisis of the same institute that has brought the crisis in the establishment by the acquisition of Depfa Bank.
As the issuing institutions, governments and less affected commercial banks are still willing to support the system, we can assume a reduction of arrears in time.
Or happen that no hope at the moment - that the financial crisis can be overcome in the next 15 months.
But faced with noise renew a partial nationalization, the probability approaching the safety has now become a mere expectation based.
This book should sleepless nights primarily to long-term creditors on the decision of whether they should be separated from their commitments.
The short-term investors can still use it on what they have drawn a line to form a loss carry forward for the next year on the next income tax on capital gains in the stock automatically removed.
Sylvana and the secrets of the box Bento
When Sylvana Hiltrop, 16, must be present for the first day at Highschool Tachibana, girls begin to giggle: the German is so "kawaii!"
What does that mean?
Sylvana already knows the word through the Manga - Log in his new trade, she speaks Japanese.
"The first day of school in Japan.
What-I was excited.
Already the way to go to school scared me.
I live on the outskirts of Tokyo towards Kawasaki and I took the train 40 minutes until the Highschool Tachibana.
I can find the way alone, fortunately I am not lost.
The beginning of the course does not seem to be set as strictly as at home in Lower Saxony.
Students appear one after the other from eight o'clock until at eight forty, a round begins with the teacher, "home room."
But before the course starts, it was up to me to introduce myself.
I'm not at all the kind of love speaking in front of people, especially in front of a class of 40 students.
As I had not yet the school uniform, I put an old skirt of my host mother and a shirt, blue knee socks and black leather shoes.
In this outfit so I introduced myself to the desk, and tried everything correctly pronounce 'Sayonara Wo she Sylvana ...' - My name is Silvana, I'm from Germany and my birthday is in a week.
At that time, I was very happy to have started to learn the language well there two years.
The 31 girls in the class all made whispering, chuckled and waved, and I constantly hear the word "Kawaii".
I already knew through my manga.
It belongs to the vocabulary essential to the survival of Japanese teens and means "cute, cabbage."
Then I quickly slipped my place.
The girl next to me gave me a big smirk, she thought it was an honor that the same should sit beside her.
The rest of the time was pretty quiet, but when the bell rang, I was assaulted by the rules.
Everyone spoke to outdo, burst out laughing and asked me many questions - in this case, it is quite difficult to understand the English Japanese.
During the break, then they all got their Bento.
My host mother had also made me kind of Lunchbox - it really is something else than the miserable German snacks.
I had rice with herbs, sausages, cucumber salad and seaweed, fruit and some kind of meat surrounded by Tofu.
Most of the time, I have no idea what exactly I eat here in Japan.
Things have a weird look and a completely new taste.
What is certain is that everything is really good.
Well, except maybe the salty pickled plums, brrrr!
The Bentos are not only lunches in Japanese schools.
Sometimes a girl gives a boy a Bento she prepared herself, and it is prepared especially carefully - in the hope of making a little better knowledge of the boy during the break.
I read it in my manga.
I'm curious if I could also observe here.
"Why Japan in particular?" my friends asked me when I told them I wanted to spend a year at school in Tokyo.
So I always answered:
"Because it fascinates me, what"
Ultimately, reading manga, this is what I prefer for years already.
And to better understand manga and culture found there at a time, I also started to learn Japanese.
For me, it was really clear that I had to travel a day.
Because I also have a weakness for the traditions, habits and customs.
And here they are given much importance.
On the one hand, Japan is the land of technology and the latest trends - on the other hand, it is tough, disciplined and traditional.
And because everything is so well organized, I've never felt lost here, even if Tokyo is the biggest city I've ever seen. "
Rats also have sensations
A rat or a cockroach flee the danger is that, does that mean he also feels fear?
The neurophysicist Joseph LeDoux is convinced that many animals also have feelings.
But how can we check that feel the same way when it acts in the same way as we do?
In the online magazine "Edge", contributions are published for many years by famous scientists.
SPIEGEL ONLINE presents a series of articles in response to the question "What do you think to be true without being able to have proof?"
I believe that animals have feelings and other states of consciousness without me or anyone else has so far been able to prove just as we can not prove that other human beings have consciousness.
But in this case, we can at least hope that all human brains have the same configuration.
When we turn to other species and that we address the issues of feeling or awareness in general, we enter into impassable because the hardware does not match fields.
When a rat is to a danger, it is the same as many other animals: it's dead, fled or attack.
Humans behave the same way, which is why some scientists infer a subjective experience comparable.
However, I do not believe it.
Two aspects of brain structure makes the implementation of our subjective difficult than the animals lived.
One aspect is that the circuits almost always associated with human consciousness include the lateral prefrontal cortex (because of his involvement in the short-term memory and executive functions and performance).
This vast area is much more developed in humans than in other primates and appears to be entirely absent in other beings.
Least so for these latter aspects of our consciousness that depend on the prefrontal cortex, including the awareness of who we are, and the ability to predict and decide it is reasonable to assume that human beings are different from the same other primates.
Another significant feature may lie in the linguistic nature of man: a large part of his life being related to language, this often means that consciousness depends.
In this case, we could exclude animals.
But even if consciousness should not depend on the language, it's surely influence, so that the animal consciousness, regardless of how it is produced, probably differentiates a lot of most of our states of consciousness.
This is why it is difficult to determine what it's like consciousness in other animals.
If this internal and subjective, can neither be measured nor because of this particular hardware, analyze, based on our own experience, then its observation presents us big problems.
Most of my developments refer to the contents of conscious experience, but there is next to another aspect of consciousness that should be more easily accessible scientifically.
One could examine the processes of consciousness of animals regardless of their content, and that is exactly what happened in studies on short-term memory in primates, particularly with the example of the visualization.
But in this approach that followed Christof Koch and Francis Crick, the focus is more on the neural correlates of consciousness as causal mechanisms: both can be the same or not.
Curiously, this approach also emphasizes the weight of prefrontal cortex in achieving visualization.
But what results he then for emotions?
I conclude that emotional system such as that fear is activated in a conscious mind of its own affairs.
What we refer to as "fear" is the mental state in which we find ourselves when the activity of the defense system located in the brain (or its aftermath, as the body's reactions) takes up the RAM.
And observed, emotions are closely linked to areas of the cortex that characterize primates and especially humans.
Subtle degrees of feeling associated with our talkative nature, emerge, because we can, with the help of words and grammar, differentiate and categorize the statements attributed to others than ourselves.
In contrast, for example, Antonio Damasio think sensations arise from primitive activities in the areas of body sensation cortex and brainstem, as Jaak Pankseep however that focuses more on the brainstem.
As the network has not changed much in the course of human evolution, it could very well attended cross sensations of all kinds.
From a purely theoretical point of view, I can not contradict him, but I think it unprovable.
Pankseep argues that what appears as fear among men and in rats is probably also felt as such in both cases: how could yet whether rats and men feel the same way when they act Similarly?
A cockroach flee the danger, but he feels fear?
In my view, similar behavior is not sufficient to prove identical experiences.
Admittedly, the comparison helps nerve: rats and men have similar brain stems, cockroaches against by not even have a brain.
But is this-that the brainstem is the origin of sensations?
And even if we could prove that for humans: how could we demonstrate in rats?
I think rats and other mammals, perhaps even cockroaches (who knows?) Have sensations.
But I do not know how to prove it.
And because their feelings are likely to differ completely from ours (since human consciousness based on special tracks and the language), I prefer to explore the emotional sensations that emotional behavior of rats.
In any case, progress on the nervous poignent plan as we gauge the same in rats and humans.
Since I did not explore the language and consciousness in rats or feelings, I do not know if they exist.
We may consider this as the short-term, but I prefer forward rather than constantly bumping me against a wall.
I am indeed a pragmatic emotional.
Platini, UEFA President: a grace period for Poland and Ukraine
The Deputy Prime Minister Ivan Wasjunik explained that preparations would soon be placed under the direct responsibility of the President and the Prime Minister.
"The government considers the decision of UEFA in Bordeaux as a proof of confidence in Ukraine and its ability to organize, together with Poland, the European Championships," announced Wasjunik.
"But it is not an amnesty for our country.
The work has just begun, and there is still much to do in the two countries. "
In the timing of the construction or destruction stages, streets, hotels and airports, both hosts are running after time.
The number of stages for the European Championship could possibly be reduced from eight to six.
"We can not waste any more time.
We must work at full speed, "said the President of the Ukrainian League Grigorij Surkis.
"UEFA has us constantly to the eye."
A more drastic measure was decided in Poland.
The direction of the Polish Football League PZPN was suspended by the National Olympic Committee after many scandals and replaced by Robert Zawlocki, independent director.
The committee was convened at the request of the Minister of Sports Miroslaw Drzewiecki.
There exists "a real danger that the PZPN not be able to act within the rules," said Drzewiecki the Polish news agency PAP.
"We provided a letter to the President of UEFA and the preparations for the European Championship in 2012 did not suffer."
Several members of the League First Division were already in the previous season, convicted for handling mandatory relegation, ultimately, the beginning of the League even be shifted at the last minute.
Dennis Quaid indignant against attack
She wanted to do the promotion for a new movie, talked about his personal life in an interview - and now has trouble with his ex: Hollywood star Meg Ryan unveiled his adulterous ex Dennis Quaid.
It scum - and against attack.
A war of late Rose for the former pair Meg Ryan and Dennis Quaid, seven years after their divorce, the two Hollywood actors engaged in an ugly battle - in full sight of everyone.
Last week, Meg Ryan was expressed in an interview with American newspaper InStyle about the causes of marriage breakdown: "Dennis has been unfaithful to me for a long time, and it was very painful."
She became aware of the extent of the deception only after divorce.
The reason for this strip of thought lies in media relations Ryan for his new film "The Women" - is told the story of adultery.
The reaction of Dennis Quaid on his qualification unfaithful husband fell clearly: it would be "Monstrous," said the latter to "New York Daily News," 54 that "Meg chews again the history of our relationship and handle. "
It would be more "unfortunate" that "the pain and turmoil that have a divorce for every child to be revived again in public" for their common 16 year old son Jack. "
While Ryan has lived alone since the divorce, Quaid remarried and will soon become the father of twins.
So was his response to scratch: "In any case, my life continues.
I consider myself fortunate to have a wonderful family that goes better. "
The price of airline tickets and hotels fall
In the first half of 2008, the flights and hotel nights were cheaper than the previous year.
In Germany, according to a recent study, the flights would be even reduced as much as 50 percent.
Flights and hotel nights would again become attractive - this is the result of a study of the financial services and American Express Travel.
The company has analyzed its booking data for the first half of 2008 and established after a price increase in the first quarter net profit decline in the second quarter.
After the market price of the hotels have increased over the years, the hotel nights were already reduced in many places.
From January to March, prices rose in 41 of the 48 examined again by 6.9 percent on average in 2007 compared with 41 of the 48 European cities European cities examined.
From April to June, prices were, however, already 3.6 percent lower than the previous year.
The trend has been particularly marked in Paris and Rome, where travelers had to pay 30 to 37 percent lower than a year earlier.
The causes of this reside for American Express in the low dollar, which led to a "desire to travel down American tourists."
Financial centers such as Frankfurt or London would be even more affected by lower prices for hotels that industrial sites such as Hanover, Cologne and Stavanger.
In the Swedish city hotel prices stand with an increase of 26.3 percent, a record in Europe.
Also for cheap flights, the trend was upward in the first quarter:
Due to the increase in fuel prices, the economy class passengers had to pay an average of 7.1 percent more than in 2007, the long-haul, very fuel-efficient, even increased up 29.2 per cent.
From April to June, prices for economy class tickets fell by an average of 12.5 per cent compared with the previous quarter, business class and first class, however, price changes were much less pronounced.
In Germany, prices were even higher than in other European countries fall:
From January to March, prices rose 11.9 percent in the second quarter, they fell 23.6 percent.
German domestic flights were even halved according to the study.
The reasons for the fall in prices would be on one side a sagging economic growth, says the firm.
Demand would cede ground in many segment of air travel.
On the other hand, there would be an increased pressure of competition by the treaty "Open Skies" liberalizing air traffic between the United States and Europe.
Sign of the tense situation is the removal by airlines of non-profitable routes, as well as the high number of airlines that have filed for bankruptcy during the first half of 2008 - up from 24 companies in Europe alone.
HSV beat Gladbach 1:0
With a goal and simple methods, the SV Hamburg became the first ranking.
In Borussia Luhukay has still not managed to find an eleven functional.
Kristoffer Klein. Enlarge. Crash landing for international player Marko Marin.
Gladbach player did not return until late in the game and his shot failed up against the frame of the goal.
His message was precisely formulated, it was out of his mouth so persuasive.
He just knew he was right.
"We need that second goal," hissed Hermann Rieger lockers in the hallway of the arena in Hamburg.
It is not much happening in the locker room, half time was over and most of them were stale in their place.
Rieger has been for nearly three decades physiotherapist HSV, it enjoys a high reputation as many old players.
And that is why his application was received at strategic places.
The assistant coach Cornelius Jol acquiesé and raised thumb to approve.
Cornelius is the brother of the head coach of Hamburg Martin Jol.
Whose orders seem to have been similar: and it jumps with the second goal!
The practice has failed.
"Everything was not very nice to see today," admitted later Marcel Jansen.
Bastian Reinhard would "also wanted to be more relaxed."
This 1:0 (1:0 to halftime), the Hamburg team owes a strike successful head Mladen Petric (the 11th minute) and the fact that the very small players Gladbach could not hurt the weak players Hamburg.
"It was a dirty victory" summed Marin Jol.
SV Hamburg celebrates its 121 years on Monday.
Already on Saturday afternoon, the fans are celebrating themselves, the blue sky above the arena and tables standings on the giant screen that showed the club as first class.
It will be a birthday party without real.
"We know to step back," said Marcell Jansen.
He suspects that the intermediate result table reflects more the unpredictability of the first league that the domination of the HSV.
The team engaged with late arrivals - Brazilian Neves Silva, goalkeeper Petric as debauched Jansen FC Bayern - certainly forms slowly, but it does not shine.
"We need more charm and more dribbling," Jol required.
After the failed vote
On Wall Street, fear flows.
The first news of the failure of the bailout have reduced temporarily the Dow Jones 700 points.
It was the biggest loss of points in the space of a day in history.
Later, the Dow Jones was a little caught up.
Around 20:30, the most important stock index in the world stood at 10,579 points with a drop of as many as five percent.
The index of Nasdaq trading technologies was 1548 points with a drop of more than seven points.
Most losers in the Dow Jones was at that time that American Express lost nearly 14 percent and Bank of America with a loss of about 12 percent.
No title could not bring profits.
The shares of the Bank Goldman Sachs accused a drop of almost ten percent.
There are only a few days, the great investor Warren Buffett had joined the company.
Under the rescue plan, the means must be mobilized for the purchase of so-called mortgage spoiled papers.
The sum must not, however, be paid at once, but gradually.
In return, the state should recover options on shares of the financial company that may be exchanged in correlation with the trend in order to reduce the burden on the Treasury.
Share prices sucked into the vortex in Europe and the United States
The billions in aid to banks in Europe and the United States does not compensate the concerns of investors.
The course of action of the major German bank Hypo Real Estate collapses and pulls the Dax to the bottom.
The U.S. Dow Jones Industrial Average collapsed despite the bailout of the financial market provided by the state.
Dramatic declines during Hypo Real Estate and Commerzbank led the German index (Dax) deep deficit.
The action of the Bavarian Financial Real Estate lost time by three-quarters of its value despite the rescue of the federal government and private banks, Commerzbank has declined by over 20 percent.
The DAX slipped significantly below the important psychological barrier of 6,000 points and was trading at 5,839 points with a deficit of 3.7 percent.
Around the world, stock markets fell to their knees.
In New York, Wall Street opened with significant losses.
Investors feared the bailout heavy 700 billion dollars from the government of the United States may not be sufficient to restart the financial markets.
The Dow Jones 10809.25 items lost in the first hour of opening paragraphs 334 or 3.3 percent.
The House of Representatives of the United States intended to vote on the bailout, a vote in the Senate is expected to follow on October 1.
Other European stock markets also experienced only direction: in London, the FTSE 100 index was down for now 3.2 percent, the CAC 40 in Paris lost 2.9 percent.
In Asia, the main Japanese Nikkei fell to 11,743.61 points after an increase from 1.26 percent.
In Hong Kong, the Hang-Seng index slipped 2.1 percent to 18,286.90 points.
In India, the main Sensex index lost 506.43 point or 3.9 percent, and closed at 12,595.75 points.
In the MDAX, shares of Arcandor fell after the announcement of a capital increase.
The private bank Sal. Oppenheim has subscribed to 23 million new shares.
The multinational commercial and tourism has also stated that the shares will not be sold to Thomas Cook.
Of dark matter influences the flight of spacecraft
For years, a mysterious phenomenon leaves researchers in the perplexity of dark matter influences the speed of the spacecraft during the so-called gravitational support maneuvers.
Experts fear that the general theory of relativity is not completely correct.
For almost 18 years, the space probe "Ulysses" flying in space.
Due to conduction fuel soon frost, cryogenic death threat.
For years, a mysterious phenomenon is causing confusion among researchers - the anomaly of the gravitational support.
The gravitational support is a maneuver space probes, for which they get an extra boost in the gravitational field of a celestial body, the Earth, for example.
Thus, the probes can save a lot of fuel.
Probe Americo-European research Cassini-Huygens used this physical trick, as the Ulysses solar probe.
This is what surprised researchers elsewhere for years: the flying objects do not always behave to 100 percent of the way you would expect in the venerable laws of gravitation.
Furthermore, irregularities appear at speed.
Probes become faster or slower unexpectedly.
Until now, physicists could not explain this effect.
They named it the fault of the gravitational support.
Some experts fear that the general theory of relativity by Albert Einstein, which describes the attraction of the material strength due to the curvature of space, can not be entirely correct.
The American physicist Stephen Adler of the Institute for Advanced Study in Princeton still firmly believes that Einstein was right and trying to explain the anomaly of the gravitational support using the so-called dark matter that astronomers have identified in the universe.
"Dark matter may be responsible for this anomaly, material which is also close to the Earth," he wrote.
Researchers space are aware of the dark matter only for about ten years.
It apparently comes from it an attractive force whose effect is observable on other celestial bodies.
She, by cons, is completely invisible, that is to say, it does not send or reflect any electromagnetic radiation, especially any visible light.
According to scientific calculations, dark matter still represent one fifth of the entire mass of the universe.
Tourists kidnapped in Egypt are free
After ten days in the hands of their captors, tourists kidnapped in Egypt should be freed and the Italian Minister of Foreign Affairs confirmed it.
Sudanese kidnappers demanded a ransom of several million euros.
During the shooting before the release, six hostage-takers were killed.
In southern Egypt, five Germans were removed.
Negotiations for ransom are already underway.
The Germans are constantly in the crosshairs of kidnappers.
WELT ONLINE depicts the most important cases.
European tourists kidnapped in the Sahara are obviously free.
This was communicated together the Egyptian state television, the Arab television station Al-Arabija and Italian media.
Italian Foreign Minister Franco Frattini confirmed the release after the bulletins of the Italian television channel Sky TG 24: "Our citizens and the other hostages were released.
We are now checking their health, "Frattini told.
The five Germans, five Italians and their Romanian and eight Egyptian guides are doing well and are safe, the Egyptian state television announced.
The 19 participants of the excursion in the desert should already be en route to Cairo.
The circumstances around the shooting before the hostages are still unclear: thus, the kidnappers were close to putting an end to the kidnapping, in the words of an Egyptian security officer, before the Sudanese army kills six kidnappers without warning.
"The problem was solved.
They agreed to a ransom, "said the agent.
It only remained to collect the hostages, "when suddenly," the surprise "occurred.
Sudanese soldiers were killed on Sunday six of the kidnappers in the border area between Sudan, Chad and Egypt, and arrested two of them.
The kidnappers had demanded a ransom of Germany in the amount of six million euros, the money should be given by the German wife of a hostage.
The daily "El Masri El Jom" stated that, in the words of a German mediator, the hostages was falling behind because the kidnappers feared for their safety.
According to the article, the kidnappers wanted to liberate women hostages after payment of ransom.
The men were to be retained until the kidnappers have found a safe route to escape.
The German embassy in Cairo declined to comment on this story.
Abuse of a stepfather "that led to suicide"
A court was told that years of abuse inflicted by her stepfather led a woman to commit suicide.
Michael Trerise, 57 years of Stithians, Cornwall, was jailed for six years after admitting eight counts of indecent assault.
The High Court has referred to Truro he regularly bound his daughter, Stephanie Randle during his childhood, from 5 to 7 years.
Trerise wrote in a letter of confession: "I feel responsible for his death."
The court was informed that Ms. Randle, aged 34, committed suicide at her home in Mutley, Plymouth, April 1, 2007.
Child when she lived in Coventry, Trerise had tied and bandaged before forcing her to perform sexual acts, while her mother worked at the pub.
Trerise and his wife divorced in the 80s, and he returned to live in Cornwall.
His daughter went to Plymouth.
But the court was informed that Ms. Randle, diligent volunteer National Trust, was haunted abuse that had been imposed twice a week.
Attorney General Ramsey Quaife told the court that friends had told that Ms. Randle, who was a good surfer and cyclist since 2006 appeared "emotionally dead" and "had lost all hope towards life."
In April 2007, his real father, Terrance Randle, was found dead in his apartment in Plymouth.
It is believed that she committed suicide by suffocating with a plastic bag.
Mr. Randle confronted the father-daughter who had also written a letter of confession which ended thus: "I clung and bandaged regularly."
"I have not abused her sexually.
"I feel responsible for his death."
Judge Christopher Elwen told Trerise: "You're really weird fetish like, your victim should certainly be scared, especially at the age of 7 years.
"This unpleasant saga ended with the suicide of the victim.
And what even more amazing is the fact that if she had not committed this act, history would certainly never finished the court. "
He added: "I note in particular, as described by his father and mother, the effects of your crime committed for years on Stephanie.
"Without them, it would probably be a happy young woman today, promising and successful."
Conviction for loss of official data.
The officer of the Cabinet Office who had forgotten the top secret documents, in June on a train, will be condemned by the Official Secrets Act, knew the BBC.
Man of the Ministry of Defence was traveling when forgot two documents highly ranked on a train to Waterloo.
Documents are passed into the hands of the BBC before being delivered to the police.
This is the least serious condemnation of this act, without any hint of criminal intent.
The BBC correspondent Frank Gardner said that this episode had a lot of people Whitehall.
"They have thought that this case would have remained within the walls of the Ministry of Defence and the Cabinet Office," he said.
An employee who can not be named, is accused of violating section 8.1 of the act, that is to say the clause that deals with the preservation of information.
. The Crown Prosecution Service suggested that the ministerial officer to be placed under the supervision of the Metropolitan Police, given the sensitive nature of his work related to the Associate Committee of Secret Service
The documents he lost contain assessments of Al-Qaeda and the resources of the security forces in Iraq.
He was informed of the decision Monday morning and was then transported home to a secret location.
Companies building facing the bill B & B.
British construction companies may have to pay a bill of more than £ 80 million to cover the rescue of the bank Bradford & Bingley.
The Government has provided £ 14 billion to protect the deposits of 2.6 million savers Bradford & Bingleys.
The interest of this loan will be paid by all companies that collect money from investors, including 59 construction companies.
The CEO of Building Societies Association (BSA), Adrian Coles said it was "irritating" to know that the companies and their members will have to pay the piper ...
The loan of £ 14 billion will be repaid when the mortgages of Bradford & Bingleys will be released.
But the interests that are at the same time increase will be charged annually to the 700 financial companies that collect deposits.
The Financial Services Compensation Scheme has confirmed to the BBC that 59 construction companies are included in this list.
It is irritating to see that institutions were cautious behavior ... must now pay some bills institutions that were less conservative.
Adrian Coles, BSA
It states that each company must pay an amount proportional to the deposits it holds, and the intermediary companies must pay 18% of the cost.
The Treasury estimates that the loan interest will rise in 2009 to £ 450millions.
This means that companies will have to find £ 81 million to settle the interests of the first year.
Adrian Coles, director general of the Trade Committee of the construction companies, told the BBC that the decision was unfair to him.
It is "irritant" to see the institutions that have had a cautious behavior in the real estate market recovery now have to pay for a lot less conservative institutions.
According to the BSA, no society has failed since 1945, when the first record.
"We need to look at all aspects of this matter in the coming weeks, to assess options to adopt to prevent the construction companies and their members pay the hefty price tag," said Cole.
Interest for 2009 cover seven months of the end of September this year until the end of March.
In 2010, it will pay interest on the entire year, which could also double.
Because companies are building organizations without shareholder their member eventually pay the bill either higher loads, or lower for savings accounts interest rates.
Milk increases to five pence per liter
The people of Jersey have to pay more for their milk
Jersey Dairy has announced it will increase the wholesale price of its milk, five pence per liter, from Monday.
This is the second price increase that follows a two-penny increase in February, and occurs as a result of research conducted by a consulting firm.
The retailers must decide whether they will in turn increase the price to consumers.
. Before the increase in February, the wholesale price of milk from Jersey was changed for the last time in 2002.
An ex-Pm Bangladesh has denied bail
A court in Bangladesh has rejected a request for bail to former PM Sheikh Hasina, is therefore likely to be arrested upon his return to the country.
His lawyers said the court refused to grant bail because of his indictment for extorting a businessman, 50 million Taka ($ 729,000.00) when she was PM.
This case is one of the many accusations that are addressed.
Khaleda Zia, the rival always Sheikh Hasina, was acquitted on bail earlier this month.
Sheikh Hasina is expected to return to Bangladesh in a few weeks, but his party, the Awami League has demanded that the country's interim military government first gives full freedom.
Correspondents noted that the terms of his release are contradictory because if we allow him to leave the country for medical reasons, they do not see why it could not be free to return to Bangladesh.
His lawyers announced that it will now appeal to the Supreme Court against the order of the Supreme Court.
"The Supreme Court rejected the request of Sheikh Hasina said she requires no bail since she was allowed to go abroad for medical reasons," said his lawyer Rafique-ul Huq.
"We will appeal against the order of the Supreme Court"
His lawyers argued that she needed to return the deposit to the country to prepare for elections in December
Sheikh Hasina is expected to return after October 17, said a former leader of the Awami.
She was detained last year after the interim military government has assumed power, but was released in June to receive treatment abroad.
Sheikh Hasina as Zhaleda Zia, deny the charges which they are subject.
Concerns for Afghan polio campaign.
In Afghanistan, nearly 200,000 children have missed the recent immunization campaign against polio in reasons related violence Taliban, said the UN.
The UN has made last week, a vaccination campaign in the six provinces.
But she says not being able to contact their children from dangerous areas in Helmand and Kandahar in the south.
A UN spokesman said that this happened despite the promises of the Taliban not to attack or obstruct nursing thousands during vaccinations.
BSkyB loses court battle ITV
BSkyB has lost his trial following the verdict of the Competition Commission, which would require it to reduce its stake in rival ITV transmitter.
The Competition Appeal Tribunal has ordered BSkyB to reduce its share of ITV from 17.9% to less than 7.5%.
The commission said that in the past, participation MSkyB had prevented competition and allowed him to unfairly influence ITV.
BSkyB bought his shares in 2006 following an agreement to actually prevent NTL, now called Virgin Media, ITV buys.
In April 2007, the Office of Fair Trading has reported that the acquisition by BSkyB of shares in ITV cast doubt on the actual independence of ITV, prompting consequently, the Competition Commission to investigate
The Virgin boss, Richard Branson, a group of consumers and the regulator Ofcom were all contrary to this purchase.
BSkyB responded that force it to reduce its stake in ITV would be unreasonable and contrary was excessive - especially considering that BSkyB has to give up its voting rights.
Further investigation in the case of U.S. prosecutors.
The U.S. attorney general has appointed a special prosecutor to check the issue of dismissal of nine U.S. attorneys in 2006.
Everything is born of the report of the case of the Inspector General of the Department of Justice, which criticized the actions of certain public officers.
The report was critical of the officers of the White House, legislators and former Attorney General Alberto Gonzales.
The survey is based on the theory of lawyers who argue that their dismissal is due to political causes.
The Special prosecutor, Nora Dannehy now investigate whether the officers interviewed during the investigation, lied to investigators and obstructing justice.
"Serious allegations of potentially criminal conduct, unfounded, have not been fully confirmed or resolved," said Inspector General Glenn Fine, in his report.
The appointment of a special prosecutor can compel witnesses to testify, was one of his biggest recommendations.
The argument begins with the radiation in December 2006 nine U.S. attorneys made by the U.S. Department of Justice.
At the time, the department stated that the prosecutors were dismissed because of poor performance.
But it then emerged that the dismissed prosecutors were not criticized more than their colleagues, prompting some observers to assign these redundancies political connotations.
Some prosecutors have been accused of being close to Congressional Republicans, while others have refused to investigate the accusations of fraudulent voting against the Democrats.
U.S. prosecutors investigate and prosecute legal proceedings for the government.
It is certain that they can be fired at any time, but can not be brought for political reasons.
The head of the Justice Department, Attorney General Alberto Gonzales, eventually accused of being involved in the case of dismissal, and in the end, he resigned.
A number of judicial officers of the Department of Justice have also resigned.
The report of the Inspector General was highly critical of the role of Mr. Gonzales in this case, stating that he considered "primary responsibility" for the dismissals, and eventually "abdicate" his leadership role, "succeeding remarkably not involved in this case.
Other officers, including former collaborator Bush, Karl Rove, has been criticized for having failed to cooperate during the investigation.
Epic Meat Loaf will be honored.
The Rock star Meat Loaf, should be honored at Q Awards for his epic song Bat Out Of Hell.
The singer, who will receive an Oscar at the ceremony in London next week, said he was "honored" to receive this recognition.
The song nine minutes and fifty seconds, was the title of the hit album Meat Loaf 1977.
The evening of the awards presented by Coldplay with this year, a limited selection to four categories.
Paul Rees, editor of Q magazine, said: "There are songs that transcend such things as time and genre, and Bat Out Of Hell is certainly one party
The song, written by Jim Steinman, required a great voice like Meat Loaf.
It begins with an instrumental section that lasts almost two minutes.
The song was put on the market in the UK as a single in 1979, finishing in fifteenth place.
In addition, the album Bat Out of Hell has spent nine years in the British rankings and was sold over 40 million copies worldwide.
Meat Loaf-or Marvin Lee Aday, whose real name-has suffered from health problems in recent years, even undergoing an operation to cure his heart beat became irregular after collapsing on stage in 2003.
In 2007, a strong laryngitis was forced to cancel concerts.
Then they found a cyst in her vocal cords.
A Street in the Dark City, Often Forgotten, and May Soon Be for Sale.
New York has hundreds of avenues, boulevards, streets and other parallel roads, some famous, others only functional.
. And even some veterans and local longtime residents know not to give directions to get to Extra Place, because they have never heard of taxis.
The street is located in the East Village and travels north from First Street-not to be confused with Second Street, between Bowery and Second Avenue.
From about 30 feet wide and 120 long, it looks like a dusty alley rather than an active artery.
. Some panels show the street.
It is virtually impossible to find on a standard atlas.
However, this street has admirers.
For example, there is Avalon Bay, the manufacturer of the recent luxury buildings on First Street.
He would repave Extra Place, and create a smoother transition to the stores and shops, which should open in new buildings.
Other admirers including long-time neighbors, said they were charmed by this shortcut simply because it is one of the last and oldest streets of the block.
But the Department of Preservation and Real Estate Development, which manages the city street, has no interest in keeping it.
This month, at a meeting of owners of neighborhood committees, representatives of city agency and Avalon Bay have drafted a proposal to allow the homebuilder to buy the street.
But the committee prefers that the street remains in the hands of the city, and asked to submit a new proposal next month, said Susan Stetzer, the local manager of the Committee 3.
"There are only a few spaces belonging to the city, and we hope that the city retains Extra Place," she said.
"They could offer to rehabilitate and manage, that could also Avalon, but we want to keep it public."
Avalon Bay announced several months ago that she wanted to repave the alley and install seats, some are also used by the builder coffee concede space.
The proposal of this potential acquisition was made public at the meeting this month.
Michele de Milly, a spokesman for Avalon Bay, said that although the company wants to use the street, that does not mean she wants to be the owner.
"The main interest of Avalon Bay is to revamp the abandoned alley, and make it public," she said, noting that it was the city to suggest the sale. "
Seth Donlin, a spokesman for the Preservation of Property, confirmed that the city wanted to commercialize the street, further emphasizing that the mission of the agency was to develop the property rather than manage it.
Compared to its more colorful neighbor, Bowery, Extra Place has left a slight historical footprint.
Some believe that extra Place this name since 1802, when the legacy of the great farm of the many children of Philip Minthorne was divided, leaving aside this small piece of land, which remained abandoned since.
The rear entrance of the CBGB punk rock monument closed in 2006, reopened in Extra Place, the street is certainly more famous for the cover photo of the Ramones album "Rocket to Russia"
"This place was beautiful," said Danny Fields, the manager of the Ramones, who took the photo in November 1976.
It was full of scrap metal, rags, barrels, posters, leaves and strings. "
Some residents, including bloggers who have already talked about the move to the luxury of the East Village, opposed the idea of ​​selling Extra Place, saying that this humble little property should remain public.
Others proclaimed Extra Place as a true rarity, a virtually identical fragment in the city that should be done for peace.
Jeremiah Moss, who drove a blog called Jeremiah's Vanishing New York (subtitled "The Book of Challenges: A Bitterly Nostalgic Look at a City in the Process of Extinction") tells the story of the City and Extra Place, published in 1952 in The New Yorker.
The author, Brendan Gill wrote: "Extra Place is a small narrow cul-de-sac, dark day and night, and bounded through the doors of a warehouse and rusty iron shutters, full of newspapers last week that fly along the gutters. "
With few exceptions, the street still looks the same.
One rat short nimbly at the bottom of the alley, near a door that once led to CBGB, which has now become the seat of a shop chic clothing.
Graffiti on the walls, a bottle of beer 22 ounces empty, rests beside newspapers that have just been thrown away.
Some bystanders said they rarely think Extra Place, and suggested its development.
Mr. Field, for his part, said in evidence that some felt the lure of the street in its current state.
"The best years of my life," he said, "took place in dark, humid and disgusting."
Bilingual Debate: Immersion in English
In this part of the program for the Supervision of Education, Bruce Fuller and Lance T. Izumi discuss the candidates' positions about bilingual education.
Lance T. Izumi, a former member of the California studies, and former director of the education department at the Pacific Research Institute for Public Policy, is the co-author of "not as Good as You Did not. Why the middle classes must be able to choose their school. "
Curry favor with Hispanic voters is a complicated business.
Barack Obama's proposals on education are an interesting example.
The Obama campaign points out that "African-American and Latino students are less likely to graduate than white students." it is a true fact.
To combat these differences, the education program supports Obama in particular among many other things, "transitional bilingual education" for those who are learning English.
However, the question for Obama is whether his desire to make a bilingual education that promotes classroom instruction in languages ​​other than English, will also interest to eliminate differences.
Take for example, Sixth Street Prep, an elementary school in eastern Los Angeles County.
Students of this school are great majority Hispanic, and low income.
More than a third of students, made up of many newcomers, studying English.
Among students CM1, 100% passed the state math exam in 2008, expert level.
Similarly, almost 93% of students passed the English exam-language-d'arts
This incredible success was achieved thanks to an ingredient other than that advanced by Mr. Obama.
Sixth Street relies on analysis of practice, constant evaluation capacity and an exemplary attitude.
In addition, and this is an example that Obama could copy, reports Linda Mikels, principal of Sixth Street, the school introduced the instruction of the English language "full immersion".
Total immersion in English focuses on the almost constant use of English in education.
Miss Mikels, contrary to bilingual education, has affirmed me "we had a huge success with a student who had just arrived from Mexico, 12 months later, if you go without the class, you would have had no chance to identify it. "
"It works, she observes," it worked for us "
Mr. Obama should not follow the example of Sixth Street Prep and replicate in other schools made up mostly of Hispanic students learning English.
The excellent results achieved by the school speak for themselves, but the education policy within his own party (the National Education Associations have long bilingual education) and its enormous support for bilingual education, dim prognosis of response from Mr. Obama.
While welcoming the fact immigrants learn English, Obama has recently considered this issue as insignificant, when he proclaimed that we all stop arguing about the wording of the laws in English.
"Instead, he said," you must ensure that your child speaks Spanish. "
If Obama really wants eliminate differences, then it should be carefully considered, education models that work, rather than despised or regarded as insignificant.
Net Oil falls after the New Concerns World Economy
Oil prices fell sharply Monday, as people fear that the rescue plan for the financial markets, will succeed in reviving the economy.
Futures trading of crude oil, fell 7 percent reaching $ 99.80 a barrel. The New York Mercantile Exchange, while sales this morning.
Prices have dropped by more than $ 20 per barrel since last Monday.
Over the past two weeks, commodity markets have been shaken by the financial turmoil on Wall Street, as well as two powerful hurricanes in the Gulf of Mexico.
After experiencing in July, an increase of up to $ 145.29 per barrel, prices have dropped to almost $ 90 per barrel this month before rebounding again in the sight of great uncertainty in financial markets.
On Monday, investors are again worried despite the agreement on the bailout, the largest in history, concluded this weekend with congressional leaders.
The news was mitigated by recent concerns that the crisis would be durative.
In the latest episode of this financial disaster, "Citigroup will acquire the banking operations of Wachovia Corporation, the government said Monday.
At the same time, the Belgian, Dutch and Luxembourg governments have nationalized party European financial conglomerate Fortis.
Analysts at Barclays Capital said that frantic negotiations this weekend concluded with the bailout deal "seem not to have succeeded in reviving the market."
While the economic situation détériorasse, the demand for commodities, including oil, is expected to slow.
"Global prospective equity, interest rate and exchange markets, has become uncertain" wrote analysts at Deutsche Bank in a letter to their investors. "
"We believe that the raw materials can not escape the contagion.
"With regard to raw materials, our most pressing concern is to understand how far the U.S. virus would spread it globally and especially in China."
Analysts at the bank have reduced their expectations for the next year, given the fall in consumption of oil due to the slowdown in economic growth, were therefore forced to reduce 20per cent price forecasts for oil and gas in 2009 .
Day Second Time Determinant for Improved Record Team.
After spending during the past eight seasons, longer than anyone in uniform Jets Shaun Ellis, the defender thought he had seen it all.
He watched the second time, when the Jets turned a 0-0 in an explosion.
"I've never seen anything like this," said Ellis.
The second phase began after the Jets and Arizona Cardinals have played badly in obscure clouds.
Then quarterback Brett Favre has managed to make a pass to Laveranues Coles for a 12-yard touchdown, precursor to an afternoon during which their relationship has surged ahead.
Favre found Coles for two more touchdowns, the first when a corner fell back and the second, 10 seconds of the half.
"I'm not out of my area" Favre said of all his passes to Coles.
"This is a mediocre player"
"We communicated very well, despite what people think."
While Favre and Coles were playing catch, the defense beat the Cardinals quarterback Kurt Warner.
Darrelle Revis, corner back, intercepted a loose shot and gave up 32 yards touchdown.
Eric Smith made another pass and was intercepted.
Linebacker David Bowens let out the ball because of Warner.
The last change, the loss of the ball Bowens could well be the most charming Event
The Cardinals took control of the possession during the last 10 seconds, and then the Jets recovered the ball, Jay Feely made a 20-yard goal taking advantage of 34-0.
It was better than the Jets were able to score at a time.
"The Jets coach Eric Mangini, who was asked to describe this madness, said" the second or third time? "
When he was told the two the Jets missed 21 points in the third indisputable time Mangini said: "I can say that I enjoyed more the second time than the third.
. "Many points have been scored in a short time."
Gebrselassie rested than his world record.
Haile Gebrselassie of Ethiopia, has again proven to be worthy of the title of the best runner of the century, after beating his own world record in Berlin Marathon Sunday, becoming the first to run 26.2 miles in under 2 hours and 4 minutes.
With a win in 2: 03: 59 accommodative race on the flat, Gebrselassie broke his record of 27 seconds 2: 04: 26, played last year in Berlin.
At 35, Gebrselassie won the 26th world record of his magnificent career in which he won the world championship or the world record for any distance, 1600 meters of the marathon.
Last month, Gebrselassie missed the Olympic marathon in Beijing, fear-may be exaggerated to today's eyes - that air pollution does not increase his asthma problems.
Instead, he promised to run in Berlin.
In almost perfect conditions, sunny weather, 48 degrees at the start, 55 at the finish, Gebrselassie won Sunday, now an impressive average of a mile in 4 minutes 43 seconds
Runners track like Gebrselassie and Paul Tergat, both Kenyan, converted into distance runners, have contributed to the decrease in the marathon record of more than two minutes in the last ten years, since 1998, when the Brazilian Ronaldo da Costa won in Berlin in 2:06:05.
After Sunday's victory, Gebrselassie told reporters, having suffered calf cramps two weeks before, and had missed training for a week.
It is obvious that the rest allowed him to remain bright, but not rusty.
"I'm so happy," he told reporters.
"Everything was perfect.
I got given last week, and today I had my doubts, but in the end, everything went for the better. '"
Was criticized him-especially in Kenya, the East African rival of Ethiopia, having too orchestrate shopping, avoiding the marathon world stars, cash makes the hare as if they were in a competition track and considering more world records as the sense of competition.
But this criticism does not diminish the greatness of Gebrselassie capabilities as a runner.
Gebrselassie Sunday, preceded by four Kenyans, recorded a time of 1: 02: 04. halfway.
Two elite Kenyan runners, James Kwambai and Charles Kamathi, continued to defy Gebrselassie after the file headers have disappeared.
A little more than three miles from the finish, Gebrselassie made his final ascent to detach Kwambai, who finished second in 2: 05: 36, improving his personal best by five minutes.
Kamathis arrived third in 2:07:48.
In the women's race, Irina Mikitenko, born in Kazakhstan, now a German citizen, was a remarkable year getting the seventh time 2:19:19.
The English Paula Radcliffe holds the world record of 2:15:25.
Last spring, Mikitenko aged 36, has surprised everyone winning the London Marathon in 2:24:14.
She could not participate in the Beijing Olympics because of a hypothetical back pain, but promised to win in Berlin, improving on his third marathon personal best by nearly five minutes.
She ran by using a clever strategy, leaving the group of Ethiopian and Kenyan runners have a great advantage, then the excess of about 18miles half after.
Margasa Askale Tafa of Ethiopia finished second in 2:21:31, while Helena Kiprop, Kenya, finished third in 2:25:01.
In a City Part, Pride events and Black Life
Hidden in the development of its huge park, a few miles from the sun, the bright and the giant Orlando, is a quiet town where the pride and complications of the African American experience born.
"Eatonville, the first all black to integrate childhood home of Zora Neale Hurston city, this description it did in 1935, is no longer so easy to do nowadays." The city in five lakes, three croquet courts, 300 dark skin, 300 good swimmers, plenty guavas, two schools and not in prison. "
It has now become a place of pilgrimage
Alice Walker, Toni Morrison and Ruby Dee came to Zora Festival is held every year in Eatonville, to pay tribute to Hurston, the most famous writer of the Harlem Renaissance.
And in many ways, the city that describe became tourist through its inclusion in the tourist guide published by The Florida Depression-era Federal Writers' Project, remains a place apart.
It is also independent, dignified, private and it was already in the 30s, when Hurston told the black rural population in Florida was often reluctant to share their true thoughts with the white man, that "we know if not, does not know what he's missing. "
Although this is the year of the election of a black president, Senator Barack Obama, who also invoked an open dialogue on race, many here remain wary gaze of abroad.
"We are very careful about how to tell the story," said Hortense Jones, 59, a resident since forever and the oldest parishioner of the city.
"It must be consistent with reality.
Eatonville has long been defined as a paradox of triumph and struggle.
It is both a historical model of black empowerment and a community of nearly 2,400 people where the poverty rate is twice the national average.
It is a central point but also an example of rural black southern culture-sometimes disdained, sometimes reminiscent of the acclaimed-birth of American slavery.
This would explain why residents are both proud and protective.
The interest in the image of Eatonville born with Zora, everyone here calls Hurston.
She presented her hometown to the world through books sincere, full of dialect, such as "Mules and Men" (1935) and "" Their Eyes Were Watching God "(1937).
Five paragraphs in the guide Florida transformed this city, located just off of Route 17, a road that runs through the center of Florida, often overlooked, which results in terms of black history and human drama.
Bold as a bass drum in life as in literature, Hurston led readers to the store owned by the first mayor of Eatonville, Joe Clarke, who was then divided into several private parties.
"Past the road on the left," she wrote, "you will find the modern public school brown and white, with its gardens and playgrounds these well preserved including Howard Miller was always careful, though he knows barely read and write.
She also mentioned the new husband of Widow Dash and wrote that Lee Glenn "sells drinks of all kinds and all that is for people passing through.
So, barely a hundred words, Hurston association Eatonville to self-government but also illiteracy, remarriage, and sex.
Of course, Fodor was not so.
It was not actually a portrait that everyone enjoyed.
Zora has described the reality, "said Ella Dinkins, 90, one of the girls has immortalized qu'Hurston Johnson, citing the songs without color, interpreted by men who rented their beauty."
She added: "Some people did not like."
It always remembers Hurston as a lively and eccentric person who frequently returned after his family moved to Jacksonville, Fla.
Augustus Franklin, 77, recalled that Hurston usually arrived in town without warning, on board of a large Chevrolet, a cigarette in his mouth and wearing pants here, where even today, we are proud of the traditional dress.
Many residents were fascinated, Mr. Franklin told, while many laughed at her.
"People were happy to see Zora," he said.
But he also added, rocking in his chair rear patio overlooking Lake Sabelia where Hurston was certainly known, that "she never stayed too long."
On the death of Hurston in 1960 she was poor and his books were out of production.
Eatonville and the world seemed to have forgotten.
Although it was once a star of the literature, a contemporary of Langston Hughes and the only black woman of 20 years of Barnard College, she was buried in a tomb any, Fort Pierce, Fla., where she lived.
In Eatonville, no big celebration or plate to the general public.
I do not think they understand the contribution and the legacy she gave to the world, "said Valerie Boyd, author of" Wrapped in Rainbows, "a Hurston biography published in 2003.
A crucial moment came in the 1980s.
Public officials of Orange County wanted to pass a five-lane highway in the city, to replace Kennedy Boulevard, the main street two-way community.
The development of Orlando has already pushed Interstate 4 to the western corner of the city.
The proposal was made when qu'Eatonville is just recovering from a difficult period in its history.
Forced, among other things integration ended relatively idyllic isolation of the community.
In the 50s, the dispute over racial mixing led to hate doors of the community.
"At that time, a gang of white youths were throwing oranges or objects against the people sitting on the side," said Mr. Franklin.
"A lady even died."
They threw a watermelon from their car. "
In a 1955 letter addressed to The Orlando Sentinel, Hurston questioned the application of the Supreme Court to forced integration, defining its decision in Brown v.. Board of Education "insulting rather than glorifieuse of my race."
Residents now claim that the elimination of racial segregation in schools, while positive in some respects, diluted Eatonville cohesion and undermines the confidence of youth.
"Black children were accustomed to be kissed I remember correctly we embraced our master in the morning and in the evening too," said Nathiri NY, daughter of Ella Dinkins and Director Chief Backup Eatonville Community, a non-profit group.
It lasted, she said, until teachers and students no longer came from the same place.
"You do not kiss your white teacher because he is white-I mean that here, a cultural dividing line," said Miss Nathiri.
Civil rights, moreover, have created space for many more Zora Neale Hurston-black writers, actors and artists who went further injury, as, armed with a joyful own confidence and guidelines such as: "How can they deprive themselves of the pleasure of my company!"
Is beyond me. "
In 1975, writer Alice Walker went on the unmarked grave of Hurston and began to struggle to revive its reputation.
Five years later, an acclaimed biography of Hurston by Robert E. Hemenway, a real bestseller, and reintroduced to the American guns.
The highway project arrived just as the most famous daughter of Eatonville had regained its appeal.
And this time, the old neighbors Hurston see it as a savior.
The community began to organize a Hurston festival to show the disastrous consequences that would result from the highway.
Hundreds of fans came to the inauguration of the festival two years later, and many return in January, to commemorate it.
After many years, told rejected the proposal of the highway.
"The fiasco of the five-lane highway, extremely fast, a real civic pride," said Miss. Nathiri.
Ms. Boyd summed it up stating that "Zora saved Eatonville."
The victory against the highway project has allowed him to change his own image.
Non-residents, as Rachelle Munson, a lawyer who attends our church since 1993, began to come in large numbers, and residents began to reconsider the past.
Eatonville is classified historic town since 1998.
A single theme library (obviously renowned Hurston) was opened in 2006 on a magnificent Kennedy Boulevard, repaved.
Today, Eatonville remains a problem for Florida: six miles from Orlando, it may at any time be considered a back street later at a summer rainy day, small as it was when it was founded by 27 black families in the 1880s.
(There are now 90 percent black)
Foreigners who come to discover the history of Eatonville, its reason for being, are still treated with caution.
You have to ask permission for most interviews, and some things like the walls of the old church of Eatonville, painted by the white man, showing black men in the fields, should not be photographed.
Many in Eatonville, like Ms. Jones, a brave teacher who has a weakness for the bright red, have always worried that their insular community is well understood.
However, given the expansion of Hurston festival, a certain level of local pride has emerged.
Young people in particular, tend to consider Eatonville as Hurston saw her entire race: beautiful, problems and all, neither better nor worse, but also proud, creative, hardworking, crazy and mixed than other ethnic and racial groups in America.
It is the sincere civic affection that we hear in the voice of Mr. Franklin's nephew, Edwin Harvey, 18, who plans to return to Eatonville after college to work for the local government or the forces Police, who need additional forces.
And even younger, like Alondra and Alexia Kenon of 11 years, twins Winter Park, seem to have learned the correct description Eatonville.
"Most people who go in this area here, think:" oh, this city has nothing compared to other "Alondra Kenon said after Mass on Sunday.
But if you stop and take time to contemplate the story is a beautiful city. "
Here in New York, all fluent in finance.
Still, nothing has changed.
If tourists in Manhattan stood away from the booth and giant TV screens in Times Square, they would realize they are not in the eye of the storm.
They never could think that in glass desks and honeycomb over their heads, bankers and hedge fund managers who monopolize New York, spend the worst "working day at the office" from the crack of 1929.
The delivery continue to sneak up on the sidewalks, with their carts and trays of muffins for matinières meetings.
Latin still lag between residential buildings bearing, like mules, fifty luxury shirts hanging from a yoke placed on his shoulders.
Office workers still queuing to buy their Matinier sandwich vendors, and it is still impossible to find a taxi between 16h and 19h on weekdays.
I had not felt the crisis despite the completely pessimistic stories until this afternoon when I decided to open a new savings account.
Luckily I planned my work in the late afternoon, as I discovered to my local branch of JP Morgan Chase, twenty people queuing.
Not in front of the offices of the cashiers, or to withdraw cash or make a payment, but before the customer service desk, where regular customers ordered their checkbooks, tourists asking direction for Macy, and new customers opened accounts.
Most of those before me, I would learn later Starr, my "personal banker authorized" were all in line for the same reason as me.
Not in the same way as they had already withdrawn their savings from smaller banks, such as New Jersey, Pennsylvania, and Staten Island.
They withdrew their money from savings accounts known as thrifts (such as a construction company), credit associations, and the type of local communities and their subsidiaries that operate in a state savings banks, and say treat clients as their families.
In the recent past, 15 of these banks failed.
In recent days, Washington Mutual, a bank with a capital of $ 327 was used to the bankruptcy trustee, and while New Yorkers went home for the weekend on Friday night, another bank, Wachovia, to savings accounts a value of $ 440 million, desperately seeking a buyer for the save.
Office and store employees in front of me, afraid of another potential debacle, have transferred their money to a bank that seems reliable, is the one that makes the most rescue Wall Street.
Any New Yorkers have become very familiar with the world of finance in recent weeks.
"I heard a lady at my local Chinese supermarket, talking on the phone Lehman Brothers, the bank that went bankrupt, and his meager CEO Dick Fuld, with the same familiarity that might have to criticize a colleague.
And Lyn, concierge uniform of my building, changed the topic from our usual conversation about Brad and Angelina or my dealer deliveries of fruits and vegetables.
She told me, after my visit to the bank. "I put all my savings in the market for money market funds.
"I've changed, I do not want to take any risk."
Muslim graves desecrated as Austria swings to the right.
Heinz-Christian Strache, who has given up the right wing of the party Austrian Freedom Party and Filip Dewinter of the Belgian Vlaams Belang right, take part in a demonstration to show the organization of the "Cities against Islamization" in Antwerp, Thursday January 17, 2008.
They are road signs depicting mosques striped in red.
Police accused the right-wing extremists have desecrated a Muslim cemetery Austria, the weekend of the victory of the extreme Right in the general elections of the country political parties.
More than 90 graves were seriously damaged in the cemetery of Traun near Linz, between Friday night and this morning, it is according to the police, an organized action.
Offenders were painted on several graves, Jewish symbols such as the Star of David, and the detectives believe, however, that this could have been done to disguise the feeling of hatred towards extremist Muslim immigrants.
This accident could it be somehow related to the elections.
A spokesman for the local Islamic Community said he was "shocked" at the news of the desecration, which occurs only during the religious month of Ramadan comes to an end.
Austria seriously thinking about finding courage, following his swing to the right in parliamentary elections yesterday.
The two far-right parties have won almost 30 percent of the votes, the Freedom Party and the Alliance for the Future of Austria, led an anti-immigration campaign. Some of their slogans were even considered, according to critics, as xenophobic.
Heinz-Christian Strache, the leader of the Freedom Party, which won more than 18 percent of the vote, has campaigned against the wearing of headscarves and burkas and even expressed his opposition to the Alaha food.
During his final race in Vienna, he spoke of "a European brotherhood" to prevent the rise of Islam.
Both parties are trying to prevent the construction of mosques and minarets, claiming they would be a political symbol of Islamization of Austria and Europe.
Surveys and analyzes carried out just after the elections, have defined the extreme right as the country's strongest political bloc, which is shown by the majority of young voters who made the difference, as concerned about their future in the European Union.
Gary Glitter banned from traveling abroad.
Courts have banned the glamorous rock star Gary Glitter, accused of child sexual abuse, expatriation in France and Spain.
The magistrates have imposed a ban Glitter six months after he expressed to the authorities who controlled his intention to travel to Spain via France.
Kent Police had given the travel ban on Thursday after proving the guilt of the magistrates Glitter for child sexual abuse.
Glitter, or his real name Paul Gadd, was not present at the hearing the court jurisdiction limited Ashford, but was still represented by counsel Corker Binning.
A court spokesman said "Thursday, September 25 the court to Ashford, Kent Police has requested an application to prevent Mr Paul Gadd to travel to France and Spain until March 25.
"Paul Gadd was not present then."
Glitter, 64ans, informed the authorities that he wanted to go abroad, even to be registered in the list of accused of sexual abuse.
He must inform the authorities if they wish to go abroad for more than three days.
It must also inform the police 7 days before the date of departure.
If it does not communicate its movements to the authorities, it could serve a sentence of up to five years imprisonment.
Kent Police said it would not discuss specific cases or potential movement of Glitter in the telling.
A spokesman for Kent Police said "The Kent Police will do everything necessary to protect our children as those from abroad.
"We believe it is easier to monitor someone who is in the UK because we have devices capable of managing any potential risks so much more effective.
"Protect the inhabitants of Kent is the most expensive to the Police for Kent, and we monitor the behavior of those who are accused of sexual abuse in the region, in order to minimize potential risks to the public."
. Glitter returned to the UK last month after serving 27 months in a Vietnamese prison for abusing two girls, respectively 10 and 11 years.
When he was released, Glitter flew to Bangkok where he would have to embark on a flight to London.
But he said they do not feel well, and refused to leave for London.
The Thai authorities blockaded at passport control, and in the end, he went to Hong Kong.
The Chinese authorities have denied entry to their territory, and thus was forced to go back to Bangkok, Thai police and immigration officials insisted he does return to England.
He finally arrived at Terminal 3 at Heathrow Airport on August 22, and remained there while his lawyer, David Corker, went to the court of limited jurisdiction Uxbridge, West London, for the registered in the list people accused of sexual abuse, as required by Scotland Yard.
In the past, Glitter was already serving a sentence of four months in the United Kingdom, for possession of images of child abuse.
A source from the Ministry of Interior said Jacqui Smith, the Home Secretary was pleased and reassured to know that Glitter had been banned from traveling to France and Spain.
"I photograph the master out of the scene to capture elements of his character" Günther Bauer - Photographer
Or heels or of opening clothes.
The essence of the great masters of flamenco, free from all tensions for the relaxed look of the man or the woman.
On one side the artist.
On the other person.
Inseparable except in private, in these times unknown to the general public, where we discover the intimate gestures and stolen artists who do not care to go on stage looks.
German Günther Bauer mixture "Flamenco - people" the theatricality of some staged with singers, dancers and guitarists with this lesser known artists side.
In this project, the photographer takes the particular iconography of flamenco from different angles.
Included in the programming of the Month of Photography Flemish, the exhibition "reflects the international importance of flamenco, most every day," says the designer, which clarifies that "Flamenco - people" "can be anyone but after seeing the photos, the viewer realizes that these are not typical pictures of artists on stage.
These people photographed "on the street" artists are able to convey on stage passion, sadness, joy ... captivating the audience.
To capture moments of personality of these artists do not make pictures on stage.
They have a personality and its own character.
What interested me was to create an intimate atmosphere that allows me to capture with the camera moments of stars of flamenco personality. "
With the festival "Song of the popular Mines," Bauer began in 1997 a long journey to photograph singers, guitarists and dancers with a camera plate.
These are portraits, through the choice of the camera and equipment, recalls the classic photography.
The implementation of different stylistic break with the classical side of the image, giving it a touch of modernity, this reflects the perception of flamenco by Bauer: "Music with very traditional roots that evolves and surprises every day ".
There is no dancing or singing in itself, but the personality and character of the artist who captivates audiences with his art.
The search for the essential and magic has been constant this work we present these days in the gallery El Fotómata.
The stars of flamenco as Diego El Cigala, Chano Lobato, Cristina Hoyos, Enrique Morente, El Lebrijano, Antonio Canales, Vicente Amigo, among others, are part of the selection from about seventy artists photographed.
The project has turned into an anthology of flamenco, which will soon be published in a book collection of portraits exhibited at the gallery.
Passion for portraits Bauer led him to repeat the idea two years ago with "Portraits of old sports" ("SportARTproject").
Although the concepts are different in "Flamenco - people", the photographer admits he loves photographing portraits of people, knowledge and power into their lives for a minute or longer.
I believe that in the portrait photography is the most difficult genre.
You find yourself in front of people, characters that sometimes you do not know or leave you a few minutes to do their photos.
Despite these circumstances, as a photographer, I always try my ideas become reality. "
This collection of portraits of the current flamenco entitled "Flamenco - people", is exposed to the El Fotómata Gallery, located at number 20 rue de la Mata (street parallel to the Tree of Hercules) will be open until 16 October.
Vargas Llosa's novel confesses that he writes is "real courage"
The novel is set in places that nobody knows and deals with unknown subjects, but once again, Mario Vargas Llosa is committed to advancing the new project he's working on a novel whose main character Roger Casemant, an Irish nationalist who lived twenty years in Congo and went through the Amazon.
The favorite for the Nobel Prize for Literature yesterday confessed to the Hay Festival Segovia, the novel that is currently "is a real bold" and that "all showed that he should not write."
"If I were reasonable, I would not do it, but I'll do it and I hope to finish it," said he concluded his speech at the festival exchange of ideas and thoughts for four days has seen in the city of water a hundred writers, historians and journalists, and thousands of people.
The author of "The City and the Dogs" was the most anticipated of the third edition of the festival and has fulfilled his contract character.
Vargas Llosa, who won the Hay Festival in the majority of the participants, was packed theater Congratulations to Juan.
The presenter of the Festival, Felix Romeo, came face to a fascinated public has not seen past the hour during which the Peruvian, with a prodigious memory and a large dose of humor, recounted the birth of his literary vocation, which is due to "his thirst to read" and "new experiences" how he wrote a "very methodical" through intense work documentation, correcting and rewriting some text to cope with the "lack of inspiration", how Faulkner, Victor Hugo and Alexandre Dumas influenced his vocation and how his memories inspired his novels.
The Spanish-American novelist acknowledged that "there is no way" to measure and whether life-changing books. "But I refuse to believe that literature is pure fun, a fleeting experience," said Vargas Llosa, who said that it "affects" and "makes people less the same" as asked writers "not to indulge in frivolity" and fulfill their vocation.
Bad weather spoils the fair Pozoblanco
The festival which concluded banderillas bullfighting at the fair Pozoblanco was suspended yesterday morning after the bullfighters on horseback have verified that the arena was impractical.
In this way, the organizing committee, in accordance with Fermín Bohórquez, Pablo Hermoso de Mendoza and Leonardo Hernandez, decided to suspend the celebration of the bullfight.
The wrong time is hard on this show, because ultimately both parties on three could not take place.
Saturday's rain which prevented the celebration of the second running of the bulls expected.
A poster, there was José Luis Moreno, Curro Díaz and Juan Bautista, who should compete in the arena of Castilblanco
And one party was held Friday
Friday, the winner was Daniel Luque cut three ears and was carried in triumph, after arm movements facing the bull with taste and aesthetics.
The afternoon concluded Alejandro Talavante two banderillas planted on the bull's back and cut the bleachers cheered discovered more than his fight itself with the bull ear.
Worse for El Juli, who entered the arena of Los Llanos without pain or glory.
During his fight with the second bull, after a much better fight, he got whistled by most of the public.
Police control of a van in the province of Alava, two thousand kilos of hashish found
Five ten o'clock.
Traffic control of the Basque Police (Ertzaintza) at the border of the City of Armiñón (Alava).
Police arrest two occupants of a van and they both undertake the flight.
Loading, more than two tons of hashish, which stop them.
The police chased and arrested one of the two occupants, a 28 year old man, identified as A. A. J., according to information released by the Department of Interior of the Basque Government.
The arrested has been charged with drug trafficking and forgery.
The incident took place when various officials Unit Alava realized traffic control vehicles on the N-1, on the border of the City of Armiñón.
They were preparing to stop a van to inspect when the driver disobeyed orders, suddenly accelerated and control began.
The police began their pursuit until the vehicle stops two kilometers further down the aisle, where the two occupants to escape down in a wooded area.
Basque police finally arrested one of the two occupants and seized 2178 kilograms of hashish they carried and they found after inspecting the van, Iveco Daily.
The rear part of the vehicle was loaded with bales of hashish. Then they proceeded to transfer to a police station for a thorough inspection and to weigh drugs.
In addition, officials have found that the license plate had been "falsified" because it does not coincide with that written on the registration of the van, which is also why they charged the prisoner a crime falsification of documents.
The Ertzaintza continues its investigation to arrest the other suspect, who managed to escape and to determine the source of the drugs seized.
The detainee, A. A. J. 28 years, has been in custody for carrying out the various steps and will be judged in the following hours.
The actress Heather Locklear arrested for driving under the influence of a drug
Actress Heather Locklear, the famous Amanda TV series Melrose Place, was arrested this weekend in Santa Barbara (California) for driving under the influence of a drug.
A witness saw her doing strange maneuvers trying to get out of his garage in Montecito, according to a spokesman of the police patrol of California announced to People magazine.
The witness said that around 16:30, Locklear "leaned on the accelerator, making a lot of noise, trying to get the car out of the garage, and going backwards several times, she rolled onto her sunglasses" .
Shortly after, the witness, who at first did not recognize the actress, saw Locklear stopped in the middle of the highway and got out of his vehicle.
This person, at that time, called the emergency services because "she was concerned for Locklear's life."
When the police patrol arrived she found the actress sitting inside his vehicle partially blocking the road.
"She looked confused," this is why the agents took her to a specialist center in drugs and alcohol to take a test.
According to a spokesman of the police, the actress has been cooperative and alcohol abuse was dismissed early, although "according to the observation of police officers at first glance, we thought Locklear was under the influence of a drug. "
Locklear was arrested are suspected of driving under the influence of a substance that was not specified and was jailed to 19.00 hours and released a few hours later.
Two months ago, Locklear is discharged from the clinic in Arizona where she was detained for treatment of depression.
Llamazares requested the Andalusian Federation of United Left to assume its responsibilities in the Silva case
The General Coordinator and member of the United Left, Gaspar Llamazares, said today that it is the regional federation to take a decision on the case of the former advisor of Youth and Sports of the Municipality of Seville, Francisco Manuel Silva, who resigned last week after being accused of making preferential treatment to members of his family.
"In these cases, I am very federalist, and it will Andalusian organization must assume its responsibilities," said Llamazares regarding the behavior of the political party that will be adopted in the council of Seville .
However, the leader of the United Left has requested that surveys reveal evidence of "transparency" for irregularities that could commit Silva: "The United Left has always defended this kind of business to have maximum degree of transparency ".
He also stressed that the political party has "strict ethical codes for all employees."
"Sangre de Mayo", the gamble of Garci
Inspired by stories of Benito Perez Galdos, José Luis Garci recreates the famous battle of the Spaniards against the French in "Sangre de mayo", which is the most ambitious film of his filmography with nearly 15 million budget .
The filmmaker has tried "to stage the many characters and illustrate social analysis" that has always admired the work of the famous novelist, he said today during the presentation of the film, with Quim Gutierrez and Paula Echevarría at the head of the long list of actors.
The film lasting more than two and a half hours, "Sangre de mayo" will make its release in theaters next Friday, which later became a television series for Telemadrid more than four hours.
Great admirer of literature Galdós, José Luis Garci sure to have done with this shoot with Esperanza Aguirre, who was charged three years ago, turning a memorial film for both "a childhood dream" hundred years May 2, Madrid, something he has always accepted when the account is held in the national historical facts.
15 million provided by the Municipality of Madrid Garci constitute a "unique opportunity" to play with the sets and clothing suitable atmosphere "a Spain that is the wrong leader for combat, since the struggle for independence led the people to rebellion during the reign of Ferdinand VII, "he reported.
But the filmmaker regret not getting funding for films like "Captain Alatriste" and "Goya's Ghosts" - more than double that obtained for "Sangre de mayo" - because he could not run for a few written in a script signed by Horacio Valcárcel, with whom he worked for most of his career stages.
The director of "Volver a empezar" influenced in his usual way of working on the staging of the actors, with whom he used to say before you start shooting and that he is not casting, since it seems to "humiliating" and considers that "the role of the director is going to the theater and cinema to stay informed."
Many actors in "Sangre de mayo" repeat on camera, as Rellán Miguel, Carlos Larrañaga or Fernando Guillén Cuervo.
Four-time Oscar hopeful (he won one), Garci considers that the three candidates who represent Spain this year at the Academy of Hollywood movies, "Sangre de mayo", "Seven French billiard tables" and finally the winner, "The Blind Sunflowers" are not representative of the young Spanish cinema, "which deserves to be better known," he said.
With this film Garci do not expect a price.
"At first you think you work for posterity, and then you realize that you work for prosperity, and now you're happy to make a movie and more," says Garci after more than 30 years of career.
Isabelle Bayón gets into the skin of the Sevillian dancer Tórtola Valencia
Sevillian dancer will pay tribute to a Sevillian dancer also.
Tórtola Carmen Valencia, daughter of a Catalan father (Florenc Tórtola Ferrer) and an Andalusian mother (Georgina Valencia Valenzuela), was born in the district of Triana and the age of three went to live in London with her family .
It was a free dance dancer and specialist oriental dances.
She was a pioneer exciting life, the liberation of women as Isadora Duncan, Virginia Woolf or Sarah Bernhardt.
It was a Buddhist and vegetarian and advocated the abolition of the corset which prevented the free movement of women.
The life of this woman who marked the history of dance in Europe between the wars, fascinated Isabelle Bayón.
"I wanted to work with Pepa Gamboa and it asked me to interpret the Sevillian dancer Tórtola Valencia and this seemed incredible."
According to the dancer, "We're not trying to tell his life but to translate his thinking.
The titles of his dances reminds me of flamenco.
Thus, "dancing butterfly" made me think of a popular Cuban dance and "snake dance" to some tangos.
Her dance was sensual and they told me that my way of dancing was identical to his own, "she says.
The staging was done by two outstanding contributions: that of Miguel Poveda who will sing again in Isabela one of his performances, as he had done in "La Puerta Abierta" and Professor Matilde Coral, which exceptionally kindly cooperate with one who was his student.
"Matilde Tórtola transforms into a mature character.
I'm happy because she has agreed to play a role in my work and it honors me. "
The staging is also done through musical composition and guitars Jesús Torres y Paco Arriaga, popular song of Michael Ortega, el Pulga y Moi de Morón, percussion El Pájaro, and the Rafa El viola Viola and collaboration of an actor, Juanfra Juárez, "who plays the role of the eternal companion of such artists who were considered divas."
This work also relates, in some way, the life of this woman who has exhibited in places so far away, especially for the time, as in India, the United States, or Russia, but throughout Europe, as ordinarily resident in London.
"I wanted to remember because I think that these are women who have a huge influence in their time and now no one knows and showcases his work," says Bayón.
The show will start at 20:30 at the Lope de Vega theater
The publication of "Diary of a newly married poet" concludes the triennium
The presentation of the first illustrated edition of "Diary of a newly married poet" in the church of St. Stephen's in New York, where Juan Ramón Jiménez married Zenobia in March 1916 was part of the activities provided by the Ministry of Culture of Andalusia to celebrate the "triennium Zenobia and Juan Ramón" (2006-2008), organized to commemorate the fiftieth anniversary of the granting of the Nobel Prize for Literature and death.
In this way, the "triennium Zenobia and Juan Ramón" comes to an end with the reissue of this work, with the International Congress held in New York, with the restoration of the Nobel Museum and the exhibition "Juan Ramón Jimenez: This poplar light "which was inaugurated in the month of May and, after traveling in different provinces of Andalusia, go to New York at the International Congress.
Similarly, the Ministry of Culture of Andalusia has bought eight hundred copies of "Diary of a newly married poet", edited by Pedro Tabernero and illustrated by Jacobo Pérez-Enciso, to continue the work of a of the most famous Andalusian poets.
America likes less without Paul Newman
"Sometimes God makes perfect people
Paul Newman was one of them. "
This sentence is the actress Sally Field, who worked with him in "Absence of Malice" and illustrates the desperation of American cinema, and throughout America, with the idea that striking Newman is no longer of this world.
He had trouble getting an Oscar
It only turned since 2007.
Everyone knew he was sick.
This was a blow to everyone.
"Sometimes one feels that exceeds any expression, and now I have lost a great friend," cried Robert Redford, "my life and my country was better with his life."
Nobody was afraid to make a fool or exaggerating.
One of the fathers of cinema and country died during a particularly dark period, where terrorists and stock markets scare, the U.S. believes has fallen far down, desperately seeking reasons of dignity.
When times are so hard and no reason to live, it is humans that admiration and it is not necessary to be Luis Cernuda to love Paul Newman.
He played for everyone an ideal of beauty and truth.
He was the enemy of Richard Nixon and the defender of lost causes and overcome, as the foundation for the anti-drug fight created in honor of his deceased elder following an overdose and the creation of its own brand of organic food.
It was a victory for a country that has been hard to win against a suicidal food culture.
This expansive wave of admiration swept Hollywood carelessly or nationalities or passport.
The latest James Bond, Daniel Craig in English, found no James Bond died before him.
Another Englishman, Oscar winner Sam Mendes, said that working with Newman marked the peak of his career.
The bad boy arrived from Australia, Russell Crowe, dare appoint Newman as his greatest inspiration.
"He set the bar high us," noted George Clooney, who is perhaps only now trying to break the screen as did Paul Newman: being very Honnet and having a serious privacy and off target.
It is not always easy or possible in the media jungle nowadays.
But there are those who try, and Paul Newman is an example.
After a divorce, he has been married fifty years to Joanne Woodward, whom he was faithful even though he had plenty of opportunities not to be.
"But why should I eat a burger out of my house, if I have a steak in my refrigerator?", He had the habit of joking.
In heaven, he assists with pride to meet his daughters with his fans on earth, something that is not so common in America.
"Of all the great roles he has played, he has never been as proud as the devoted husband, father love, caring grandfather and philanthropist," he says.
Madrid in the race to host the 2016 Olympic Games
And yes, the dream of many of us is that Madrid can organize the Olympics, after the failure in 2012, this could be achieved in 2016.
But I wonder if we are ready.
If we take the example of yesterday's race: we do not have!
They call it the perfect race, but I think it was the worst race I've ever attended.
If they had taken into account all the errors that occurred during the race, they would be a pass mark.
But look at everything in detail and from the beginning.
The errors start with the withdrawal of numbers, which forces you to go ahead.
This is not bad but if you do move it would be better that gives you everything (including the chip for racing).
Well no
They made you go there only to take the bib (first mistake, only to move it), and (after a long queue) surprise, there was only the size 'S' for the jersey ( Second mistake, because I need a size XL)
What kind of world do we live?
Is there because of the crisis they have decided to buy that suits small with less fabric and the cheapest at once?
Well, this is nothing compared to what happened on the day of the races.
Apart from the fact that you have to go early to remove the chip, the queue is 15 minutes and more, leave his backpack at the entrance.
The wait lasted more than 35 minutes, it is incomprehensible as 11,000 people are expected for these races.
Since there was a long queue, competitions started and we had not even left our backpacks at the entrance, but once done, the withdrawal was worse.
In addition, rain accompanied the wait more than 40 minutes that took place rebellions and attacks the hut.
I think about 500 people have pneumonia tomorrow, and some people like me do not even will figure in the classification with the exact time because the chip they gave me, which I think has not properly marked departure.
Of course, if they asked me to cite an example of a perfect race, it did not occur to me especially to the idea.
So I think we can always dream to become the host city for the 2016 Olympic Games.
Microsoft is looking for a receptionist (virtual)
At the Conference on Emerging Technologies Microsoft MIT was presented a new system image recognition and human interaction, a kind of Artificial Intelligence has little intelligence, but able to perform some basic tasks, such as calling a taxi (or in the case of Microsoft, a shuttle to get around the campus of the company) in response to what he was asked during a conversation.
With a camera and a system of recognition of shapes and faces, the "receptionist" can know how many people there are in place, that they are - including remembering what positions they occupy - and listen and hear the words keys of their conversations.
But also group them by conversation groups
In the video presentation, the receptionist detects a third person, but she understands that she does not belong to the group is talking with her and she is not part of the company.
She asks him if she's here to visit someone and she tells him she will meet him in a few moments.
All this without blue screen.
Impressive.
But of course this is the future.
Now the company has other things on which to focus, for example on the next version of its operating system, Windows.
This week we talked about in addition to a change in strategy at Microsoft.
Windows 7 will be lighter and will have much more associated programs.
Steve Ballmer has discovered that if computers were sold with the essential instead of unnecessary applications, they go five times faster.
This represents a breakthrough as Microsoft release after release, has not ceased to added features and "extras" to Windows.
The policy change is welcome.
Microsoft is right, its operating system loses significance but also its software.
When Google Chrome came on the network, I was one of those who adhered to the theory that Google Chrome is the first step on the part of Google to compete with Windows.
Many people have rightly pointed out that a browser is not an operating system.
The operating system will always be necessary because it is essential for the hardware and the software will include base.
It occupies the same function as your wife or husband when you have to say something to your mother.
This is true.
It will never go away but you should see the "death" of the operating system rather than as an absolute truth, but as a relative truth.
This week, Ballmer confirmed this idea.
People are less and less attention to the operating system, but increasingly the Internet browser.
It turns on the computer only to run Firefox, Chrome or Explorer and every day people spend more time surfing the Internet than to go windows.
Who are half of the applications in the system?
Who can do more can do less.
And Windows 7 will contain fewer applications, much less than Vista.
Lighter, months crowded, less complex.
For now, Microsoft is more interested to launch its own online services and finally they become an alternative to Google.
They desperately need this, indeed, and I will show you an example.
The picture presented in this paper, was taken earlier this month in one of the lounges reserved for employees in Redmond.
The vending machine, a poster asks them to use their own search tool - "Your search our future.".
In 2006, a study concluded that 66% of Microsoft employees using Google to search for information on the Internet.
Last week a delay occurred in the new version of Windows Mobile 7.
It does not come out in early 2009 but by the end of 2009 and see in 2010.
Microsoft surely try to launch Windows 7 and Windows Phone 7 right now.
The phone, after all, looks more and more like a computer.
But the launch of Android being late and the iPhone is already on the market, it will cost them dearly.
Le Fabuleux Marcel
Pablo Picasso endorsed on the French Riviera, Leonardo di Caprio wore in 'Blood Diamond' Edward Zwick, like Al Pacino in 'The Godfather' by Francis Ford Coppola and is part of the holding of the Association of Gay muscular.
And if we begin to list all of his appearances, one could also cite this beefy mustache that lifting weights in a traveling circus.
This is not a simple jersey cotton male body, casting and sleeveless.
The English called 'tank' but Fabuleux Marcel de Bruxelles stands out among all others.
First, by its flamboyant name - although it is known as the 'Marcel' - that has to do with the sport since it takes the name, according to legend, the boxer Marcel Cerdan, a lover singer Edith Piaf.
The 'Marcel' is distinguished from others by its excellent cotton, its unisex cut, by its distinctive logo and the small Belgian flag (barely recognizable) as the best known vests have in the neck.
But beware, because the Belgian company not only produces as tank tops.
But it also produces t-shirts, retro shorts, cardigans, cashmere pants cotton, babies, mini shorts ...
Clothes designed for comfort underwear.
Although it is a shame to only wear as underwear.
They are too charming.
"I want to become a young mother, the candidate does not care"
Its huge resemblance to his sister he was not prevented from developing its own personality.
Monica Cruz is small but full of vitality.
Currently the Cruz sisters take very seriously their new business in fashion.
According to Monica, they are not as beautiful and famous girls who lend their names.
She was there to promote the brand Mango has made Paris his new headquarters, but as well as the presentation of the most important awards of the Spanish fashion house sponsors.
Monica is warm and shy.
Tell us what you do in Paris.
I came to present the new collection that my sister Penelope and I have created for the new Mango for autumn-winter season, but also to attend the presentation of the second edition of 'Mango Fashion Awards' dinner and the Opera in honor of Valentino.
A very long day, but at the same time exciting, waiting for us.
What is the basis for your new Mango collection created for this fourth season?
The cinema of the 50s and 60s delights us and we draw heavily for our collections.
I love wandering around the city and see the women to see how they are dressed, how they combine their clothes, I often do.
Dancer, actress and designer, you are a very versatile woman, is not it?
I think yes, but eventually everything comes together and these activities have a lot in common.
Since I was little I liked the clothes, I wished to go to my grandmother to look in the cupboards to see my aunt and her clothes.
It was great, almost better than going to the amusement park.
Then when I became a dancer, I always tried to take care of the way I dress.
The dancers really like to dress up for the courses and tests, to look in the mirror and feel good.
And in the role of an actress when you endorsed the clothing is at this point that you're actually put into the skin of the character.
Suddenly, everything is connected.
You were not there long 30 years: it was it hard for you?
Not at all.
I feel better than ever, my 30 years I rejoice.
I think the woman is more mature, has more experience and enjoys life with fewer problems.
The biological clock does not scare me.
I did all the things I wanted to do since I was little and it gave me a lot of inner happiness.
So do you think becoming a mother?
Of course, I want to become a mother because my body asks me, and again, I want to become a young mother, I do not want to lose that.
Regarding the candidate, I do not care.
What I will do is give a lot of happiness to my son and raise him with love.
To get to the cinema, you expect that the different films that you turned out last year.
It's true, I can not wait that out.
Me, a woman from the theater, I am very anxious and worried, I would have everything now but of course this is not possible.
I look forward so that the films 'La última hora' and 'In the busca tumba de Cristo'.
See what you think ...
A few days ago you started on the catwalk with Naomi Campbell, is not it?
Do not say that!
I'm not up to the bridge to the model.
Quite simply, Naomi Campbell called me, I know for quite some time, for inviting me to participate in a parade in London for his charitable organization for the support of women and the clothes we exhibions - j ' have exhibited two of our clothing collection created for Mango - were auctioned to raise money for the NGO Naomi.
People Naomi is a person with a tender heart.
They say so much about it, I know it, many things are not true.
In addition, if the right side of Naomi fascinates me.
She asked me to march for a noble cause, but if she had asked me to do a headstand, I would have done anyway.
The important thing is to make life better for women in the Third World.
Repeat offenders of drunk driving will install the 'alcolock' system
The Interior Minister wants the driver who had more than three administrative penalties for alcohol, having to install in his vehicle a system that prevents starting the vehicle while intoxicated, or if it does not breath.
The initiative has already been announced in the month of June and it now appears in the report of the Minister of State in which the initiative is seen as a pilot project last year.
Its purpose is to reintegrate the driver by offering him during road rehabilitation.
The Minister of State road safety but also the General Directorate of Traffic Safety and the Institute for Security Technology Foundation of the automobile involved in this initiative.
According to statistics, between 30% and 75% of motorists arrested for driving more than once intoxicated, take the car.
The alcolock avoid it because it is connected to a vehicle that measures the level of alcohol in the breath and prevents the vehicle from starting if the driver does not blow before system, or when the driver's alcohol level is than allowed.
The cost is higher than 1,000 euros and is the responsibility of the driver.
In this regard, a study in the United States in 2007 showed that vehicles with this device reduced to 65% of offenses during the first year of installation.
And in Spain it is estimated that it could save the lives of 115 people each year.
This relying solely on administrative sanctions for two reasons: to address these behaviors before they become criminal offenses.
And facilitate its implementation, since the legal reform can be done by ordinary means, but, however, the reform made by criminal way requires reform of the Organic Law.
The device is not yet available on the Spanish market in any commercial form, although some industrial vehicles and already has a function as experimental.
Specifically tomorrow, the Congress of Deputies vote an initiative of the Spanish Socialist Party proposes to install on school buses this system as was done in France.
Mexico without 'peep-toes'
5:40 p.m. A precise, formal scheduled time, the aircraft of the Spanish Air Force in which the Princes of Asturias traveled landed in the presidential hangar of the Benito Juarez Airport in Mexico DF.
The sun was about to go to bed but its rays still forced to put their hands as a shield so you can see the royal pair off the plane.
At the foot of the stairs, the Spanish ambassador and other officials were present.
A few hours earlier I had asked in the street, the taxi driver if he knew that the Spanish Princes visited the city to complete their official travel.
- Ah, well, suddenly you can not go to the airport to pick up customers at this hour ... Are you here, or ...?
- No, sir, I am Spanish but I've lived here two years thinking.
- Ah, well ...
But the Mexican press knows who the Princes of Asturias and knows the importance of travel.
They are more waiting in the airport hangar near the red carpet and a military row consists of 27 marines.
The Prince is smiling and dressed in navy blue, Princess, for its part, has the wind in your hair, is dressed very conservatively and do not wear his 'peep-toes' routine, perhaps they had told him that a storm threatened.
They make a brief stop with photographers before entering the room where the official procession ahead.
At the door of the hotel where they are staying, one of the four largest hotels in the city, a fun Mexican television reporter ahead.
The most prestigious fashion
There is surely no more appropriate place in the world to present an award that Paris fashion and are certainly not most extraordinary designer living and good living as Valentino.
Mango has presented the second edition of Botón-Mango Fashion Awards, to strengthen the international image of the new fashion talent.
The winner will receive a prize of 300,000 euros.
Yesterday Sandrina Fasoli, the Belgian output winner of the first edition, the models looked in the window of Mango at 54 Boulevard Haussmann in Paris and she was almost crying with emotion.
Certainly it is the second largest brand store in Europe that has been opened with 1,335 square meters of surface.
The first store in London.
Events, as well as the desire to thank the designer Valentino, president of the jury, we have found ourselves in a luxurious dinner at the Opera Garnier in Paris.
With neighboring table as that of the extraordinary family Chagals the presidential table prepared by Mango, seemed even more spectacular.
Having heavy heart and doing a bad job against heart, because of the recent death of his brother, Nati started Mango clothing and some ornaments of Elah, which cut the breath, and arm in arm below with his son Luis - a handsome almost two meters tall - she accompanied her Valentino dinner prepared in his honor.
Andik, the owner of Mango, a gentleman, and Baron Rotchil ended the evening without a jacket because they had lent to two ladies.
Monica Cruz, who came to the store with a pair of trousers and a shirt - from his own collection - and for dinner has been transformed by donning a sexy black robe, was moved when during the night tour opera, accompanied by Goya Toledo, they showed us the ballet rehearsal room and remembering the good old days, she grabbed one of the bars and made the gesture of a 'big folded'.
Inés Sastre did not stay to visit the dependencies of the palace, but she showed us in on his cell phone pictures of her son.
The next morning, we had the pleasure of seeing Olivier Martinez - another handsome man who moves a motorcycle - and John Travolta, who arrived at the Hotel Intercontinental in Paris, with her sheets, towels and her having asked first, that there is no odor in his room.
The stars in the night sky of Paris.
Oops, that's life.
1001, the number antistress
There are not only 1000, but 1001 ways to forget the chaos and frenzy of everyday life.
And to top it all, they are all listed in a book that will bring relaxation to bookstores on September 30.
The alarm almost saddens us when it rings every morning at 7:00, but it's even worse when you consider the pace we needed agitated life today.
The office is synonymous with power and computer back pain.
Stress is the evil of the XXI century.
But it is neither one nor two methods to fight daily fatigue and problems related to the workplace.
But in 1001, nor more nor less.
Apart from the yoga positions, classical massage or treatment 'spa', Susannah Marriott brings the pages of a book while a 'menu' of methods adapted to the taste and time of each.
The work is called anti-stress '1001 ways to relax' and will arrive in bookstores directly from the publisher Pearson Alhambra and DK.
If anyone thinks that it is not possible to achieve peace in places like work or through personal relationships, 'manual' denies such a belief.
In addition, this manual provides other methods such as contact with nature or 100% natural recipes that help you relax.
If adrenaline is not running in your veins to restore the balance of your body and if the stress has become a problem, it is time to sit on the sofa, to disconnect from his mind and focus on reading .
Talking in your sleep
Some children speak overnight.
I do not refer me to those who wake up very awake by telling us something that happened the day before, but the children who in their sleep.
The first time it happens it may surprise you, but in reality it does not matter.
It is a benign alteration of sleep called sleep talking.
This is quite common, especially among children and adolescents.
Sure there is more than one who speaks for the night.
This can occur very sporadically (once in life for example associated with an episode of high fever) or more periodic (daily, once a week, once a month ...), the day after the child does not remember anything.
There is no single cause that determines its appearance
They are often related to other changes in sleep as nightmares, night terrors, nocturnal enuresis (bedwetting) or sleepwalking, but this is not always the case.
As we said before, they can also be associated with very high fevers in situations of stress or excitement.
Either way it is a little studied phenomenon.
The intensity with which it occurs is also very variable.
He may speak with a quiet voice, with single words, murmurs or otherwise with shouts, tears, long speeches ...
In case somniloquy becomes very frequent, it would be wise to observe the child and see a specialist to see if there is a problem that causes a lot of anxiety and to get an explanation for this problem.
We said that this is a benign alteration, which is why there is no treatment, unless it is related to another sleep disorders that can be treated (for example, if it is linked to sleep apnea or stress).
What we can do is to take into account a number of simple preventive measures such as:
Try not to excite the child before going to sleep.
Therefore look for quiet games and avoid programs or television shows that are more or less violent.
With very nervous children who have difficulty to relax, relaxation techniques can be used to help calm down inside.
This will allow the child to have a more peaceful sleep.
Once the somniloquies appear try to remain calm.
Remember that they are harmless to the child and the next day he will remember more of what happened.
Useful Tips
Do not wake up.
It is useless because it is unconscious and you réveilleriez.
Even if he speaks, he sleeps and then rests.
Remember that it is very anxious several times, it is advisable to consult a doctor or check out what causes so much anxiety in the child.
If you understand what he says (which is not usual), do not be tempted to ask for information.
You will get nothing, because sleeping, he is not aware in order to organize his thoughts.
In addition, you will hear what he says, but you do not know what he is dreaming, suddenly pay attention to the way in which you will interpret the information and the conclusions you draw.
Never tell a child that you can ask during the night to know his secrets.
Not even joking.
This causes a lot of anxiety.
In conclusion, do not worry, it's nothing too serious, it's an episode that lasts only a few minutes.
Illhaeusern ... finally
Illhaeusern finally found the way to victory on the field after a long period of scarcity.
Without a big game, the Yellow and Black have created the largest number of occasions and have managed to turn one for the win.
The pace was not very strong at this meeting where the attackers had difficulty expressing themselves.
After a first attempt Captain visitor Kauffmann that bordered the window on a long range shot, Illhaeusern would take slightly upward and turn Fonderflick far, then with Hirn above, the Roman toe or Diebold came tickle defense Dannemarie.
In front, there was block in midfield and just let the stirring Riahi at the forefront of the attack.
The start of the second half was going to be decisive with first two occasions and signed Riahi Temporale for Dannemarie, immediately after the opening goal for Illhousiens by Marais, well positioned to resume a postponed a first attempt ball Diebold (53 ').
But Illhousiens scorer can not enjoy happiness long and will have to return to the locker room a dozen minutes later and let his teammates outnumbered.
But Dannemarie not enjoy it and will not pose major problems to illhousien Eleven has just dropped a bit to "compress" his defense, except in the very last seconds of the game when, after a big mess, the ball going very around the cross.
Sarkozy to meet angry fishermen
Before leaving for the United States, Nicolas Sarkozy will make a detour to the UK.
Faced with the show of force fishermen who disrupted Monday access more Brittany and Normandy ports, the President decided to go on Tuesday morning at the port of Guilvinec, in Brittany, to meet with their representatives.
They have promised to host "in a constructive spirit" and hope that it "will come up with concrete proposals."
A presidential visit that falls at the same times that a general meeting of the "crisis committee" created by the Breton fishermen for measures to deal with soaring fuel prices, which peaked at more than 1.14 euro per liter on average.
According to spokesman David Martinon lElysée, the president "and discuss them with solutions that can be devised to help their businesses regain competitiveness and to secure the conditions of employment and remuneration of sailors."
Nicolas Sarkozy is expected to firm up by fishermen.
Tuesday morning, they conducted operations in Morbihan snails and Calvados, causing jams near 10 km.
The harbor of Quiberon was also blocked, but the links to Belle-île not stopped.
A filter dam has been underway on the Quiberon peninsula.
The sailors have already shown their determination by burning Monday at dawn, tires and pallets to a fuel depot port of Brest and Lorient, while demonstrations were held in Concarneau and Saint-Brieuc.
The movement has spread to other ports on the Atlantic coast and the English Channel, as Sables d'Olonne in the Vendée, where trawlers remained docked, and Le Havre, where about twenty boats blocked movements of merchant ships.
The fishermen Turballe and Croisic in Loire-Atlantique, were stopped in the evening the blockade of major Total refinery of Donges.
Those of Boulogne-sur-Mer decided to wait until after the Wednesday meeting at the Ministry to decide any action.
Guilvinec to the "crisis committee" should indeed decide Tuesday what action to take in the movement and its participation in the interview under the Ministry of Agriculture and Fisheries in Paris.
But some Breton fishermen do not want to be represented by officials of the National Fisheries Committee, which did not support their movement.
"The strike will continue" because "the fishermen will not leave anything" and "do not want to move to Paris," for example, announced Liliane Cariou, the President of the Fisheries Committee of Lorient.
Professional fishermen who do not pay taxes on diesel, currently paying about 50 cents per liter, but they believe that the breakeven boat is achieved with a lower diesel 0.30 liter .
Paul Newman the beautiful
The unforgettable interpreter of "Butch Cassidy and the Sundance Kid" has died of cancer at the age of 83 at his home in Connecticut.
Hillary and Bill Clinton, Nicolas Sarkozy, George Clooney, Julia Roberts, Robert Redford or Sam Mendes welcomed the screen legend and actor engaged, Paul Newman, died at age 83.
Embraer maintains its delivery forecast for 2008
Brazilian aircraft manufacturer expects 215 aircraft deliveries this year despite the threat of recession looming over the global economy.
The fourth largest aircraft manufacturer, Embraer, maintains its delivery forecast for 2008 with 215 aircraft delivered, reiterated Fredrico Fleury Curado, its president.
In the first half, the manufacturer delivered 97 aircraft.
The Brazilian manufacturer hopes many of the Chinese market, particularly for its aircraft in the range of 30 to 120 seats.
To date, Embraer delivered 41 aircraft to Chinese customers in eight years.
AIG plan to sell more than 15% of its assets
The insurer American International Group, the U.S. monetary authorities have bailed, plans to sell more than 15% of its assets to repay the $ 85 billion that have been advanced to him, according to the Sunday edition of the Financial Times.
AIG is willing to consider the sale of most of its activities beyond its life abroad and its pension business in the United States, the newspaper said, citing sources familiar with the matter.
The Board of Directors of AIG met Sunday evening to discuss possible sales, according to the FT.
No confirmation could be obtained from AIG.
Assets that AIG plans to include separate its leasing subsidiary Air International Lease Financial Corp.., Its 59% stake in reinsurer Transatlantic Holdings and its real estate portfolio and investments in private equity, says the FT.
No final decision has been made on these sales, says the FT.
AIG must quickly realize cash to repay the loan of $ 85 billion it has made the Federal Reserve at the risk of the U.S. authorities to take 80% of its capital, diluting existing shareholders due proportion.
Paris Historical Analysis of the session Morning Meeting Morning Meeting History
The New York Stock Exchange showed a record fall Monday after the rejection by the House of Representatives of the Paulson plan to rescue banks: the Dow Jones lost 6.98%, or a loss ever approaching 800 points and the Nasdaq 9.14%.
The Dow Jones Industrial Average (DJIA) plunged 777.68 points 1O.365, 45 points.
In terms of points, the biggest drop in its history (684.81 points) had previously been registered on 17 September 2001, the day of resumption of trading after the terrorist attacks of September 11.
The Nasdaq, dominated by technology, sold 199.61 points 1,983.73 and the broader Standard & Poor's 500 index 8.81% (or 106.85 points) to 1106.55 points, according to final figures Closing.
Already depressed in early trading, Wall Street sank after the unexpected by the House of Representatives of the bailout of the banks was expected to regain some stability in the market rejection.
By 228 votes for and 205 against, the representatives refused to Treasury Secretary Henry Paulson how he wanted.
Nearly two out of three Republicans rejected his plan.
"This is a bad signal to the market, which sees unable to adopt a plan Congress," said Lindsey Piegza of FTN Financial.
"This shows how much the market had on this plan," she added, fearing a project adopted in several days arrives "too late."
"If the project is actually dying (...) then the relay will be passed quickly to the Fed (the U.S. central bank, note) and other central banks to manage the crisis, which would further strengthen the credit conditions," said defendant Brian Bethune, chief economist at Global Insight.
And further accentuating the sense of urgency, "each day brings the fall of a financial institution" in the United States, said Ms. Piegza.
After the bankruptcy of Washington Mutual Friday, the authorities organized the takeover of Wachovia banking by its rival Citigroup.
In Europe, the crisis has accelerated sharply, pushing the emergency response to banks in the UK, Benelux, Iceland and Germany, a sign that markets face "not just an American crisis but a global crisis, "said analyst FTN Financial.
The bond market rose sharply.
The yield on the 10-year Treasury fell to 3.632% against 3.827% Friday night, and the 30-year 4.161% against 4.357% yesterday.
Obama, who won the points of the first televised debate
In the first debate on Friday between the two candidates for the White House has succeeded another to know that John McCain or Barack Obama, won.
Unsurprisingly, HQ Republican and Democratic campaign proclaimed their own victory in the televised debate that was followed by a third of American families.
Political analyst David Gergen believes that the provision of John McCain, but honorable, was not quite "brilliant" to allow him to stop his fall in the polls to five weeks of the presidential.
The Gallup poll, one poll published Saturday grants five-point lead Obama (49% against 44% for McCain), believes that this is the Democrat who pulled out of the game
Among undecided voters, who are the ones that count, Obama was the winner with 39% of respondents, while 25% of them give the victory to McCain, according to a CBS poll.
Obama is expected to confirm his lead Thursday with the expected good performance of his running mate, Joseph Biden, at the first and only public debate with his rival, Sarah Palin.
"It would be a mistake to underestimate.
She has good instincts, "but warned Bill Clinton this weekend.
The septuagenarian McCain has never ceased to emphasize the unquestionable experience in foreign policy, stressing the "naivety" of his opponent on the issues that were at the heart of this first face-to-face.
"Senator Obama does not understand that ..." Has he accused several times.
"I do not believe that Senator Obama has the experience and knowledge to be president," he also assured.
An angle of attack hammered yesterday in Republican television commercials.
Obama himself has said that he represented the future.
Undaunted, he showed concise and accurate.
He highlighted his ability to make the right decisions, and to restore the image of the United States in the world.
"McCain has not understood, while Obama if" retorted, this weekend, a Democrat spot criticizing the Republican for not having taken the full measure of the impact of the crisis on the " American street. "
"During the ninety minutes of debate, John McCain had a lot to say about me, but nothing on you, Obama denounced yesterday before 20,000 personnesrassemblées for a campaign rally in North Carolina in the pouring rain .
He did not even utter the words "middle class" or "workers." "The financial meltdown clearly benefit Obama, who is regarded by the Americans as the most likely to save the economy to the brink.
"The coming week could be a turning point," thought yesterday, the influential Democratic Senator Charles Schumer.
Democratic Representative Rahm Emanuel, a former member of the Clinton administration, compared the "good economic instincts" Obama to those of Bill Clinton during the 1998 financial crisis.
For the Democratic candidate, the current debacle "is the final verdict of eight years of bad economic policy implemented by Bush and supported by Senator McCain."
Reaffirming succeed still cut taxes 95% of Americans despite the turmoil on Wall Street, the Illinois senator also noted that the implementation of any energy independence by promoting renewable energy was its first priority, with the establishment of a health insurance system.
McCain, he wanted to build a fleet of 45 nuclear power plants by 2030.
Cautious, both candidates dodged questions about the financial rescue plan of 700 billion dollars (470 billion euros) last night passed by Congress and extremely unpopular.
In Minsk, "you noticed that there was an election, do you?"
Young and opponents showed Sunday night on the main square of the Belarusian capital in advance to reject the results of parliamentary elections.
Some hundreds of Belarusians gathered Sunday evening at the closing of the polling stations in the central square of Minsk to protest against the fraudulent parliamentary elections.
While no results have yet been announced, many young people had come to protest against the regime of President Alexander Lukashenko, "the dictator resignation."
Some admit they have not even vote: "What good do what they want because of my voice," said one young.
They do not believe that the regime did well to foreign observers in order to resume talks with the European Union is ready to make a shift to democracy.
Sanctions, including a ban on visas for 40 Belarusian officials and the freezing of certain assets could be lifted if the elections were considered by observers own.
They have not been in the opposition.
"We were kept out of electoral commissions and our observers were not able to attend the recount," lamented Yuri Potemkin, the spokesman of the Union of Democratic Forces, a heterogeneous group of twelve parties.
"This is a cosmetic change, says Alexander Milinkevich, former opposition candidate for president in 2006 and leader of the pro-European movement, because the important thing is who counts the votes, and in us is the executive.
If the opposition entering parliament is that they have been appointed, not elected.
But their entry into parliament can mean space on television, meetings in the regions and proposed laws. "
The opposition must therefore enter the political game because "we must engage in dialogue with the European Union.
For if our economy, which is heavily indebted vis-à-vis Russia, is in crisis, and we do not reform, we risk becoming a protectorate of Russia.
Now we want to be independent. "
The opposition fears that the Organization for Security and Cooperation in Europe that followed the electoral process does not recognize the validity of the election.
She stressed that participation numbers seem too high, and the generalization of advance voting (26% of voters in Minsk) has opened the way to manipulation.
"You noticed that there was an election, you? Asked the Social Democratic leader Alexander Kozulin, one of the last two political prisoners released in August this year.
There was no one in the polls.
And there will be a maximum of five members of the opposition in parliament, those best suited to power. "
The silence of the night falls on October Square.
On television, President Lukashenko and members of the Central Electoral Commission welcomed their success.
Interview - Blood returned safe
Hema-Quebec yesterday celebrated the 10th anniversary of its foundation, and its president, Dr. Francine Décary had reason to rejoice because Hema-Quebec has become a supplier of blood safer and efficient in the world.
Above all, he has regained the confidence of the public who had been seriously undermined by the tainted blood scandal in the 1980s and 1990s.
As we know, the national blood supply managed by the Transfusion Service of the Canadian Red Cross have been infected with virus (HIV) and hepatitis C during the 1980s.
Before this drama and public discontent, the government of Canada established in February 1994 a public inquiry, headed by Justice Horace Krever inquiry that sought to shed light on the circumstances that led to this tragedy and to make recommendations for such a disaster never happens again.
While Krever slow to submit its report, while some provinces have set up a committee with the aim of planning a new system for managing Canada's blood.
In Quebec, the Gélineau Committee completed its mandate.
Following Gélineau and Krever report, two suppliers were created in Canada: Hema-Quebec to serve Quebec and Canadian Blood Services to supply all other provinces and two territories.
"In 1998, when Hema-Quebec began its activities, only 38% of people still had confidence in the blood system in Quebec, recalls Dr. Décary.
The situation was discouraging.
By dint of efforts to improve the safety of blood products and fieldwork during the years that followed, we regained the public trust, "she said before proudly say at the beginning of 2008, nearly 94% of Quebec's population now had confidence in Hema-Quebec.
However, Dr. Décary keep in mind that "trust is something very fragile thing."
Since its inception, September 28, 1998, Hema-Quebec applied the precautionary principle.
At this time, there was in Europe at the outbreak of numerous cases of the human form of mad cow disease, new variant Creutzfeldt-Jakob says that holding the fort since its founding in 1998.
"And we did not know at all if the disease could be transmitted by blood.
It was then supported on a key recommendation of the Krever report and Gélineau, that when you do not know a serious illness and can result in the occurrence of Creutzfeldt-Jakob disease, which is characterized by brain degeneration leading inevitably to death, it introduces measures of exclusion.
In April 1999, has refused the blood of people who had spent over a month in the UK since 1980.
But a few years ago, it has been demonstrated beyond any doubt that this disease is transmitted by blood.
This episode has shown us that the precautionary principle was applied made sense. "
In 1999 appeared on the market a much more sensitive technique for HIV: the nucleic acid testing (NAT) that allow direct detection in the blood of donors for the virus itself and not the antibody against virus, which was based on the tests used previously.
TAN helped shorten the silent period, which extends from the time the person has been infected and when the first viruses can be detected in blood by our techniques, explains the specialist.
It was able to reduce this period to a period of less than one week.
It has substantially decreased the risk that some donors are infected without knowing it and they can not be detected.
These improvements have greatly reduce the risk of contracting AIDS through a blood transfusion.
Today, one in 12 million at risk of receiving HIV-contaminated blood.
"In other words, this means that it will distribute 12 million blood products before someone is infected with HIV.
As Hema-Quebec distributes each year between 400,000 and 500,000 blood products, it will take more than 24 years before the onset of a case of HIV transmission through a blood product.
I think we can now feel comfortable to receive and prescribe a blood transfusion to restore health, "said the head of the Hema-Québec.
"Our challenge for the next decade is to maintain the safety of our products.
You never know which pathogen will emerge in the system.
No later than last year appeared on the island of Reunion Chikungunya virus, like West Nile virus is transmitted by an insect in the blood.
You have to be constantly vigilant, "says Dr. Décary before emphasizing that in addition to secure supply, Hema-Quebec must also provide a sufficient supply.
"The needs are increasing as the population ages.
Cancer treatments are more aggressive, patients often need a refill of red blood cells or platelets.
The aging population also has consequences on the network of blood donors which includes an average of 3% of eligible to donate blood Quebecers. "
Anyone in good health, aged 18 and older who meets the eligibility criteria may yet give blood every 56 days, or six times a year.
On average, 14% of people who offer their blood are not accepted because they have AIDS or malaria, for example, and if they have traveled to a country where malaria is prevalent, they will be excluded for a period of one year.
"With these 3%, we can maintain an inventory that meets the needs of hospitals.
Shortages are rare.
But we must renew the members of this network of donors as they age and can no longer donate blood.
It is difficult to convince people to donate blood, but also to retain them and encourage them to become regular donors.
Life today is so rampant, we rarely find the time to spend an hour to donate blood, "laments Francine Décary.
With an annual budget of $ 297 million, Hema-Quebec not only provides blood products, but also of human tissues, including bone grafts, heart valves, eyeballs and skin that is almost exclusively used for large burned.
These tissues are analyzed, processed and frozen before being stored at Hema-Quebec, which also manages the only public cord blood bank in Quebec.
The umbilical cord was once considered as biomedical waste is full of rich blood stem cells can be used to treat serious diseases such as leukemia.
"We celebrated, a few weeks ago, the banking thousandth of our sample of cord blood and is expected to draw more than a thousand a year.
We should begin to provide for transplants at the beginning of next year, "says Dr. Décary that describes this sampling program of cord blood to be very popular.
"Many moms are disappointed not to be able to access" because Hema-Quebec does not have the means to offer this complex and expensive program in all Quebec hospitals.
Soccer - The Impact in the semifinals
The Montreal Impact has qualified for the semifinal round of the playoffs in the first division of the USL, thanks to a 3-1 win (4-3 on aggregate goals) over the Seattle Sounders yesterday during the second and final match of the quarterfinals series on aggregate goals, at Saputo Stadium.
The midfielder Antonio Ribeiro scored the decisive goal in the 90th minute of play
After a scoreless first half on one side or the other, midfielder David Testo and Rocco Placentino scored the other goals of the Montreal team.
Roger Levesque was the only one to defeat Matt Jordan for the Sounders.
Recall that in the first game of the series return on Friday, the Impact had suffered a 2-1 loss at Starfire Complex in Tukwila, a suburb of Seattle.
The Impact will face the Vancouver Whitecaps in the semifinals.
Saturday night in Minnesota, the Thunder rallied from a 3-1 deficit in the return match to win 4-3, but the Whitecaps still advanced to the semi-finals 5-4 on aggregate goals.
The Impact should face the Whitecaps on Friday and Sunday, but the details of the series will be confirmed today.
In short - victorious Kovalev Goal
The number one Canadian trio is ready to start the season.
The unit consists of Alex Kovalev, Tomas Plekanec and Andrei Kostitsyn led attack in a 3-2 Canadiens in a shootout against the Florida Panthers last night at the Bell Centre.
Kostitsyn, the first star of the game, scored a goal, Plekanec had two assists, and Kovalev picked up an assist in the win, the Habs fourth in six preseason games.
Kovalev gave the victory by scoring the only goal of the shootout.
"I'm not ready yet, warned Russian.
I need another game to feel comfortable. "
"He tried to do too much in the first period, noted Guy Carbonneau.
But I think he enjoyed the match.
He had a nice ovation. "
Charest placing on the North
The Prime Minister did not rule out an election before the end of the year
As soon as the meeting of the Liberal Party finished, Jean Charest went yesterday in Jean-Talon in Quebec, where the new health minister, Yves Bolduc (left) tries to get elected during the by-election today.
"Pushing the limits of our last great frontier of the north": this is the long-term ambition that Jean Charest presented with visual strength while remaining broadly at the end of the General Council of the Liberal Party of Quebec, Lévis yesterday.
Behind him during his speech was projected a kind of Image Mill.
Turning loop on three huge screens, spectacular shots of hydroelectric dams, mining, Quebec, seen by "Google Maps", maps, etc..
Major means as election period.
During a press conference, moreover, the Prime Minister refused to rule that trigger the election this fall, although he noted that his schedule was hectic.
The "Plan Nord" is the fourth pan of a "vision" that the Prime Minister claims to have Quebec, that of a "new economic space", which includes an agreement on labor with France an agreement between Canada and Europe agreements with Ontario.
Often mentioned in the speeches of the Prime Minister recently, the opening of the North - the Northern Territory at the 49th parallel - has never been the subject of a presentation.
The Prime Minister, however, merely explain why the North was "a gem with huge potential", but did not due, investment amounts, or specific priority in future projects.
At most a few avenues which could be further developed: in particular hydropower, forest, but especially the mining sector, boosted by growth in emerging markets and reconstruction of public infrastructure.
The North contains "nickel, zinc, copper, platinum, gold, silver, iron, titanium, and even diamond," according to the listing of Mr. Charest.
This "area twice the size of France", "this is our home, it is in Quebec.
Not only is it home, but it's us, "he insisted, as if to show that he sought a national founding myth.
Quebec has many built in its relationship with the North, he said: the gold rush in Abitibi, Québec engineering, James Bay.
"This is us, this is our future," he added, after a dramatic pause to contemplate the huge map behind him.
The North, 70% of Quebec's territory includes a portion of the Labrador Quebec has always claimed, said the Prime Minister at the press briefing.
"This is a traditional position that all governments have reiterated.
There is a border line on which there is no agreement for a long time and when the opportunity arises, I reiterate that position on behalf of the government, "he said.
Moreover, "with climate change, we must rethink our vision of the North", he said in speaking of the passage of the northwest, which is open all year due to melting ice.
In this new geopolitical context, the Prime Minister considers only occupy the territory is a duty.
And the inhabitants of the territory, First Nations and Inuit?
The Prime Minister said that the Government of Quebec would be very attentive to them and that the project would benefit them, especially young people.
Two former ministers from two different parties, Pierre Corbeil and Michel Létourneau (former PQ Ungava MP), have already started consultations with thirty communities.
An interdepartmental committee chaired by Benoît Pelletier and in which Julie Boulet (Transportation and Natural Resources) has an important place began work.
The Prime Minister does not "not necessarily a top" excludes a large meeting, but a time when "we give a common vision."
Northern Development would also comply with the principles of sustainable development.
The Plan Nord will be "coordinated, orderly and respectful of the environment," he promised.
Jean Charest described the "vision" as a continuation of the Liberal Prime Minister who preceded him.
"As the Liberals who have preceded us, we thought otherwise to turn challenges into new opportunities for growth and development."
This has also been a recurring theme of the weekend, which started Friday with a cocktail party to celebrate the 50th anniversary of the arrival of Jean Lesage at the head of the party.
One of the resolutions proposed to rename the Central Beauharnois Dam-Adelard Godbout.
"From Godbout, who created Hydro-Quebec, Lesage made the Quiet Revolution and the nationalization of hydropower, Bourassa was the James Bay, our party has been able to shape the future," said Jean Charest .
During a press conference, he cited another reference, conservative one, the "Roads to the North" program John Diefenbaker, prime minister from 1957 to 1963.
In addressing the proposed hydro-electric dam Eastmain1a-Ruper, Mr. Charest said that its commissioning was scheduled for 2012.
"It's still us, but I plan to be there," he told his supporters, instilling in them the applause.
Indeed, the Prime Minister, who said in April that there would be no election in 2008 and probably not in 2009, did not rule out the possibility of triggering an election this fall, the law it permits.
He stressed that his schedule is filled, however, including a mission board of the federation in China and Quebec-New York summit.
The General Council of the weekend provided the Liberal leader a platform containing nationalist resolutions, including "constitutional aspirations" that are passed as a letter in the mail: the QLP requires in particular the recognition of "specificity of Quebec" in the Constitution.
It also wants Quebec appoints members of the Council of Canadian broadcasting and telecommunications and that they have a right to veto decisions in Quebec.
The side of the opposition, was broadly welcomed the Plan Nord with skepticism.
The PQ leader Pauline Marois has emerged Development Policy of Northern Quebec and the Landry government had launched in 2001.
She said the Liberal government came to power in 2003, gave up applying.
Had he done so, "we would be more advanced today," commented Ms. Marois alongside its candidate in Jean-Talon (elections held today), Françoise Mercury.
The ADQ has expressed support for the adoption of the Plan Nord by the government.
"But what we want is that it is not just a show," said the leader Sébastien Proulx, replacing Mario Dumont, who returns from vacation today.
Letters - A disgraced country
This is Mr. Vic Toews, former Minister of "Justice" (ironically) in the Harper cabinet, which allowed last summer said Louise Arbour she was a "shame" for Canada.
Jeter and shame on this woman who has led a relentless struggle for justice and deserves our admiration says as much about the environment as Prime Minister Stephen Harper himself.
We are a government that is the only one of all the Western countries involved, not to repatriate its nationals imprisoned in the concentration camp at Guantanamo.
A government that does not take into account the fact that Omar Khadr was a young teenager at the time of the facts alleged against him.
The only government that, despite the fact that Canada has signed the Geneva Convention, breaks his word and let languish in inhumane conditions a child soldier.
The only one that relies on a travesty of justice to assess the guilt of the accused.
Us recall that UNICEF, Amnesty International and the Canadian Bar Association, among others, call for the repatriation of Omar Khadr that he receives a fair trial in Canada.
This is the same government that condones torture: whatever it is now a young adult psychologically destroyed, perhaps forever after so many years of abuse.
We do not yet reflect in, but we are now witnessing an insidious erosion of our rights, our freedom and our "democracy", the word that Harper keeps waving and sounds so hollow in her mouth .
Now is the time when no moral no longer exists: it can bully, torture, arbitrarily detain a Canadian citizen at the discretion of the head of a minority government so far (what will it then after 14 October ...).
Number of voters believe they will find salvation in a party that advocates Virtue, Law and Order: they do not see that the government has abandoned what made the reputation and dignity of our country.
Shame, Mr. Toews, it is in this renunciation, and not elsewhere.
Free opinion - The Orwellian speech Barrick Gold
In its edition of September 17, The Gazette published a letter from Patrick J. Garver, executive vice president of the Canadian mining Barrick Gold.
Continuing an Orwellian logic, it says that most of the world gold mining company filed a defamation lawsuit against six million three authors and small publishing house penniless in order to launch a "transparent public debate" .
While judges are independent and impartial, it is not the truth they believe, especially in the case of libel, but the law.
Not surprisingly, this fundamental difference is completely obscured by Garver.
As for Barrick Gold, the best way to conduct a public debate would it lead to ruin anyone who dares advocate a position contrary to his?
Whatever the outcome of the trial, the authors and publisher of the book Black Canada will spend considerable sums to prepare their defense and combat, with uneven arms against an army of lawyers supported by almost bottomless pockets of mining.
The tactics in this unequal struggle, is also often ruin the defendants to impose a settlement that bâillonnera opposition more scare anyone dare to revisit the issue.
If Barrick Gold really wanted a public debate, it is the court of public opinion it should have presented its view of the facts.
Unlike what happens in many countries where Barrick Gold works, the debate in Canada are normally by the exchange of ideas and not with truncheons.
It is therefore sufficient to mine to open its books, records and establish a real debate through newspapers, media, publications and funding of independent research teams that could shed light on the issue .
But Barrick Gold does not seem to trust the public opinion and rejected out of hand the petitions and letters of support to the authors of Black Canada.
Perhaps Mr. Garver could explain how it can both ask for a "public debate" while despising the opinions of the same audience?
In the world of Vice President, it seems that the word refers only to highly paid lawyers and not all Canadians, this is a rather narrow view of the concept.
In a democracy, even the critics have the right to speak.
That does not understand - or do not understand - Barrick Gold, is that the public supports the authors and publishers of Black Canada is primarily because it rejects the brutal manner of mining.
The public is ready to hear Barrick and judge, but on the basis of civilized exchange of arguments, and not as part of what many perceive as a SLAPP (pursuing the "public debate", Barrick Gold has just Besides filing a formal notice to the location of the authors of Black Canada telling them to stop using that word ...).
Beyond surreal speech Garver, further Barrick Gold is a direct attack against the freedom of academic research and the quest for truth, essential to any democratic society.
She denies block, the right to quote credible sources and discussion of the facts and interpretations that are the foundation of intellectual work.
If it is impossible to study and discuss issues that displease the rich companies of the world in a country like Canada, under penalty of prosecution repeatedly, which can?
If Barrick Gold really wanted a public and transparent debate, it may do so by following the scientific standards used by the authors of Black Canada.
She has a right of reply.
Academia, to which we belong, has long handle debates and disagreements and resolve conflicts.
The excessive pursuit of Barrick Gold clearly shows that, contrary to what she claims, she did not want an open debate.
This is a loss to the academic world, as well as for public debate in Canada, and it is time for governments to put in place measures to limit this kind of malicious prosecution.
Bailout of Wall Street - Democrats and Republicans agree
The Bush administration and the leaders of Congress, both Republicans and Democrats have finally reached an agreement yesterday on the largest economic bailout since the Great Depression of the 30s.
The new version of the plan of 700 billion U.S. dollars to curb the financial crisis in Wall Street for months has yet to be ratified by both houses of Congress.
It provides for: a better control by elected its implementation, new mechanisms to ensure the repayment of public money involved, new provisions to contain the number of foreclosed homes for non-payment and a right to review the salaries paid to executives of companies rescued.
The U.S. Treasury Secretary Henry Paulson, president of the House of Representatives, Nancy Pelosi, and the Republican representative to the negotiating table, Senator Judd Gregg, announced the good news a few minutes after midnight yesterday, at the end of a marathon two-day talks.
"We have made great progress towards an agreement that will be effective on the market," said the representative of the Bush administration, Henry Paulson.
"Everything was done in order to shelter the real economy and ordinary Americans from the crisis on Wall Street," said the Democrat.
"This is the fundamental point: if we do not do this, the trauma, chaos and disruption of the daily lives of Americans will be huge," said Republican Judd Gregg.
The negotiations had turned to sprint in the final hours for fear of the effect that would cause another failure on investor sentiment.
The deadline we had given was market opening this morning.
Associated late in the negotiations, the two candidates for the U.S. presidential election were rather favorable to the agreement, but did fail to express their displeasure that one is forced to come to this end.
Sen. Barack Obama awarded the addition of certain provisions of the agreement, particularly the proposal to allow homeowners to keep their home and that the salary of directors of companies rescued by the state.
"When we ask taxpayers to take extraordinary measures because of the irresponsibility of some, there is nothing to commend.
But these measures are necessary, "he said on the airwaves of American television.
Asked on another channel to see if he would vote for the proposed plan, his Republican opponent, John McCain, said: "I want to see the details, but I hope so."
"The outline that I read [show] that's something we're all going to digest and with which we can move forward.
The option of doing nothing is simply not acceptable, "he said.
The plan is to purchase $ 700 billion of taxpayer money with bad debts, assets and risks unmarketable U.S. financial institutions.
It comes after 14 months of a crisis triggered by the bursting of a housing bubble that first led to the collapse of the subprime mortgage (subprime) before spreading to other more common forms of credit securities (ABCP) and lead to a liquidity freeze and the rout of banks and financial institutions.
This is a group of elected Republicans that wrecked the first draft agreement last week.
Is believed to be out of this impasse since the Democrats have agreed that some "toxic" assets from troubled companies are only insured by the government, rather than purchased.
To round the corners for everyone in Congress, we also added a provision that if the government were to assume losses for five years with the program, it could establish new taxes to help recover its implementation.
The new plan provides for payment of a first tranche of 250 billion which may be added another $ 100 billion if the President deems necessary.
The payment of other 350 billion expected to be endorsed by another vote of Congress.
In exchange for his help Washington get stakes in rescued companies that earned him the dividends if he can sell and profit when the storm is over.
The federal government will be able to delay the proceedings of foreclosures on housing attached to mortgages affected by the plan, and to set limits on compensation and severance payments to executives of companies affected.
The architects of the plan would like to see put to the vote of the House of Representatives today, and the Senate on Wednesday.
Despite all their efforts, it is not yet certain that their plan will go ahead.
Voices have indeed continued to rise yesterday against this project as a Democrat in the Republican camp.
"Obviously, Washington can not hear you," he said at his Republican voters Scott Garrett, a member of the Finance Committee of the House.
"Yes, we have a serious financial problem.
Yes, there are solutions.
But not one that is to take advantage of the taxpayers. "
Leader of a small group in Congress known as the "caucus skeptical," Democratic Representative Brad Sherman presents things differently, but arrives at the same conclusion.
"Four hundred prominent economics professors, including three Nobel laureates, wrote to tell us: we ask Congress not to rush and to carefully consider the way forward," he said yesterday.
At the same time, in Europe, once again there was evidence of the global nature of the crisis.
After an emergency meeting, the three Benelux countries have announced the partial nationalization of the banking group Fortis for 11.2 billion euros (16.3 billion U.S.).
The intervention of the governments of Belgium, the Netherlands and Luxembourg was necessitated after the French bank BNP Paribas has indicated that it would not acquire its competitor in the wreck since she lost 2 billion euros (U.S. $ 2.9 billion) in the crisis of subprime mortgages in the United States.
Fortis employs 85,000 people and is part of the twenty largest European banks and the ten largest insurers.
"It's not a waste of money, said yesterday the Dutch Finance Minister Wouter Bos.
In exchange, it gets a vote in the bank and influence.
This is just something that investors and households are now enjoying the uncertain times ahead. "
Meanwhile, across the Channel, the British government seemed on track to nationalize another bank battered by the financial crisis.
According to the British press, the government would take account of all its outstanding loans at the bank Bradford and Bingley, more than 41 billion (U.S. $ 75.5 billion) of mortgages.
Spanish bank Santander said yesterday that it was she who would buy the branches and customers of British bank accounts.
Bradford and Bingley is the second largest bank after Northern Rock, the British government should nationalize since the beginning of this financial crisis.
Paul Newman (1925-2008) - Death of a committed icon
Her beauty was the blue eyes long his trump card, some say its weakness.
Had he released the narcissistic mirror, the American actor with a charming smile?
Yes and no.
His modesty, sensitivity and talent flowing from the source will also be removed from the register of the real power in labor superstars.
But what a great runner!
Paul Newman, who died Friday at age 83 of complications from lung cancer at his ranch Connecticut remains one of the last icons of American cinema of the boom years.
Less monumental than Brando, who he looked like and he has long been a kind of rival to the screen, more cautious in his game, certainly more fragile, but also an apostle of freedom and the breakdown of dramatic conventions.
The mixed blood often beautiful children.
He was born in Ohio in 1925, a German Jewish father and a Hungarian mother of origin.
These European roots born a glorious face of the American dream.
No egos, the ultimate mark of quality.
For in him threw an entire country loving self-made man, the fighter of the Pacific War, wounded in battle, which in the early 50s studied drama at Yale and attended the Actors Studio in New York, before to triumph in theater, television, cinema soon.
The same man who campaigned for civil rights was also the car driver who came second at the 24 Hours of Le Mans in 1979, coupled with a sex symbol, though a member of a couple pattern formed since 1958 to actress Joanne Woodward.
Go with him as the shadow of this secret star, discreet, committed allergic to bursts of show business, which we will not have quite the enigma drilled areas.
An honest man, in the noblest sense.
The disappearance of Paul Newman has given dizziness moviegoers this weekend, while his main roles collide on a black screen memories.
More than half a century of American art seventh constantly changing scrolls through it.
Return jostle remember the cowboy charm of Butch Cassidy and the Sundance Kid (1969), the young man rejecting his sultry wife (Elizabeth Taylor) in Cat on a Hot Tin Roof by Tennessee Williams adapted in 1958.
Closer to home (1990), talks about his sensitive Mr. Bridge, troubled in his old age by a marriage that did not fulfill its promises.
Many others Paul Newman passed into history.
This boxer Rocky Graziano, delinquent, tormented, violent, unforgettable in Somebody Up There Likes Me (marked by hatred), Robert Wise, a role for James Dean, taken after his death, which really threw Newman in 1956.
This friendly thug in the brilliant The Sting (The Sting), Oscar for Best Picture in 1973.
Player bitter and vengeful pool in the beautiful The Hustler Robert Rossen (1961), he will take on the character's return in The Color of Money by Martin Scorsese, which earned him his only Oscar in 1987 on new appointments.
This face through the ages, it was him.
Him again.
Ages jostle through his career.
Young people know him mainly through the cult classic Slap Shot George Roy Hill (1977) by Reggie Dunlop, coach a hockey team unorthodox ice.
His fans were found in 1994 in The Hudsucker Proxy by the Coen brothers.
With a last role of patron of the Irish mob in Road to Perdition Sam Mendes in 2003, had come full circle.
In contrast to several legends of cinema gave way early craft, Newman will long remained in the saddle, while denouncing Hollywood, its gold, its splendor and its concessions.
French filmmaker Bertrand Tavernier considered, not without humor, "as a living challenge to the" underplaying "judging its services supported too.
The profession has not always been kind to the beautiful Paul Newman in that role fell all cooked in the long beak.
However, he played less often than the first street youth: neurotic, alcoholic, or desperate bastards whose perfect features reflétèrent drifts and revolts.
As director, Newman revealed little known facets of his true modest sensitivity.
Its Rachel, Rachel, in 1968 (after the novel by Canadian Margaret Laurence), with his wife Joanne Woodward in the lead role, drew a fine portrait of female melancholy.
He who lost his son Scott overdose dedicated his movie Harry and Son in 1984, the work of shame and sorrow.
Among the tributes that swept rain yesterday Newman, his great friend and former comrade Robert Redford (they had played together in The Sting and Butch Cassidy and the Sundance Kid) stated, very sad: "His presence has made my life and what better country. "
Generosity, love of life are vibrant features of the actor disappeared.
Beyond his legendary career, also removes a great activist for civil rights, ecology, independent cinema, a protest of Hollywood's excesses.
We have seen a lot on his hoe enthroned pots dressing, sauces, biscuits and other food, judging process in rather bad taste, although gag out.
The profits from these sales were nevertheless made to the Foundation for Special Education.
Newman, rather than sit on his myth, becomes engaged to the end.
He left his five daughters a letter containing these words: "Always and to the end, your father was incredibly grateful for his good fortune.
It was a privilege to be there. "
And a privilege for us to have followed the path of so lucid and generous American artist.
Model citizen, and in fact included.
That could well make Zuschlag & Company in their factory invoices?
Soon, October 8, will begin hearings relating to the criminal proceedings, against János Zuschlag and his accomplices.
The politician and his accomplices are accused of fraud in the form of criminal organization, permanent and regular basis, having led major damage. Other charges were brought against them, such as forgery and use of forgery.
According to the prosecution, the money from grants was spent for personal use, while benefits were justified by false invoices.
The money from the state and municipalities, about 65 million HUF in total, was a share in cash movement Fiatal Baloldal and secondly, in the pocket of some people.
Their method, published also by the authorities of the survey was to collect the money from grants obtained by issuing bills of costs, behind which no actual service was provided and thus the associations never met their commitments .
According to the indictment, much of the invoices were false.
For the latter, they were acquiring books invoices Józsefváros market, while they made the stamps to Halas.
For the names of companies that would appear on invoices, it was decided, among others, during tours in Northern Province of Lake Balaton, conducted by István Lados on request János Zuschlag.
According to the testimony of the latter, it must identify pensions and restaurants.
For personal consumption, he asked for a bill, modeled on that they realized the other bills they would introduce, among others, the Ministry of Youth and Sports, the Ministry of Social Affairs and Labour and Municipality of the Capital to access grants.
The majority of bills was created by István Lados and his accomplice András O ˝ ri, which according to our information, dealt primarily to write the files required to obtain grants.
In a "circuit identification", a choice was Lados bistro.
According to the two bills issued by Zuschlag in 2003, this place has ensured the restoration of a group of 90 people, members Biztos Egyesület Bridge.
However, in the words of the manager, could not have been so many people occupy this place, at the same time.
Similarly, in the summer of 2002, the invoice on behalf of the foundation Jobb Jovo ˝ ERT which later will be known as a Együtt Harmadik Évezredért, teeming with errors shapes and background.
A pension, located Badacsonytomaj, had really only three rooms, and a maximum of ten people could spend the night. However, the invoice indicated hundred thirty clients.
Billers to the imagination also fell overboard, when the company mentionnèrent Pigal Kft, also belonging to the hospitality industry. In their accounts, nor the name of Jovo Jobb ˝ ERT nor the Hoppa did not appear, according to information provided to the prosecution.
Gyo ˝ zo ˝ Farkas, the manager of the company, said the site hvg.hu when the floor was called and showed him the bills, he knew right away that this was false documents.
"The name of our company and our tax number were placed in a wrong place on the stamp."
He added: "In addition to the form, the fact that according to the bill, one hundred people have stayed there, did not fit either, since this institution has only eleven rooms, which do not have much space.
In addition, the bill also mentions food and our restaurant is closed for a long time. "
Issuers zealous invoices were not informed about the travel agencies in Budapest as part of their choice, but that organizing trips abroad. Thus, naively, they said stays in Hungary bills to pay in cash, which also goes against the accounting practices of the agency.
In addition, as it appeared during the investigation, they also added the VAT on these documents, while benefits for travel activities, whose destination is outside the EU, no VAT is charged.
Similarly, the VAT rate of four invoices on behalf of the Hotel Révfülöp about Jobb Jovo ˝ TRV was incorrect, since the benefits of the company do not support a VAT of 25% as stated, but a VAT 15%. In addition, the hotel staff only issue paper bills, while false were handwritten.
The Prosecutor's investigation reveals that "issuers" also erred in stating that the delivery freight transport by road, the company issuing the bills could not exercise, because his profile was as investment advice.
In addition, it is also defective in forms, such as types of improper invoices and forged stamps that invoices issued to the order of a Együtt Harmadik Évezredért Alapítvány, XXI. Századi Kulturális Egyesület and Biztos Bridge proved false.
As in the case of Bt Ravenna company or athlete Kunfeherto course, deny that any two to be authors of invoices issued in their name.
Counterfeiters do not pay attention to the fact that the company HIB Kft., Established in Nyíregyháza, was in liquidation at the time (2001) the group Fiatal Városért Egyesület was supposed to have a meal at home. According to our information, it is for this reason that the liquidator of the company denied having issued the invoice.
Invoices deliberately
Another category of billers that is composed of those who were well aware that they were required to issue false invoices.
The Esély Budapestért Alapítvány Foundation at the request of the group Fiatal Baloldal - Ifjú Szocialisták, issued an invoice to the order of a Együtt Harmadik Évezredért foundation for a sum of four million HUF.
According to the indictment, the manager of the company Collab Kft. was brought to issue false invoices by one of the accused, Ludovic Györfi.
Similarly, cooperated with Zuschlags the company Biogate Kft., Which is currently in liquidation and in 2003, issued bills payable to the foundation Jobb Jovo ˝ TRV Alapítvány, the association and the Atlasz Egyesület Association Vörösfenyo ˝ Egyesület for a total of about five million HUF, but behind which no benefit was actually provided.
No financial movement has taken place, either, because the invoices were issued later canceled, but the agencies have carefully avoided mentioning in their accounts.
The next category of issuers bills is that companies directly linked to the accused.
Thus, the Administrative Officer of the Director General of Delta Trió Kft., Dealing with trade of fuel and cars, whose headquarters was in Budapest, but where there was found, was Iván Kubatov.
In October, November and December 2005, the company has issued several invoices for the sale of computer equipment for an amount of approximately 18 million HUF.
According to the survey, these devices were purchased by the company Cash Investment Kft. of Halas, who was in liquidation since 14 September 2005.
The director of this company was a man of Romanian origin, who Iván Kubatov have also sent documents related to the company between 2002 and 2005.
From what we know, Kubatov admitted during the investigation that issued invoices to order companies Atlasz, Hoppa and Együtt has Harmadik Évezredért Alapítvány, and has won their against-value.
It is precisely at the request of the Romanian Iván Kubatov masons created companies Fa-Bani Jos Faipari Kft. Investment and Jos-Bt
In reality, none of these companies are operated, the accused explained by the fact that they were not getting work.
He used even when these companies as at the request of Mr. Zsolt Szente, editor and co-defendant acts of founding companies, he established invoices to their names, in the order of associations related to Zuschlag, as Atlasz and Y Generació associations.
Kubatov gave organizations, 15 bills in total, issued by companies Cash Investment, Delta Trió Fa-Bani Jos Jos Investment and Linaxtrade, worth 14.2 million HUF.
The prosecution believed that 10% of the amount shown on the invoice and VAT were in the pocket of Kubatov.
The man even used the company Szi Beri-Bt to establish fictitious invoices that were used in the grant application Biztos Bridge.
In January 2006, the Y-Generació Association and Modern Magyarországért Szövetség has introduced a grant application to the utility of the Socialist Party, Táncsics Mihály Alapítvány (TMA) organization.
They got the grant for $ 500,000 HUF twice, but these amounts were not used for the purposes specified in the application.
To avoid this be known, five fictitious invoices received from the company Team Works Kft. were presented in TMA.
Moreover, these are bills that were found during the search of the Árpád Kemecsei office, the Ministry of Education.
At the hearing, some of the accused chronicling the manufacturing method of the invoices, as it had done before the floor above.
This could be really interesting is that the main accused, János Zuschlag himself, decided to lift the veil on the whole story.
So far, his confessions are not very detailed, and although he repeatedly promised to tell every detail, it has not yet done.
The question is whether it is in his interest, or so, possibly, the Socialists have reached an agreement whereby in exchange for repayment of a majority of fifty million HUF, Zusi would only hat.
Today, it is probably upset because the demand for his house arrest, based on a reduction of his prison conditions, continuously fall in deaf ears.
While those who have caused much greater damage, and the authors are not repairable economic crimes roam freely or at least expect their own homes by the end of the procedure. He does not have that option.
The psychology of bidding: why do we spend more money?
At auctions, buyers tend to spend more, and overestimate the goods.
Researchers in neurology and economics from the University of New York have managed to update the neurological and economic bases of the known and seemingly irrational behavior.
According to their study published in the journal Science, humans do not want to be distanced in this type of competition, such as an auction on eBay, and that's why they even prefer to pay too high a price.
These studies have attempted to develop a neurological pattern of this kind of "game" using experimental auctions.
One group of volunteers playing the lottery, while the other group took part in an auction fun auction, while in the process of using a functional magnetic resonance imaging (fMRI), researchers analyzed the brain areas active experimental subjects.
In both games, the participants could earn money, but during the auction which is an essential element of one-upmanship third, all located in the brainstem, called the striatum, is put in motion intensive manner when the portion of the loss.
This part of the brain, along with several other functions, plays a role in the mechanism of "self-stimulation" of the nervous system.
That is why, according to the researchers, the rise in prices is due to the leakage at the violent reaction of the striatum.
In support of their theories, economists in this group of researchers have continued analysis of financial supervision.
When these three groups surenchérissaient facing a partner in various circumstances.
They simply informed the control group of the actual value of the product in question, and they have done and their implementation.
In another group, they promised that if, in addition, they came to win the game, then they would receive an additional $ 15 in rewards.
While the third group received her the $ 15 before the auction, but the group also lost money in case they lost the auction.
The difference between these two groups is that the focus was at one with the victory, while in the other, about the failure.
Thus proving the hypothesis of neurologists, the team players "against failure" were willing to put higher than those made by the control group and the group "for the win."
"These results can not be demonstrated by any existing economic theory.
In fact, each of them explaining the phenomena observed during auctions by the thrill of winning and the parade to the risk.
Only methods of neuroimaging helped remove the contradiction between the two leading theories, now a third explanation. "- Found Andrew Schotter, Professor of the Faculty of Economics at New York University.
Hepatitis: When should we see a doctor?
Worldwide, about half a billion people suffer from chronic hepatitis B or C, while in Hungary, chronic liver disease is mentioned among the leading causes of death.
Patients carrying the virus estimated one hundred thousand hepatitis in Hungary, but only seven miles undergoing treatment. This is due to the fact that patients often do not know they are infected.
Hepatitis is the name given to infections of the liver caused by different viruses generic name.
There are many similarities between their symptoms. Inflammation of the liver and jaundice are typical, but the pathogens and diseases caused differ from each other.
The hepatitis, according pathogenic genes are spread mainly in two forms: hepatitis A and E through the digestive tract (eg contaminated food or water), hepatitis B, C, D, and other viruses by blood and body fluids (semen, vaginal secretions, saliva).
For travelers, it is in any way recommended to be vaccinated against influenza A and B. There is no vaccine against C.
Symptoms of hepatitis A appear two to three weeks after eating contaminated food in general, accompanied by malaise, weakness, stomach pain and nausea.
Then develops on the skin and the whites of the eyes are visibly jaundiced, the stools become lighter and urine takes on a darker color. Recovery may take two to three weeks.
Around the world, every year, one million people die from the most severe form of this disease, such as cancer or cirrhosis of the liver caused by hepatitis B.
The main reason is that according to estimates, only one patient out of ten receiving medical treatment.
Hepatitis C can also have serious consequences if it is not treated, it can lead to cirrhosis or liver cancer.
Most patients do not know have the virus, because the pathogenic gene destroyed sneaky liver cells. In many cases, symptoms do not appear until 20 to 30 years.
Therefore, early prevention is very important, as well as regular screening tests.
Contamination is much higher than average among a population of three groups: those who received a blood transfusion before 1991, drug users and tattooed.
Currently, it amounted to 200 million patients with chronic hepatitis type C in the world.
Since the disease can be detected by a routine laboratory, it is advisable to consult your doctor as soon as observing symptoms of unknown origin.
The disease can be cured if detected in time. The virus can be eradicated from the body, in this way the risk of infection disappears and the development of cancer is prevented.
September 30 is World Hepatitis Day, held for the first time in 2004 by organizations representing patients around the world.
Its aim is to draw attention to the chronic liver cirrhosis, caused by the virus, the cause of development and the importance of early diagnosis of the disease.
Whoever believes in God feels it less pain?
According to the results of recent research, religious belief function as a kind of analgesic, which has already helped to make more bearable the death of Catholic martyrs.
British newspaper The Telegraph published an article in which researchers at Oxford University have made an interesting experience analyzing what level of belief in God could influence the pain tolerance of the human being.
As part of this experience for the least weird, 12 Catholics and atheists as believers were subjected to electric shocks, while each watched a painting of the Virgin Mary.
According to the results, the Catholic believers were able to exclude a large part of the suffering.
Using a technique of palpation of the human brain, it was also discovered that the Catholics were able to activate part of their responsibility for the regulation of brain pain.
This analysis is the first in a series of experiments in which academics, scientists, philosophers and theologians participate from different parts of the university.
More specifically, the experiment is conducted as follows: an instrument emitting sparks and disseminating ECT is set on the left hand of the experimental subject.
The researchers asked the participants to the experience of watching a sustained two paintings, one being the Virgin Mary painted by Sassoferrato 17th century and the other, the Painted Lady with an Ermine by Leonardo da Vinci in the 15th century .
The researchers behind this experience hoping that the sight of the Virgin Mary evokes a sort of state of faith among believers, while the choice of painting Da Vinci, not very different from the first, was on his soothing effect.
Experimental subjects spent half an hour in an MRI scanner, and during that time, received 20 electroshock in four parts in succession, while watching or painting religious theme, or the more general theme.
Catholics have said that the sight of the Virgin Mary, they felt like "safe," as someone who is "taking care" and they "calmed down, and invaded the peace."
At the sight paint religious themes, they reported 12% less pain than when they looked at the work of Leonardo.
The psychologist Miguel Farias, who himself took part in the experiment, think we can achieve the same effect with any other strong image among atheists, if you can find the appropriate picture.
"We should find a picture against which they react very positively, such as a mother or a father," said the psychologist.
Tom Wright, Anglican bishop, welcomed the results of this research.
"The practice of faith should change and in many cases actually change our personality," said Wright.
After these excellent results, there remains the question of what would be the effect on the regulation of pain issues if we show the believers a painted by Leonardo or by a painter of the same caliber Madonna?
Does the sight of a Virgin Mary better cause better results?
You are what you divulged about you
On the occasion of its tenth anniversary, Google says it can be found at the bottom of the pockets of the people as well as the sky above their heads. He knows where they spent their holidays, which specialists they visit and what are their interests.
This is however not enough, according to Eric Schmidt, who is one of the influential people in the society.
While that for the skeptics drawing a parallel with the vision of horror Orwell, they just do not see most of the web 2.0.
Eric Schmidt said, long ago, the Financial Times that the main goal of Google is to gather more information about its users. This is necessary so that the founders of Google can fulfill their original purpose that sounded as follows: "a system in us gather all the world's information".
According to Google executive asked, after ten years of work worldwide upheaval, they are still at the beginning of their goals to process all the information.
To the question: what will be there in five years? Schmidt said he would like Google to answer questions like "What can I do tomorrow?" or "What is the job that best suits me?". However, the software can not answer that kind of question, simple at first glance, that when they know enough about the users.
It is not perfectly clear to all users that the words used in research on the internet, the IP address of the computer that initiates the search pages and then consulted by interested persons are specifically listed address.
Through the Personalized Search program launched two years ago, users can, for example, store their own historical research and can see what they looked, what they clicked. With this, long-term recommendations, program based on the same logic, will be able to give more personalized answers, and we will present products and services based on our previous statements and our preferences recorded.
-What happens if someone uses my data against me, if he looks at what is my job? ask users who are worried seeing the monopoly of information from Google.
In most cases, the potential power represented by the company that can generate fear, and it is not remorse, fear of punishment, the desire for freedom and eventually revolt against the power can arouse users against a feedback.
But it is a confirmed fact that search terms are not only saved, but in justified cases, they are transferred to a third party, and in such legal cases, nothing protects the personal rights of Internet users.
The most shining example of recent times is probably coordinated action against pedophiles Brazil, during which Google sent the Brazilian government the information he had gathered on the public page called Orkut, allowing identification.
Customers concerned about the human rights could breathe a sigh of relief in May when Google arm with the body of electronic legal protection EFF has proved his rights in court against the FBI. According to the judgment, in the future, Google will still not be bound by any of the points of the constitution to disclose information about the secret request of the FBI, of any nature whatsoever.
(At the same time, the federal government has successfully obtained some 50,000 web addresses and 1,000 search terms that he won from the law enforcement on child protection, passed several years ago. But in the end account, he failed to obtain lists of searches of private users, or the entire list of websites and keywords of the last two months.)
The judgment of Google is quite contradictory: it is criticized by those who fear the transmission of personal data, because they think their private sphere and private sphere suffer when they start using Google services. Therefore, they attack them in the spirit of revolt against the manifest that proud of their conservative image multinational corporations.
Meanwhile, American culture geek and "savages" bringing together passionate activists and enthusiastic computer users that appear in many countries see Google's next generation of large enterprises, the "connected corporation", by opposition to his rival, Microsoft, labeled as invaders of the world because of Windows, and even though both are fighting for the same goal.
This can be explained by the fact that Google, unlike Microsoft, does not require its users to identification code, do not ask for money for its applications. The documentary code and package programs, continuously updated, has a younger and much more accessible cool effect, against the practice of official software giant.
The reason may be that geeks see exactly the problem between human rights and internet connection, and that Web 2.0, the key word as proclaimed in recent years, takes just behind him.
Indeed, Web 2.0 is not about anything other than collaboration, the fact that we intentionally leave traces behind us, and we use the communication channels available to us, and while the size of these changes one by one, most remains the same: we are exposed.
A young, in general, can take on a more public profile pages, Facebook, Xanga, and it can even connect them to other services, such as in Twinter, or last.fm, listing his musical habits . Then it can connect them to a tracking system, such as FriendFeed or Blip.fm. These young people can also be blogs, which will automatically appear in their latest photo galleries they store on Flickr or Picasa.
While we may be aware of many examples, such as the girlfriend who understands easily view pictures in the morning, taken by the circle of mutual friends with her unfaithful friend who spent the night, or that of the company that fired an employee, just for the honest opinions that he wrote on his blog about the top management, you can be sure of one thing: the end of privacy is totally reconsider nowadays.
One who lives a life online, consists of what he shows himself, and thus we can define the principle hiding behind the behavior of today's youth.
He wants to hide something, or at least wants to try to circumvent the monopoly of Google can do (starting, for example, with Scroogle, using the Google search system, but at the same time, not intentionally leaving no trace ).
The number of people who deliberately do not register on public pages so that it is not possible to find, is not insignificant. Google's services online, through word processing to image processing, reading information can be replaced by alternative versions, which are not attached to huge server farms and that together not our best side, which existed until today.
The public expects, without really hide when Google will reveal its true nature.
The company, with its current value of $ 156 billion, is worth more than IBM ($ 140 billion), Intel ($ 124 billion) and Coca-Cola ($ 110 billion). Advertising areas AdWords / AdSense threaten sales of advertising agencies, while benefits introduced at a rate of more important cause of severe migraine headaches not only Microsoft, but many other creators of computer programs.
However, critical observers are, beside all this, contradictions with disturbing effects: for example, the top management of the company has refused, in its entirety, the protests of employees, after it has doubled the price of mother company and after the Company has deemed too costly to restore multiple daily taken anytime. All this pales next to the fact that already in 2006, Google has acquiesced to the Chinese government and under the terms of their agreement, the company finds all results that hurt the taste and interests of the Chinese regime.
According to the internal rules of the company, the new services are not advertised when they can be used. What's on, is that in the coming months and years, they will move the world with new issues. While some believe that the project scanning and archiving of books and magazines Google takes so large that the company will soon be faced with the Supreme Court of the United States dimensions, others tremble before its system Health, because in it, we can build a complete from results of previous analyzes, our doctors and medical problems profit.
The fact that Google up a DNA database can give a good raw material for the next generation of writers of science fiction. The famous novel Cory Doctorow wrote with semitones Orwellian describes the future in which a man could be so frightening nothing approached only through the Google data.
Two miners helped to remove the traces of the double homicide of Ózd
"The police summoned two minors for questioning in the case of the double homicide of Ózd. According to well-founded suspicions, they helped to remove traces of the crime." - Said the spokesman of the police Borsod.
Young acknowledged the charges against them. For now, they are accused of complicity.
The two miners, who, according to information from MTI (Hungarian Telegraphic Agency) are girls, defend free.
The complicity of murder may lead to detention up to 5 years.
The suspect in the double homicide of Ózd, a young man of 23 years old corner, was remanded in custody on Sunday.
The charges against him are multiple homicide committed with premeditation and interest.
During the investigation, it was found that the young man of 23 years had a large sum of money to a man of 53 years.
The suspect did not want to pay his debt and that is why it caught his creditor, last Wednesday, in a site Ózd where he was killed, and the granddaughter of the man, aged 9 .
According to information of MTI, the young man planned the crime. The weapon with which he would commit its hidden on the crime scene crimes is proof.
The police examined the weapon and the circumstances of its use with the help of specialists.
The Warsaw Stock Exchange made a proposal for the acquisition of the Prague Stock Exchange
The Warsaw Stock Exchange has proposed two hundred million euros, about five billion crowns for the acquisition of 100% of the share package of the Prague Stock Exchange.
Ludwik Sobolewski, President of the Warsaw Stock Exchange, confirmed the proposal that the Poles have made although, previously, the Czech have excluded the Warsaw Stock Exchange in the circle of potential new owners of the Prague Stock Exchange.
The reason for this exclusion is that the Warsaw Stock Exchange is in the hands of the state.
99% of the shares are in the hands of the Polish State wishing to separate over 60% of its shares in a few months of operation.
According to the Czech business daily E15, the Polish proposal is the highest that has been made so far for the redemption of the Prague Stock Exchange offer.
According to the Czech press, the Vienna Stock Exchange, the transatlantic exchange Nasdaq, the New York Stock Exchange, the London Stock Exchange and Deutsche Börse made an offer so far.
Petr Koblic, director of the Prague Stock Exchange, said last week that among the stakeholders, the Warsaw Stock Exchange is the new owner worst, and did not rule out that this could lead to the disappearance of Prague Stock Exchange in the future.
The value of the Prague Stock Exchange is estimated between 5 and 10 billion Czech crowns by market specialists.
Based on an agreement between the shareholders, some 90% of the papers would be sold.
The largest owner of the Prague Stock Exchange is the investment bank Patria Finance, with about 25 percent of investments, followed by 14.7 percent of the bank Ceska Sporitelna and Tiger Holding Four S. a.r.l. with 13.5 percent.
The financial crisis from the perspective of the European press
In their comments Tuesday devoted to the international financial crisis worsening by the day, the leaders of the European press newspapers already evoke a 'second 11. "
"The global financial disaster, should the U.S. President" - accuses the Rome daily La Repubblica. "The president has not even been able to block with his own party behind a bill, improvised hastily, to rescue a desperate situation ..."
Instead of a new Pearl Harbor, as evoked the billionaire Warren Buffett, it is more appropriate to speak of a second 11.
Part of the Madrid press also sees the scapegoat in Washington.
According to the vision of the daily El Mundo, it is the failure of political leadership there that brought the world economy to the brink of collapse.
The danger of the collapse of the U.S. financial system is growing every day, and then the whole world will pay a heavy price.
Bush's plan was far from perfect, however, after the vote of Congress, a real danger threat that Washington does not offer policy tool to address the crisis.
The global economy hangs in the air, just as in the history of capitalism, one of the biggest changes took place.
One can not ignore the threat any longer - emphasizes the Tages-Anzeiger Geneva.
Some states may also extend a lifeline to their staggering financial institutions, and through their taxpayers' money, they can save it from bankruptcy.
Of course, if more banks collapse like dominoes, then neither the financial resources nor new improvisations will be sufficient.
In the long term, we need the states of the European Union do little if their national egoism, and they centralize control over the financial markets divided.
Just Monday, the weakened financial institutions have received more than 100 billion euros - recalled the Vienna daily Der Standard, adding that fears that European taxpayers will also have to put their hands in the pocket, very deep, similarly to the U.S. in order to overcome the crisis, becoming more realistic.
So far, the EU has not really handled the crisis, such as a tsunami crosses from one side to the old continent.
The "rescuers" should not brandish immediately hundred billion euros, by cons it would be wise they noted in which case it would be rational to touch the taxpayers' money, with the goal of preventing larger damage.
The intelligent car mimics the flight of the bumblebee
Which method would be better able to develop technologies to avoid an obstacle, if not the imitation of a sensor already existing obstacles in nature?
Such as that of bees.
In the amazing project presented at CEATEC, taking place in Japan, buzzing bees gave the strategic idea of ​​starting engineers at Nissan for inspiration on how they should design the next generation of obstacle avoidance sensors.
In collaboration with the University of Tokyo, Nissan has built a mini robot car, a system self-control robotic bio-inspired, BR23C type it with the qualities of bees, the ultimate goal is to encourage the development of a system capable of avoiding all obstacles.
During his flight, each bee is its own space, oval, which actually looks a lot like our secure shell protection - explained at the exhibition Kazuhhiro Doi, director of research and development department and relationships public technology brand.
The compound eye of the bee plays a crucial role, since it is able to see in all directions at an angle of 300 degrees.
To mimic the functions of the compound eye, engineers have addressed the idea of ​​the laser rangefinder.
This identifies obstacles at an angle of 180 degrees and a distance of 2 meters in front of the BR23C, it evaluates the distance and sends a signal to the microprocessor board, which transforms it into evasive action immediately.
The perception of the barrier occurs in a fraction of a second. Then the auto mini robot, mimicking the movements of the bee, immediately changes the direction of the wheels turning an angle sufficient to avoid the collision.
Unlike any system currently available, this evasive action takes place entirely in an instinctive way.
"If it were not so, the mini robot car could not react quickly enough to avoid the obstacle" - explains Toshiyuki Andoh, director of the Laboratory and Mobility Project robot car.
It must react instinctively and instantly, as this technology is the most vulnerable and the innermost layer of the protective sheath, a layer where the moment the collision is deemed unavoidable.
This whole process should reflect that the bee does to avoid other bees.
The process must be carried out in a glance.
In contrast to bees, the difference can not go up, down or diagonally, it may be only two dimensions, and only in the direction in which the wheels can turn.
In this way, instead of the endless combinations that have the bees to avoid other bees, in our case, we could use the rotary motion, acceleration and slowing as laborers at the disposal of the mini auto robot
The BR23C uses Lithium polymer batteries are lighter and whose energy is concentrated more, making them last longer than the lithium-ion version of life.
According to Andoh is instinctive intelligent reaction is paramount, not data processing, let alone the ability to store.
This mechanism should treat some incoming signals per second, and react to them.
It is not necessary to store and react with the intuitive logic based on data from previous maneuvers. In this way, it uses only a few dozen kilobytes of memory continuously.
You do not need a memory capacity of gigabytes or even megabytes.
This is the first step towards the design of a technology for instant avoidance. Estimates of Nissan, the system will enter the produced cars in the next ten years.
Another application could be its incorporation into the system of GPS satellite navigation so that it can guide the driver to their destination avoiding obstacles in its path.
They even gave a name to the baby overpriced
Written the economic rescue plan of 700 billion dollars to redeem the bad loans of the banks, and use several times version is ready.
In the first round, half of this sum will be spent.
Reuters announced that in new debates extending until midnight Saturday local time on the east coast, congressional leaders have agreed on the existing controversy for days and days about the bailout a total of $ 700 billion.
"We have made a major step forward" - said Nancy Pelosi, the Democratic speaker of the U.S. House of Representatives, after which it remains only to agreements on paper.
The compromise, born from the plan is supported by both presidential candidates, Barack Obama and John McCain.
The U.S. Treasury Secretary Henry Paulson said in commenting on the results of the compromise that the program will work and be effective, however, other measures need to be implemented. According to Pelosi, there is no question here of the Wall Street bailout, but to make the wheels of the economy turning in the other direction.
The written version of the plan was made public before the Asian markets opened Sunday night at 20h local time in Washington (that is to say Monday at 2am, according to the local time in Central Europe) but did not cause dramatic rise in scholarships.
On Monday, the House of Representatives will be the first to pass the bill by the name of emergency law of 2008 economic stabilization. Then, his fate will be in the hands of the Senate.
Saturday evening, President George W. Bush spoke to Pelosi and the White House also welcomed the news of the agreement.
"We are pleased with the night advanced, and we highly appreciate the efforts of both parties to stabilize our financial markets and to protect our economy" - said Tony Fratto, a spokesman for the White House.
In addition, the program diverges from the original proposal made by the Bush administration, which she stated that the $ 700 billion to be spent at once, for the purchase of securities on impaired loans.
Now, no more than half of the $ 700 billion can be spent. The first 250 billion will be issued immediately after the adoption of the law by Congress, probably Monday. This amount will first Treasury Secretary to buy bad loans from banks, while the use of an additional 100 billion dollars will be at the discretion of the President.
The program will be overseen by an independent body, in which the president of the Federal Reserve will also take part.
Spending the second half of the 700 billion depends on a new decree of Congress.
Under the law, the secretary of the Treasury may establish a combined strategy: it may, at the same time, buy bad loans, securities on mortgages and bad mortgages and other types of claims " toxic ".
The competent persons of the Ministry stated that the acquisition can take place through an auction, but also directly.
The rule provides an opportunity for the companies involved, to participate in an insurance program, where of Treasury guarantees tools causing concern for companies that have paid a premium equal to the foreseeable damage.
Henry Paulson said that the law provides the necessary tools to provide $ 700 billion for the urgent needs of the financial system, whether it is large redemption of doubtful receivables, their insurance, or to avoid the risk see the system causing the collapse of any major financial institution.
"We will take the necessary steps to be ready for the application of the law once it is signed" - he added.
However, bank managers being in poor posture and waiting for help from the state can expect that their severance, simply called golden parachute overseas, will be capped by the government.
The salary cap is mentioned only in specific cases. In addition, the limitations depend on how the Secretariat of the Treasury provides assistance to the company.
The principle means that if the cap of the Treasury buys through an auction, they will levy a tax on golden parachute surplus, unless the bank president discredited partner retired.
Immediately after the acquisition of bad loans, the government will intervene aggressively to ensure that the amount paid to executives is not exaggerated.
So that the image is complete, you must still add that existing golden parachutes are not changed. The cap applies only to new contracts this to motivate and plan participation.
This is the first time in the history of the United States as legal caps are in effect on the salaries of CEOs - commented the Chairman of the Committee in charge of financial services of the House of Representatives, Democrat Barney Frank .
In addition, the state provides a right to acquire shares in the banks participating in the plan. In this way, the risk of taxpayers declines, they may even be a winner in the case when the economy and with it the rescued banks fall back on their feet.
The bill states that within five years, the President shall submit to Congress a proposal to approve the way the losses will be returned to taxpayers from the financial sector.
On both sides, there were obviously those who have expressed their doubts over the plan.
This is not what the American people have mandated us, this does not protect taxpayer dollars - said California Republican Congressman Darrell Issa.
His Democratic colleague from Ohio, Mary Kaptur think they are the same crowd that taking measurements, as those responsible for the collapse of Wall Street.
Industrial prices have continued to increase
In August 2008, prices of industrial domestic sales rose 0.1 percent from the previous month, and 12.9 per cent in August 2007 - communicates the Central Statistical Office of Hungary.
Prices of industrial export sales rose 1.1 percent compared to July 2008, while compared with a year earlier, they fell 3.9 percent.
As resulting from fluctuations in domestic prices and export prices of industrial output rose 0.7 percent compared to the previous month and 3.2 percent compared to the previous year .
Prices of industrial domestic sales rose only to a lesser extent from 0.1 percent the previous month.
The domestic selling prices of the sectors of processing industry have been a small increase of about 0.1 percent compared to July.
In August 2008, the most significant increase in prices was observed in the sector of manufacturing leather products and footwear (2.8 percent), with first, making bags and belts with higher monthly 4.6 percent, then the production of shoes with 2.5 percent monthly increase.
The level of higher prices for plastics and chemical raw materials has resulted in a significant monthly rise in prices in the sector of manufacturing and chemical materials (1.6 percent).
Deflation has resulted in the sectors of oil processing (1.4 percent), manufacture of machinery and electrical equipment (0.9 percent), and a minimal increase in the area of wood processing (0.1 percent).
Prices for paper production activities editing and printing have not changed.
Other sectors of the processing industry grew, between 0.2 percent and 0.9 percent.
In the areas of supply of electricity, gas, steam and water, representing an important weight in the national industrial operations, prices were up 0.3 percent in August, mainly due the effect of the increase in gas prices introduced by the authorities since July 1.
In a comparison of twelve months, taking into account the domestic sales of processing industries, it is the price of processing industry of oil that have experienced the most significant increase (32.4 percent).
In the manufacturing of metal products, there has been a price increase of 13.2 percent, while in the important area of ​​food production, beverages and tobacco prices rose by 11 percent .
Price declines have occurred in the areas of textile production and textile products (2.5 percent) and in the manufacturing of machinery and electrical equipment (0.3 percent).
In other sectors of the processing industry, price increases varied between 0.6 percent and 9.1 percent.
Throughout the processing industry, prices rose 10.2 percent in the past year.
Prices sectors of electricity, gas, steam and water supply exceeded 18.7 percent higher than the previous year.
Among the groups of domestic trade and in the allocation of sectors, in August, are the initiators of profit on investment sectors that showed the most significant increase in monthly prices (0.7 percent).
In the areas of production of consumer goods prices rose 0.3 percent, while those of producers of energy and materials for further processing sectors have not experienced a change from the previous month .
In August 2008, compared to the same month of the previous year, there has been a greater increase in the areas of energy production and materials for further processing (16.8 percent).
In the areas of production of consumer goods was measured inflation of 6.8 percent, while for the initiators of profit sectors, a decrease of 1.4 percent.
The price of export sales of industrial sector, HUF, rose 1.1 percent in August from the previous month, while they decreased by 3.9 percent over 12 months.
In one month, our national payment has weakened 1.7 percent against the euro and 7.1 percent against the dollar. Compared to August 2007, he has strengthened 7.5 percent against the euro and 15.9 percent against the dollar.
The next year, Will you still need a visa to go to the United States?
Göncz think there is a good chance that by January 12, the US-Hungarian visa waiver agreement enters into force. This is what the Minister of Foreign Affairs said in Chicago, before the leaders of the local Hungarian community.
According to her, "Now, everything depends only on the time entry systems and electronic control of the Atlantic will be put into operation."
All the time, she drew attention to the fact that in the new system, there will be no entry visa, but tourists must register before departure.
The head of the Hungarian diplomacy will be negotiations starting today in Washington.
He will meet with the Minister of Foreign Affairs, Condoleezza Rice, to whom he will give the decoration of the Commander's Cross with Star of the Order of Merit of the Republic of Hungary, and will meet with advisers in foreign policy candidate for president, Democrat Barack Obama and Republican John McCain.
Obama and McCain both support the bailout of banks
Sunday, Barack Obama like John McCain, the presidential candidates of both major U.S. parties have pledged their support for the government bailout of $ 700 billion. However, there are politicians who demand the resignation of Treasury Secretary.
After marathon negotiations that lasted for days and days, representatives in Congress and the Administration finally announced Sunday at dawn, they reached agreements in principle to the bailout of the banks.
This financing plan aimed thawing of the crisis on Wall Street and the credit markets paralyzed, became the central issue of the presidential campaign.
Obama and McCain are the same, each as more suitable than the other, to lead the country out of the economic crisis.
According to the latest polls, with the focus on economic issues, Obama has managed to get a little ahead again. The advance of McCain, obtained with the appointment of Sarah Palin as his running mate just after the Republican convention, melted.
At a campaign rally in Detroit, Sunday, Obama expressed his hope that Congress quickly passed the law on the bailout of 700 billion.
He stressed that the proposal contains passages of consumer protection that also supports.
"It is now that we must act with responsibility (...) any threat to your job, your savings, entire industries and the stability of the whole economy" - he said to a crowd of 35,000 people.
It has not failed to qualify economic ideas McCain exceeded.
In an interview with ABC interview, McCain said: "We all have a hard time swallowing (...), but doing nothing is not a way forward."
The Republican senator said in the proposal, mentioned the creation of a commission of Treasury Control and cap severance of senior management, and he was personally very attached to these points.
Obama told CBS that McCain had no role on the ground in the negotiations, while he was in daily contact with the Treasury Secretary.
Nancy Pelosi, Speaker of the House of Representatives, said on Sunday that there are serious hopes that the chamber vote the bill on Monday.
Press review of the German language area
The right camp is intact, it is only in the heart of the party that voters have become more aware - this is evoked by Der Spiegel, the low score in the Bavarian CSU countries.
Haider is ready to govern Austria to prevent the coalition of black and red.
Der Spiegel (spiegel.de)
In the internet edition of the German news magazine left, Franz Walter analyzes the causes of the dramatic defeat of the CSU in his article entitled "The Revolution in Bavaria devours his fathers."
According to renowned political scientist, erosion CSU began well before the sad duo Beckstein-Huber took office.
The Christian Socialists turned Bavaria for decades and now it is these modern citizens who turn their backs.
This change in time is also the problem of the Christian Democracy, and therefore also that of Angela Merker.
For CSU, the failure was not entirely a surprise, but Sunday came to an end a process that was probably there that, just ten years the undisputed hegemony of the national party has completed.
There is this decade, in 1998, the CSU picked up with 47.7 percent, and for the first time since the fifties, with a score below the level of 50 percent.
This was repeated three years ago in the Bundestag elections of 2005, that is to say at the time of the so mentioned Stoiber.
The cause may be attributed to the modernization "devouring his parents," implemented in the region consistently by the CSU.
For 40 years sociologists announce it but they are very wrong about the pace. However secularization, the results of the education and the establishment of the German north and east in the region of Bavaria, in full development, could not remain without consequence on the fidelity of voters CSU.
Modernization is associated with increased opportunities, and the consequences of such a policy are also visible.
The right camp is intact, it is only within the party that voters have become more aware, more critical and stubborn.
It is also surprising that in recent weeks, it is precisely the groups classic citizens who are more distant from the CSU, such as independent artisans, tray holders and graduates of higher education.
In these groups, support CSU has dropped below 40 percent.
Die Presse (diepresse.com)
In his article entitled "Who? With whom the party president stand on the reservation face questions from the coalition," the Austrian conservative daily deals with the situation of the internal political confusion that settled after the elections Austrian.
Austrian socialist SPÖ wish to discuss with the conservative ÖVP.
The SPÖ ÖVP prohibited to interfere in its internal affairs.
The populist party BZÖ shows open for negotiations. Green does not want to agree on coalition.
The elections were held now everything revolves around the coalition during the debates on public television, party leaders have barely glimpse leave their cards.
Werner Faymann, the chairman of the Social Democratic Party, confirmed that he wanted to discuss with the ÖVP.
The SPÖ wants to show that cooperation between the two parties is indeed possible - this is what exists in some regions and in the socialist partnership.
The question that we imagine a coalition with Wilhelm Molterer, the current president of the ÖVP, as Vice-Chancellor, is open from Faymann.
As mentioned, the orientation Schüssel-Molterer was, in any case, rejected.
A replica of this combination is out of the question.
Molterer reacted cautiously to the proposals of red.
As already mentioned, collaboration will surely unsuccessful if Faymann trying to interfere in the internal affairs of the ÖVP.
In his party, the choice of the opposition or of entry into the coalition is a matter entirely open momentarily. These points should absolutely be discussed within the ÖVP.
Jörg Haider, the chairman of BZÖ, shows open to all new proposals.
"To prevent the coalition of black and red, we are ready to assume the responsibilities of government" - said Haider.
Járóka said: We must break the vicious circle of poverty and segregation
Today began in Paris, the European Summit for Equal Opportunities, whose host is France, as representative of the current presidency of the European Union.
In his message presentation to the plenary, as one of the main spokesmen of the expert consultation, Livia Járóka Fidesz MEP European People's Party, drew attention to segregation in education, as it is a violation of law that most affects Roma children and therefore one of the main obstacles to their success in life.
On behalf of the French Presidency, this high-level conference was opened with one hand, Xavier Bertrand, French Minister of Labour and Social Affairs, and secondly, by Vladimir Spidla, European Commissioner for Labour, Social Affairs and Equal Opportunities.
Among those invited to take part in the consultation, there is the European social partners, as well as the most prominent representatives of the legal protection and European civil society organizations in the field of equal opportunities.
According to the press office of the member's Fidesz People's Party, Járóka warned that besides the distinctions noted in hiring, Roma disappear from the labor market in the first place, as a result of their low qualification.
"An overwhelming majority of young Roma do not have secondary degrees, and therefore a basic education of poor quality, only a fraction has the opportunity to obtain a graduate degree."
Moreover, Járóka stressed that education as a fundamental right of the human being plays a key role when we must assert the other fundamental rights.
Investment in early education for Roma children means a stronger economy of the member countries of the European Union.
According to the MEP, it is necessary to raise awareness of these reports in the widest possible circle, also between Roma and non-Roma.
Indeed, earlier a Roma child starts school, the more he increases his chances of becoming a productive member of the labor market through taxes paid from income and its consumption, he participated in the state budget .
"By their citizenship of the European Union, Roma must be assured of their right to a quality education, and be protected from low quality education and sectarian." - Said Livia Járóka.
According to the MP, a collaboration between the European Union and goal-oriented action is needed for immediate acceleration of school desegregation. To do this, compliance with existing anti-discrimination directives and preparation is of paramount importance.
"We must break the vicious circle of poverty, segregation and the unemployed. Should be given the opportunities provided by democracy to Roma children, so they can participate as full citizens in the future of Europe "- demanded Járóka.
On behalf of the "European Year of Equal Opportunities" provided for the purpose of the summit for equal opportunities in Europe held annually since the summit in Berlin last year, is to ensure single platform to support measures in favor of equal opportunities and the fight against discrimination, referred to the European level and in member countries.
CSU: thanks for the transition period
It was in October that will be making the decision on the fate of the fallen duo Huber-Beckstein
Despite this pitiful electoral defeat, the heads are not yet fallen, and the debate on personal questions to the summits of the Bavarian CSU was adjourned.
The party president, Erwin Hube and head of regional government, Günther Beckstein, can still maintain their place. The question is until when will the grace?
The fate of the tandem, who suffered a catastrophic loss of voice by 17 percent, will be the agenda of the extraordinary party congress, held the last weekend of October.
The members of the pair were heavily criticized, in any case, felt they did not take their special seat.
With this, they are used to soothe the angry members of the fraction and the base, which one day after the "Bavarian tsunami" demanded personal consequences for the loss of an absolute majority.
There are five this year - that's right, still under the direction of Edmund Stoiber, the peak of his career - the socio-Christian Union won 60.7 percent, while today, one year after the putsch against Stoiber, there are only 43.4 percent of their strength.
For 46 years, the CSU was the "sole ruler" of Bavaria giving 18 percent of German GDP.
But the Conservatives have always strongly in the southern region of key importance for the Hungarian economy. In the future, they will be forced to the coalition.
As one of the first signs of an internal reorganization of the party, the Vice President and Minister of Agriculture Horst Seehofer, presented as a possible successor to Huber, also received a place in this small group of recognition, which initiates discussions groping with liberal FDP, as well as the Free Voters, formed along the right values, about a possible coalition government in Munich.
A foot strange nose of fate was that with the list of electors Free, enters the legislation Gabriele Pauli, including taking action against Stroiber served possibility coup perpetrated by the duo Huber-Beckstein then shrift very ambitious municipal politician.
Now, the leaders of CSU put all their energy to stabilize, one way or another, Beckstein.
In this transition, Stoiber, who until now was pulling the strings behind the scenes, will also receive an active role. The former head of the regional government and former president of the CSU, has designated September 28 as the most bitter days of his political career.
Monday, Huber launched some scathing remarks to the CDU. According to him, they deserved much more support from the sister party.
Other CSU politicians have interpreted the defeat as a warning to the CDU and also for Angela Merkel.
Following the Bundestag elections, which will take place in September 2009, Merkel will again be Chancellor if they call up one way or another, with a joint force, the CSU, having played an important role in national success in 2005.
According to Merkel, hardly concealing his disappointment with the fiasco, the loss of land CSU does not affect negatively the grand coalition in Berlin.
Although this is relative because it will be easier to manage the injured CSU, and the crisis of social democrats forever.
Since 1946, the SPD has reached its worst results with 18.6 per cent in Bavaria.
Lukasenko - rivals: 110-0
No member of the opposition has not acceded to the Belarusian parliament after Sunday's elections.
According to Russian observers, this is explained by a country ruled by Alexander Lukashenko, which ensures stability and prosperity, while according to the Organization for Security and Cooperation in Europe (OSCE), this is explained by illegalities committed during the counting of votes.
The OSCE has sent 450 observers from 43 countries, does not recognize the elections.
Although the legislature composed of 110 people in this country of 10 million people is going great opposition from many decades before yesterday's elections, the opposition joining forces as the United Democratic Forces ( ODSZ) seriously hoped that Lukashenko, renewing his term as president for the fourth time when questionable elections in the footsteps of the constitutional amendment in 2006, "would" this time the presence of some members of the opposition parliament.
In this way, the ODSZ waived his boycott originally planned.
The fact that Belarus economically more and more dependent on Russia, would improve its relations with the EU, where because of the Belarusian political termed undemocratic Lukashenko and several senior politicians do not get visa input, was one of the expectations of the opposition. Belarus had to take a loan because of lower imports of increasingly expensive Russian natural gas, and thus contributed to the passage of Beltransgaz company, owner of the gas lines through the country passed into the hands of the Russians.
The fact that the OSCE during the evaluation of the campaign has focused on the positive changes rather than failures, such as the prohibition to stand for a third candidate for the opposition, referred to prior appeasement.
However, the statement of the OSCE Monday already challenged the campaign during which most of the opposition candidates could not appear in the media, and particularly the fact that the opposition could not be present at the counting votes.
Despite all this, the opposition still feels a palpable improvement in the political system: the political prisoners regained their freedom, and Minsk is ready to small confrontation with Moscow, still refusing to recognize South Ossetia and 'Abazzia separated from Georgia. But Russia with Belarus which form a confederation paper considers two independent territories already been a month.
"We made two steps forward and one step back, but the most important is that the dialogue was initiated between Belarus and the EU" - said Alexander Milinkevich our newspaper.
According to the opposition candidate for the presidential elections of 2006, it is desirable to keep it that way, although "power was scared in this parliament has no weight to bring even a single opponent."
The opposition does not provide for protest actions based on the results. Rather it tries to send the message on the need for economic reforms with voters.
"Of course, we have many concerns that side, we have to print our opposition newspapers in Russia, local authorities put a spoke in the wheel for what is broadcast, but I can also see that they are increasingly supporting the elections, even in the circle of old "people - Milinkevitch said, referring to the fact that under the current regime of Lukashenko which considers social security as its main result, the layer of retirees most supported officially no longer considered really as appropriate.
"Because of the country's debt and rising trade deficit, the collapse of social security, 'referring to the silence of a graveyard' is no longer a matter of time" - believes Milinkevitch.
Unlike the opposition politician, Russian observers described the elections as democratic.
Sergei Lebedev, head of mission of the Commonwealth of Independent States, told the Russian news agency Ria Novosti: "People do not believe in words, but in deeds.". In this way, the absence of the opposition is that the evidence of the maturity of Belarusian voters.
Brunetta: "Starting today, breakfast before work."
Never in the history of the Palazzo Chigi, not only had a revolving door for entry and exit of employees.
But starting today, is in effect the new measure against the crafty, against that point and will then drink the coffee bar during working hours.
The new anti lazy was presented today by the Minister of Public Administration, Renato Brunetta, and the Secretary General of the Presidency, Mauro Masi.
"The revolving door-tells-Brunetta is a tool to work better with more productivity, more attendance and more services," says the minister.
Now begins a new season of accountability and transparency.
"It's reformism" further emphasizes Brunetta.
Installation in all institutions of the Presidency of the Council comes complete with the Chigi Palace.
According to Masi, "the choice of revolving doors is important even from a symbolic point of view.
No resistance from employees was recorded, provides general secretary: "This is a process shared by the employees, and we had the collaboration of all."
In short, over breakfast during working hours, over coffee or croissant.
Promise Brunetta, suggesting smiling, "a good cappuccino at 7am is an excellent and safe resolution."
At a conference at the School of Public Administration
Rome, the Minister communicates that "'in three months, the absence of disease of public employees are reduced by 50% or 60milles more workers in a year."
And he adds that it is essential to make it more efficient Public Administration.
Italian, "which explains the dynamic wage-minister past 8-10 years have doubled compared to the private sector, and right off the inflation rate.
At the same time, thousands of public employees have come together to challenge the norms of the Decree Brunetta making use Codacons.
"" While the Minister of Public Service today spreads the data on reduced absenteeism in the workplace due to illness-written consumer association, the people of the "lazy assets" continues increase.
Indeed, in Italy, thousands of employees of the correct and productive Public Administration, met to declare war on the illegitimate standards contained in the decree.
In particular, Tar, is challenging the exclusion of additional benefits in case of disability due to service an extension of time schedules constantly sick worker's home, which are performed during the visits, as well as other aspects contained in the new provisions required by the Minister.
Accidents in the workplace, Napolitano: "crucial Prevention"
Every day, in Italy, there are 2,500 accidents, three dead and 27 people remain permanently disabled.
In 2007, Inail data indeed confirm that the white dead were about 1,200.
These figures reflect the seriousness of the phenomenon remains a major cause of death and causes almost twice as many deaths as homicides.
For the attention of institutions, social forces and means of information on this drama, the famous Anmil today, in all Italian provinces, the 58th National Day of victims of accidents on the job, institutionalized the second Sunday of October.
"The worrying data released by the Anmil, as well as the tragic events of recent days, confirm the importance of the topic of prevention in the workplace," says the president of the Republic, Giorgio Napolitano, during a message sent to President Anmil, National Association of maimed and disabled workers, Pietro Mercandelli.
The Head of State expressed his "sincere appreciation for the continued voluntary effort for the prevention of workplace, protection of injured workers, assistance to victims' families and the raising of public opinion"
"Naturally indignant, everyone hit the fist to put an end to such tragedies, by their size, raise the cry of the media and the participation of the public, even if the daily reality presents dramatic case even repetitive in their dynamics.
Napolitano does not hide that "there is certainly a problem of resources: it is essential to invest in training and information"
The many initiatives promoted in the school sector, assume particular importance for a more direct awareness on the part of young people entering the workforce.
It is our duty to keep the attention this phenomenon, do not undervalue the social alarm severity, implement and improve the legislative standards.
For his part, the President of the Chamber Gianfranco Fini stressed how the "phenomenon of white dead is an absolute social emergency that insult the conscience of each of us and requires all institutions to make a specific effort to end it quickly. "
Data on rough work seem to signal a slight positive trend, but that does not mean that the number of white deaths is still impressive, "said the president of the Anmil Pietro Mercandelli later.
"We do not want this" trend on the cheap "is translated in fact, a minor attention because it is precisely when the attention relaxes, comes the tragedy.
"We believe that in general it is not doing enough to contrast the phenomenon of accidents and contrast can be made with multiple actions."
"In our stressed-Mercandelli-plus checks and inspections are required, as a larger work on the training of workers, and this, at school."
- He added, "to do more effort in terms of communication and awareness of public opinion.
"But we must above all a greater sense of responsibility on the part of employers faced with a phenomenon which represents a social emergency."
"Mercandelli then denounced" the progressive deterioration of the protection of the compensation provided to victims of labor "and" drift assistance to which the system is moving in recent years. "
"The goal, therefore, is to give the employee the insurance coverage - he added, so that the fate of one who has an accident, should not depend on spontaneity or enlargement of the legislature"
Mp3 player singled out, they put at risk the hearing.
Listening to music at full volume for an extended period using portable music devices such as MP3 players, can cause permanent damage to hearing.
This is announced by the European Commission, in a statement issued in Brussels, cites the opinion of the Scientific Committee on Health and unanticipated risks identified recently (Csrseri) of the EU, published today.
"This scientific report, we read in the notes it appears that 5-10% of those who, for a period of at least five years, listening to music at full volume using portable music devices, more for one hour per day per week risk permanent loss of hearing. "
"I am concerned that so many young people who frequently use portable music devices and mobile phones at full volume, can unknowingly damage their hearing irreparably" said Kuneva.
"" According to scientists, it continues Ue responsible is a clear risk and we need to react quickly.
What matters most is to educate consumers and make this information public.
We must also review the existing control systems seen scientific opinion, so they can be fully effective and keep up with new technologies "
Brussels has asked the independent scientific committee to examine the problem, given the extensive use of portable music devices and the increasing number of young people exposed to noise that they generate.
"Scientists-finish Executive Ue-confirm that there are good reasons to worry, and that the European Commission will now examine with Member States and other interested parties, what could possibly be adopted to better protect children and adolescents against exposure to noise from portable music devices and similar equipment.
There is already a European safety standard which limits the noise of portable music devices 100Db, but concerns are growing about the hearing damage that could derive from excessive exposure to such noise sources.
It is possible to limit the data well by using solutions such as reducing the levels and duration of exposure to noise.
Ue the Scientific Committee noted that users of portable music devices, which listen to music at high volume (more than 89 decibels) for 5 hours per week exceed the current limits on the maximum noise level made on workplace.
Those who listen to music in such conditions for extended periods risk permanent hearing loss after five years.
This concerns 5-10% of users of these devices, and their number can be quantified at around 2.5 and 10 million people in the EU
Rome, Alemanno gave the order to leave the Commission for the future of the capital.
Today we begin in March we finish in June we will draw the money.
Here is the schedule set by the Capitol to the work of the "Commission for the future of Rome Capital", that took place this morning at the new headquarters, behind the Baths of Caracalla.
In six months, the president Antonio Marzano and 49 other components of the Commission will develop guidelines for Rome.
In March when they are completed, the Committee and the City Council will evaluate analyzes and projects, to be presented in June, the Strategic Plan for Rome with the "official stamp" of the Capitol and its mayor Gianni Alemanno.
"" The commission is absolutely independent, and all the political, social and cultural ideas are represented-emphasizes Alemanno it will propose ideas for development of Rome which can be used by policy makers, who are the Committee and the City Council .
Any overlapping roles, but only the desire to have a corner where a large development project for Rome.
In March, she has finished its work and then disappear, because this experience must have a specific time duration.
In June, announced the mayor will present the strategic plan from the work done by the Commission for the future of Rome Capital. "
To those who accuse the Commission to be useless, because his opinions are binding Alemanno replied: "It depends on the work that the Commission will be able to do, and the quality of its proposals.
If the quality is there, as in France thanks to the Attali Commission, as also in Rome, I am sure, his contribution will be fundamental.
Too often politics is overwhelmed by the daily management and emergencies that occur from time to time.
We, on the contrary, we want to see the front and further towards a deeper prospective seriously working on the development of Rome and its future. "
In addition, the mayor of Rome wishes to emphasize that "this Commission is not a body or a useless bureaucratic together: it is absolutely free and does not cost a euro to Roman citizens, and will study and engage the best intelligences that express the capital.
For Alemanno, in effect, "we need a draft strategic reference or farm or still, to allow our city to improve, what she really needs, while thinking about his future now a spirit of unity, ".
A future that says the mayor of Rome, "will not be limited to the usual municipal boundaries, but look further," not only from the perspective of the future metropolitan city and its legal status as capital, but "as compared the role that Rome can and should be, as the Capital of Europe and the Mediterranean. "
Obama? The first anti-American president. That's why.
A famous American politician who wishes to go for independent, wrote: "Barack Obama is the second anti-American president.
The first was Jimmy Carter, who, because of his decisions, destroyed the U.S. economy and had relations (as indeed it still is today, as a private citizen) with the enemy Islam. "
Attacks against Obama are increasing while the election date approaches.
A lady from Miami wrote on a website: "this person is full of ambition."
Obama is really cheeky: he believes he will win the highest office of a nation that has a total of two governors and five black senators! "
In reality, it is attacks that do not say much, it is obviously attacks racial nature, and do not answer the question of all voters: he will be a good president? We also polls all Obama win and a good advantage that report.
In this case, there is still someone who speaks from the heart and not the brain.
A newspaper of the Mississippi, in the bowels of the southern United States, wrote an article once in the voting booth, we know who the American patriot give his vote.
Here emerges an aspect of the American mentality kept secret until the end.
"Say what you want, we will ourselves to the cross on Obama or McCain.
There are even people who swear: if Obama wins, we will leave the United States.
Things never revealed until now, to the point that the success of black candidate seems almost certain.
Anyway, despite all these arguments, the winning card for the Democrats is George Bush.
We asked 1,500 people: what were the mistakes made by Bush during his tenure? 89 percent responded Iraq.
America changes.
In Vietnam, the nation lost 50,000 soldiers and was sent home to kick the butt.
In Iraq, 4,500 soldiers were killed, and the U.S. have been forced to pack.
Despite this, Iraq was, for the most part, the weak point of Bush.
Who will replace George W will have a huge task ahead.
Usa, the economic meltdown is felt even among journalists in the press, it's time deletions. And many blame the Internet, this "murder" newspaper.
Five hundred American journalists were arrested by the Pew Research Center about the status of their profession and mind control for the future.
Well, almost all journalists today are pessimistic about their future.
However, they have not openly declared the attached information, feel less worried about credibility.
They do not feel isolated as before.
The problem of American journalists, it's money, the money.
The crisis of 2008 for these journalists is a crisis of economic model destroyed.
In addition, deletions in the newsroom, in the room where the writers work assembling newspapers, are a big problem.
This is a problem that must be solved, according to the interviewed journalists, if you want the traditional journalism as the public hears, being reduced consistently.
An obvious but complex pessimism pervades American journalism.
Six out of ten senior executives and journalists from print newspapers are convinced that journalism at the national level is currently taking a wrong path.
Locally, the executive group is 65%.
Against broadcast printed publication.
Journalists have no trouble seeing where will the web.
The larger publishing houses make their way to the Internet, perceived by many as "the murderer" newspaper.
"Economic pressure" that journalists feel is increased to 79%.
The 500 journalists interviewed agreed to put the technology hoping that "do something good" for their journalism.
Today, the biggest hitch in American journalism lies between newsrooms that direct-that is to say, the directors and reporters who work for them.
56% of managers at the national level, are convinced that reporters share their values, while at the local level, this percentage drops to 23%.
For some, this is related to "security work".
The directors believe that losing their job in the space of 3 years were 47% nationally.
Regarding the media, it goes to 30%.
That of "safe work" the staff level (our editors, ed) in America is always on the agenda.
Only 13% of journalists working under contract.
In a vast nation like Usa, with 300 million people and thousands of journalists, magazines, radio, TV and Internet, employers often provide what they want, and it becomes a question of take it or leave quickly.
The directors are almost always big salaries, while the writer can earn $ 10mille per month, in addition to the payment of pensions and insurance.
As for the holidays, the logic becomes complicated: x days after the first year, x days after the third, up to 15 days in all, spent a number of years.
But according to their revelations, American journalists are often "sick" during the year.
It is the fault of the climate.
UNIPOL: COURT ROME, DANILO COPPOLA REMAINS GROTTAFERRATA.
President of the Second Criminal Section of the Court of Rome, Carmelo Rinaudo, decided to reject the authority of the real estate agent, Danilo Coppola, who had asked to leave the city, Grottaferrata, for a house in Rome.
. Coppola is investigated for bankruptcy under the instruction on climbing Unipol-Bnl.
At the trial in his office last week, he got home setting freedom transformed into compulsory residence in Grottaferrata.
His lawyers, Michele Gentiloni and Gaetano Pecorella, had requested that the real estate agent can make the journey from the provincial town to a house in the capital.
According to the court, such movements (the pm has not granted) would allow it to influence the society and have access to evidence that the accused.
Elites in danger.
The phenomenon had already appeared a few days ago, with the vote of the House of Representatives, contrary to the bailout of $ 700 billion approved by the White House: a good number of Americans was significant, and is still more interested in punishing Wall Street than saving the U.S. economy.
And this is the New York Times yesterday that we communicate confirms that the current crisis divides the Republican Party, even shared his soul before East Coast, moderate, pro-federal as well as the business community institutions, and his new soul, on the contrary, conservative, hostile to those "Washington" and the world of finance, especially strong in the states of Central and South America.
The soul, in fact, that was felt so despotic with the vote that I mentioned at the beginning.
However what has been mentioned is just one example of the changes, major changes that the economic earthquake during pre-announcement or leave already running: not only the United States but throughout the West, and can not just here.
The United States and Europe, the crisis seems to accelerate the phenomena incubated for some time, so much so that, in the new climate, they solidify and prove.
The first of these phenomena is updating the extraordinary revival of the dual-class sovereign state, compared to a kind of re-nationalization of the economy.
The crisis, in fact, a crisis-bank financial institutions that, obviously close relations with foreign countries, but, above all, are involved in large-scale balances of individuals and families living in one's country, in one state.
This immediately creates a political problem which the government: that is like answering the difficulties and protests from individuals and families who are also an electorate.
In short, the economic crisis appears global, but politically it is almost here National.
The internationalization policy seems really offside or did not have much to say, clear evidence is provided by the European Union, divided as usual between the various interests and between the various national strategies, gets to decide no common political line.
And so is the government of each State all waiting interventions, bailouts and stimulus packages, the new rules, especially a condition of credits: when going through a difficult period, there is the States that have the economic resources, the mass of financial resources capable of trying to put things in place.
They also have the necessary means and legitimacy to use: two invaluable resources, elements of which no market or international organization can never have similarly.
This new emphasis of the nation-state crisis are still in perfect harmony with the major that always the latest economic developments in the economy tend to assign a fairly associated with this item factor importance of territoriality.
. Paradoxically, in fact, while we were convinced that they have now entered into the realm of networking, increasingly sophisticated technology, the non-material, convinced that global finance was now destined to dominate the world, we have realized a sudden one, that our future will instead settle accounts ever with pretty little material such as water, crops, oil things.
Things that can certainly be transported from one place to another land, but are absolutely related to a circumscribed space, territory.
So, who is sovereign, certainly has more cards than one who is not, that is to say, who has the misfortune to live in a place without harvest, without oil or water.
I come now to the second novelty, however, provides a fracture.
Who said Territory, State, Government, Politics inevitably says, and therefore Leadership.
In this regard, the economic crisis seems to produce two converging phenomena.
On the one hand, the consciousness of objective need for authoritarian leadership, looking for someone who can take control of the situation.
On the other hand, a wave of discrediting existing leaderships, economic species that have proved inadequate and full of gray area.
And besides, something even more profound thing in a sense, even worrying discredit, suffering, an inadequate image, a sense of remoteness which tends to involve the entire class of directors in a growing number Country of the West.
And even increases the conviction of the various classes, before the shares are the same ideas of social elites until now at their peak, their way of listening and being, their culture in the complex sense of the term, to have the same time and still be more alien to the views of majorities.
In short, demand for leadership, so groundwater supplies, a powerful and branched délégitimassions movement of the ruling classes and traditional political orders, which are manifested in the election "riots" or improvised in changes of collective moods these very recently, from the conservative ascent Austria Bavaria, the fall of the Labour Party in Britain, the U.S. Congress rebellion against Bush (and it may well be that the victory of the right in Italy is not happened by accident).
One has the impression that the traditional elites, their parties, their programs, but also their rites, their newspapers, their accredited intellectuals, their format, like someone always harder, which did not start today 'Today, to understand and therefore to represent the deep layers of Western societies, and that the economic crisis strengthens, increases and potentially agitated disproportionately.
In view of all this talk about a current "rebellion of the masses" to the agenda, frankly seems exaggerated.
But they say well, keep the eyes wide open, it is not without reason.
Superglue to walk on walls.
Defeat the laws of gravity with a super glue and in the future, walk on walls like Spiderman.
That's the goal of various American research centers, and today, a team of four institutes are almost succeeds.
With adhesive stood only 2.5 square centimeters, researchers have managed to maintain a bonded body 100 kg on a vertical wall.
STUDY-The journal Science published the findings of some researchers at the University of Dayton, Akron, Georgia Institute of Technology and Air Force Research Laboratory.
The material, invented by the team of researchers, is an evolution of what we know about using a particular structure of carbon, called carbon nanotubes.
"The principle of the adhesive can be imagined as a series of tubes arranged like a pile of spaghetti." Says Zhong Lin Wang of the Georgia Institute of Technology in Atlanta.
Scientists were inspired by geckos legs covered with microscopic hairs that allow the animal to ensure a perfect grip.
Tests on various materials such as glass, Teflon, glass and paper, have shown that the new adhesive is ten times more powerful than the legs of these reptiles, and at the same time, it "stands easily to the wall, "says Liming Dai, a researcher in the Faculty of Engineering of the University of Dayton.
WALK ON THE WALL? - "This material could be used as a temporary adhesive" says Liming Dai.
May be to walk on walls like Spiderman? Maybe so, but the researchers believe to be used much less fascinating as the connection between electronic devices, since the carbon nanotubes are conductive of heat and electricity.
Other applications could include an aerospace engineering.
For now, no superhero.
OTHER RESEARCH University of Berkeley, California, is dedicated also in search of a new adhesive.
In an article in the journal American Chemical Society, the California researchers presented an adhesive made of microfiber like hair, which self cleans dust during movement over a surface to ensure a perfect and consistent grip.
Drugs: Never with fruit juice.
Beware of grapefruit, orange and apple.
These drinks, consumed especially in summer as refreshing and rich in vitamins, if associated with certain vital drugs, alter the absorbement amplifying or decreasing depending on the case, their effectiveness, even with serious health consequences.
David Nailey, professor at the University of Western Ontario in London, said the risks of juice they are, canned or fresh, if associated with the ingestion of certain medications during the 236th national meeting of the American Chemical Society in Philadelphia in progress, he launched a new alarm: just a glass of grapefruit, orange and apple to reduce absorbement some vital medicines, canceling their benefits and endangering the patient health.
Grapefruit juice has been strongly criticized as held responsible to increase the effects of certain anti-arrhythmic drugs, antibiotics, anxiolytics, anti staminal and neurological up to toxic levels.
DRUGS A RISK-This is the Italian Medicines Agency itself, which gave the news in an information bulletin dated two years, alerting doctors and patients not under estimate the danger arising from the mix and be careful what you drink, if you take drugs such as diazepam or methadone.
THAT THE GRAPEFRUIT-According to experts, even the orange and apple juice contains substances that inhibit the drug.
Long is the list of active ingredients inhibited by grapefruit and other juices.
From there, call Michele Carruba, director of the Department of Pharmacology, State University of Milan: "These findings are in general immediately reported to various national and international agencies need drugs if necessary, change the informative notes drugs.
It is always advisable to read the papers illustrative of the medicines you take, and if something is not clear, do not be impressed, but speaking clearly to your doctor or pharmacist "said the expert Ansa agency.
The Nobel economics Paul Krugman.
The Nobel Prize in Economics was awarded to American Paul Krugman for his work on trade patterns and location of economic activities.
Krugman, 55, is a neo-Keynesian who teaches at Princeton University and is also a celebrated New York Times.
Krugman is one of the biggest critics of solutions in economics and foreign policy of the Bush administration.
A few months after the attacks of September 2001, during the days of the collapse of Enron, Krugman wrote in an article published on the New York Times, the second event was more important than the first, in terms of impact on the history of the United States.
Forecast that unleashed numerous controversies, and was charged to the economist for years, but now proved correct.
"I'm surprised and a little shocked by the speed with which the memory of scandals such as the collapse of Enron and Worldcom, have disappeared from the public eye" Krugman stated at the end of 2002.
According to Lorenzo Bini Smaghi, the executive committee of the European Central Bank, Krugman is an "economist valuable", but also a whistleblower at very aggressive style, "particularly critical of the excesses of liberalism of the Bush administration.
Open Office, this is the third edition of the package "anti-Microsoft"
This is the day of release of OpenOffice.org.3.0, the open source personal productivity is always touch and more users, home office, professional public administration suite, offering a free alternative to the more popular Microsoft Office.
Following almost a year of work, directed by volunteer developers, monitored by SUN Microsystems, the new Open Office package shows the general public with a variety of new features: the welcome screen and the redesigned user interface and become less austere, other more important, such as compatibility born for Apple Mac OS X operating system, and support for the new ODF (Open Document Format) 1.2, the latest version of the standard ISO format.
Open Office has paid particular attention to the interaction with Office 2007, and it is possible to open documents with the new extension of Microsoft (. Docx,. Xlsx,. Pptx).
Also interesting, some functions specific to certain modules, such as that reduces the size of PowerPoint presentations useful, for example, to send email, or import PDF file into the graphic processing unit, retaining the original appearance of the page.
Also on this front, it is possible to create documents "hybrid PDF" uniting the typical graph of Adobe size items in a spreadsheet or text winemaker.
Collaboration between several people is something that has had various improvements within the applications in the spreadsheet, different users can intervene, avoiding conflicts of changes in the development of texts, because each employee is assigned a color commentary for better recognition being revised.
Some companies are even working to bring some of OpenOffice functions on the Web (on the cloud, the cloud), and in the coming weeks, they should make the final result.
The Italian version is dischargeable in http://it.openoffice.org/download/3.0.0/download300.htmlet address is added to the English version that was on the mirror since Friday.
In addition to Windows and Mac OS, the result is as usual available in addition to the Linux operating system.
On request the installation CD can be shipped to home or workplace.
And if the subject of the charge may be a way to diffuse into the houses, it is precisely in the business, Open Office after attempting the challenge, can already count on a variety of projects in the public administration and schools.
Besides the reality that provide a training service, consultation and assistance, ideal for small and medium enterprises, which could also open to prospective business.
Open Office consists of five main modules: Writer to write the video equivalent of Word, Calc, the spreadsheet is designed to replace Excel, Impress for rival Powerpoint presentations, Dbase, such as the famous Access is program that allows you to work on databases and finally DRWA is the graphic module.
Target for 2008, reaching 5 million downloads, and considering that today there are nearly 3 million and 600,000, it is likely that the release of the new version, we can even exceed the number expected
Kohl also is positive, this is the fourth case of doping.
New positive cases in the last Tour de France: it is the Austrian team Gerolsteiner's Bernhard Kohl, qualified third and won the best climber's jersey.
This is the site of the daily L'Equipe reported that the new.
At 26 years, Kohl is the fourth positive cyclist Cera, Epo third generation after the Italian Riccardo Riccò and Leonardo Piepoli and German Stefan Schumacher, Gerolsteiner too.
Blood tests performed on specimens Kohl are among those made in recent weeks by the laboratories in Lausanne and Chatenay-Malabry.
If testing confirms against positivity Cera, Austrian loses his third place in the Tour and will necessarily expect two years of disposal.
The news of the positivity of Kohl Epo third generation was confirmed by the head of the French anti-doping agency, Pierre Bordry, who contacted The Associated Press, have reported positivity to the Austrian authorities.
The Austrian 26years has placed on the podium behind Spaniard Carlos Sastre and Cadel Evans American, and wrapping up the polka dot jersey for the best climber.
IMMIGRANTS: NEW YORK TIMES ASKS WHETHER ITALY IS RACIST?
Italy 'as Country of emigrants was recently transformed into a preferred destination for immigrants "greeted with reluctance.
It would transform the beautiful country into a nation of racists? That is what is intéroge the New York Times devoted a long article discussing the subject of racism in Italy, based on the case of the young Abdul Guibre William, a native of Burkina Faso, who was killed last month in Milan, for stealing a box biscuits.
This case highlights that the New York Times defines as the "paradox of the North": the northern regions are those where both "integration more and more work" is recorded, but also "an anti sense the strongest country immigrants and greater support for the Lega Nord "
To confirm the growing tension between Italians and immigrants, the NYT also refers to episodes of intolerance Milan, Parma, Rome, Ciampino and Castel Volturno.
not only.
Even the new desired by the Lega to curb immigration and facilitating the expulsion of illegal legislature, is cited as evidence of climate change in Italy.
Trend highlighted by the Pope and the President of the Republic: "Giorgio Napolitano during his meeting with Pope Benedict XVI at the Quirinal, has requested that the State and the Church work together to overcome racism."
Students victims of high rents, up to 900 euros for a room.
The rental market for students knows no crisis
According to the latest survey of Samaya, the union of tenants, rent a single room can cost a student up to 900 euro in Milan, Florence 700, 650 Naples, 600 in Rome.
"The phenomenon has now reached serious aspects to the exclusion of entire categories of young people, the right to study because of the very high overall costs that families need support from, says the head of the research department of Samaya, Laura Mariani, in these cities, demand from students has so distorted the market a process generalized increase was amorcémême for residents.
In most cases, rental also comprise a series of violations: free type contracts, unregistered, without limitation rent, sublets.
For Samaya, extraordinary interventions through the revision of taxation are needed to calm prices.
Reading in detail the survey, we see that Milan for a bed in the Brianza area, it takes about 450 euros for a single room, we will minimum of 650 euros (zone Bande Nere), an average value 800 (area Lambiate, Udine, and Fiera) to a maximum of 900 euros (Vittoria area)
In Florence, a bed costs an average of 350/400 euros, 700 euros a room.
In Bologna, where students are concentrated in areas close to the University, must be 250/280 euros for a bed in a double, and 370 to 500 for a single room.
In Rome, in the areas near the central universities (San Lorenzo, Piazza Bologna), it takes about 600 euros for a single, 450 for a bed in a double.
Slightly lower values ​​(550 euro for a single) for areas near other Universities (Ostiense and Cinecittà).
You can not save if you move away in peripheral areas: 300 euro for a bed, and 450 for a single in the predestined, Centocelle or similar area.
In Naples, for a bed should be 300/400 euros for a simple, one spends 400 to 600 euros, the highest price in the Policlinico areas, Vomero and Colli Aminei.
A Bari to bed, it takes 250/350 euros, at least 350 for a single.
In smaller cities, prices are lower in absolute terms, but they have a major importance in the urban economy.
Finally, cities such as Perugia, where rentals are often made by non-EU students, there was a further anomaly: the rent charged to foreign students is increased by 25/30% compared to that applied to the Italians.
Farewell old cinema Paradiso, cities eliment the historic rooms.
Historic cinema halls close for the Multiplex.
"A city without cinema is a blind city is like a face without eyes"
The picture provided by the director Giuseppe Tornatore, illustrates what happens in major Italian cities, but also in provincial towns
The marginalization of cinemas, with the birth around large multiplexes and died of consumption of mono rooms in the central areas of cities, is one of the major events that seems to us inevitable and undeniable, it has all of those features a true cultural crime.
To disappear, they are often responsible for memory and historical places, "it is as if one of my friends disappeared, someone you know, with whom we shared a long way and so many emotions," observes director of Nuovo Cinema Paradiso, Tornatore film offers 20 years ago, the first Oscar and the Grand Prix at Cannes juror, who told poetry en province, and the nostalgia of a way of life film, may be lost forever.
The figures provided by ANEC, the main association of traders, mean everything: the past five years, 316 cinemas have closed traditional type, and these are the rooms of the major cities who paid the most: at least 10 Florence, 9 in Milan, Naples, Bologna and Rome, 6 less in Turin, Palermo 5.
Among the most affected by the closure regions, Emilia Roman leads with 82 cinemas lost mono rooms, followed by Tuscany (44) and Lombardy (41).
The evidence confirms that the first t responsible for their disappearance is the advent of the multiplex, because those are the three Italian regions that experienced the most new multiplex cinemas: 195 more screens in Lombardy in the past five years, 81 Tuscany as in Emilia-Romagna.
"The Italian operation has grown irrationally" notes Paolo Protti, President of ANEC, "it is useful to build new structures, but it would still ensure the survival of those that already exist, because when a farmhouse living in a city, these fréquenteurs are not necessarily willing to go all the multiplex.
Not to mention the missed deliberation credit for traders: the antecedent debt of the State is about 10 million euros.
It is shameful that an ethical and moral point of view, the Government did not comply with existing laws.
To support the sector, it would take between 16 and 18 million per year.
Note the case of Bologna, the first Italian city which concerned the closures, decided to resolve the situation with the signing of a protocol between City Hall and ANEC, the first of its kind in Italy, to defend and promote the cinema Single rooms historical centers and peripheries.
Among the standards set, there are measures of tax incentives for managers and public benefits in terms of mobility: the audience will enter the restricted traffic area, and have special rates for parking and some parking .
"This is an initiative that I like" notes Giuseppe Tornatore "and I hope that other cities will follow the example of Bologna implementing other measures.
However, it is clear that to contrast the super power of the multiplex, traditional rooms should also improve the quality of sound and image, because today's audience is more demanding.
The defense of traditional cinema is a theme for me, has always been important: the closure of Supercinema Bagheria, the place of my childhood and adolescence, was the spark that convinced me to "New Cinema Paradiso" which I been thinking 10 years.
I live in Rome for 25 years, and when I pass the Rialto or the Quirinale Via Nazionale, now closed, where I lived as shared emotions, I turn to the other side not to see panels blackened by dust.
Links between policy and 'Ndrangheta, arrested the mayor of Gioia Tauro.
"The mayor of Gioia Tauro was willing to standardize the choice of Mayor Piromalli clan's interests."
heavy charges are initiated by the magistrates of the Calabria Anti-Mafia Directorate, to the mayor and vice mayor of Gioia Tauro, Giorgio Dal Torrione and Rosario Schiavione, and the mayor of Rosarno Carlo Martelli, arrested this morning for open competition for mafia association.
The controllers also Gioacchino Piromalli, the former mediator between the clan and the government, and his little son lawyer namesake boss, already convicted of conspiracy mafia type, as well as pay 10 million euros.
"An affront to the legal and ethical standards, and especially common sense" wrote prosecutors, two local authorities had expressed willingness to pay consultations Master Piromalli.
"So we have been granted the clan write-judges-to formally enter inside the halls facilitating opportunities, already considerable, control and orientating public administration"
The President of the Calabrian regional committee Agazio Loiero, does not hide that "collusion between local committees and organized crime, there is more than one" in the region, "there are places where the mafia intensity is stronger than in others, where collusion is almost inevitable.
But there are many politicians who resist the pressures of the Ndrangheta, heroes who are honest "
The arrests this morning follow those of last July, following which the police have announced decapitated Piromalli clan.
By the end of April, the municipal council of Gioia Tauro had been dissolved, and already in 1991, and again because of suspected packages between organized crime and the local administration, local politicians had been relieved of their duties to administer city.
Giorgio Dal Torrione, Mayor of the UDC at the time of dissolution, had been appointed head of a center-right coalition after the May 2006 ballot.
He cried foul when the prefecture ordered the dissolution of the municipal council.
He accused the deputy interior minister at the time, Marco Minniti, accusing him of having engineered all for a political issue, but since the application for committal signed this morning, the judges explained that the clan had Piromalli even managed to ask the change project A3.
Starting interceptions ordered against Dal Torrione the write pm, tip is "availability requirements to marry a businessman, best known representative of a group, close Piromalli, standardizing the choice of public administration at clan interests.
When the energy born of the waves are getting big now.
This is a disproportionate deposit which occupies more than 70% of the area of ​​the world and now the world's major energy companies are trying to find out.
Waves, currents, tides, that new renewable sources that giants like Chevron have laid eyes on, and are now trying to put the hand.
The ability to obtain energy from the movement of the sea has been studied for centuries now, and in the 70s, in conjunction with the first oil crisis, research has intensified.
When oil prices dropped around 1980, the idea of ​​exploiting marine energy was set aside, but now ecologists instances and further increase oil give a great boost to sector
The World Energy Council (WEC) in London estimated in 2007 that 15% of world electricity needs could be covered by operating the swell of the sea systems.
This amount would be double that produced by nuclear power plants.
And besides, there would be currents and tides ..
Giants to attack.
The first company to focus on marine energy was Enersis, which in 2005 siglé an agreement to build a plant in northern Portugal.
When the agreement was announced, it seemed not a true revolutionary.
Two years ago, more and more candidates from these companies have always been dedicated to the traditional energy rely on marine energy.
"Chevron is currently studying ocean energy technologies, said the spokesman of a company associated with the American oil giant, the business daily Wall Street Journal, and evaluates opportunities to cooperate with us."
Cooperation in question relates to the production of a deliberate effort by the U.S. Commission for energy necessary to give rise to an operating marine energy project in Alaska allowed.
This is a very interesting signal, especially when you consider that just in Alaska, Usa to continue extracting oil, and President Bush recently set up a project for new excavations
In addition to Chevron, there Verdant Power Inc. of New York and New Jersey Ocean Power, who walk the path of energy from the sea, and the money invested until today, although their details are known, according to observers indicate a growing interest.
Tecnologie to make the point.
Experts speak of a technology still in its infancy, because of the fact that marine energy does not dissipate fears about the environmental impact.
Currently, systems like those of Portugal, or some in Scotland, are small and do not seem to create a big problem in the ecosystem.
To produce energy on a large scale, however, use of technology with a higher environmental impact.
"And the choices are diverse: Ocean Power, for example, uses a system of buoys connected to each other.
The thrust of the waves, which moves the sludge to the top and bottom, is converted into a hydraulic pressure of the pistons and cylinders inside floats.
Pressure drives a turbine which in turn powers a generator.
Power is sent to shore through submarine cables.
For now, we have four such systems in the design phase, pending federal approval and a unique part of the energy could be used for a military installation.
Verdant Power, however, is already producing energy for a shopping center and parking using six underwater turbines in the East River in New York.
The movement of the tide in water, rotates the turbine blades, creating a rotational movement which powers a generator.
Verdant have announced a long list of customers waiting for permission to draw energy.
After the waves, the tides.
Of particular interest, they say to the Research Institute of Electric Power, deserves at this time, the potential of the tides.
Although an intermittent phenomenon, the tide is more predictable wind, sun and waves, and therefore more reliable as an energy source.
And it is precisely on tidal energy that states like New York, Maine and Alaska, with others, looking towards the coast, have invested $ 7 million and a half dollars in 2008 and will invest up to 35 million in 2009.
